```{r, include=FALSE}
knitr::opts_chunk$set(echo = F, cache = T, warning=F, message=F, 
                      fig.width=4, fig.asp = 0.618, out.width = "95%", 
                      fig.align = 'center', fig.pos = 't')

source(here::here("index/disseration_helpers.R"))
intro_figs_path <- "index/chapter_child_rmds/Active-social/figs/"
```

## Introduction

Early cognitive development is remarkable. Consider that children, despite limitations on their processing capabilities and ambiguity in the input, rapidly acquire new lexical concepts, eventually reaching an adult vocabulary ranging from 50,000 to 100,000 words [@bloom2002children]. And they accomplish this all while also developing motor skills, learning social norms, and building causal knowledge. How can we explain the children's prodigious learning abilities?  

Social learning accounts point out that children do not solve these problems on their own. Instead, they are typically surrounded by parents, other knowledgeable adults, or older peers -- all of whom are likely to know more than they do and want to facilitate their learning. Social learning accounts also emphasize how social contexts can bootstrap children's learning via several, distinct mechanisms. For example, work on early language acquisition shows that social partners provide input that is tuned to children's cognitive abilities [@fernald1987acoustic; @eaves2016infant], that guides children's attention to important features in the world [@yu2007unified], and increases levels of sustained attention, which results in better learning outcomes [@yu2016social; @kuhl2007speech]. 

Social contexts can also change the inferences that support children's learning from evidence. Recent work in the fields of concept learning and causal intervention suggests that the presence of another person engages a set of psychological reasoning where the learner thinks about *why* other people performed specific actions. The critical insight comes from knowing that another person has intentionally selected examples, which allows children to make stronger inferences that speed learning [@frank2009using; @bonawitz2016computational; @shafto2014rational]. For example, children learn at different rates after observing the same evidence depending on whether they thought the actions that generated that evidence were accidental (less informative) or intentionally selected (more informative). Moreover, adults and children will make even stronger inferences if they believe that another person selected their actions with the goal of helping them to learn (i.e., teaching) [@shafto2012learning].

However, children are not passive recipients of information -- from people or the world. Instead, they actively select behaviors -- for example, asking questions or choosing where to allocate visual attention -- that can change the content, pacing, and sequence of their learning experience. Recent theories of cognitive development have proposed the metaphor of the "child as a scientist" and characterized early learning as a process of exploration and hypothesis testing following principles of the scientific method [@gopnik1999scientist; @schulz2012origins]. Moreover, empirical work across a variety of domains -- education [@grabinger1995rich], machine learning [@settles2012active; @castro2009human], and cognitive science [@markant2014better] -- has directly compared learning trajectories in self-directed contexts (active learning) as compared to settings where the learner has less control (passive learning). The upshot of this work is that active contexts often lead to faster learning because of enhanced attention and arousal or because learners select information that is closely linked to their current goals, uncertainty, and skill (see @gureckis2012self for a review). 

Thus, children are capable of selecting actions to support their learning, and a large body of work shows that social partners can create particularly rich contexts for learning. Empirical work within each framework, however, has often focused on the separate effects of active or social processes on children's learning. An approach that does not reflect the ecological context in which language acquisition unfolds. That is, children acquire their first language from interactions with other people where they have the opportunity to select actions -- where to look, where to point, what question to ask -- that influence the content and pacing of the experience. This mismatch between the existing empirical work and the ecological context in which children learn highlights the need for integration across the active and social theoretical accounts.

But how can we integrate these two proposals, which often include definitional issues and a lack of formal foundations? In this chapter, I present an integrated account of active learning within social contexts, arguing that it represents an important step for theories of early cognitive development. To connect the active and social learning proposals, I use the computational frameworks of Optimal Experiment Design [@emery1998optimal; @lindley1956measure] and Bayesian models of social reasoning [@goodman2016pragmatic]. The key insight is that the presence of another person can modulate the *availability* and *usefulness* of different actions that the active learner could select. Specifically, social interactions can shape learners' goals, hypotheses, actions, answers, and decisions about when to stop gathering information.

In addition to the theoretical account, this chapter provides concrete definitions of active and social learning to clarify the behaviors and phenomena that the account aims to address ([Part I](#scope)). Then, we briefly review the framework of Optimal Experiment Design (OED) ([Part II](#oed)), highlighting how it can be can be used to formalize human information seeking behaviors. We also discuss the empirical evidence for OED-like reasoning in both adults' and children's learning. Finally, we conclude by presenting the integrative account of how social contexts can shape information seeking ([Part III](#active_social)). In the final section, we also highlight a series of new links between the social and active accounts, which present a way forward for empirical work that sheds light on how children's active learning operates over fundamentally social input.

## Part I: Learning from others and learning on your own {#scope}

A diverse set of scholars, theories, and empirical work has considered the contributions of active and social processes to children's learning. One consequence of this range of approaches is that the terms "active" and "social" have become associated with a variety of meanings. Thus, before integrating the two accounts, it is worth defining what we mean by active learning and social contexts. By providing clear definitions, this section aims to clarify the behaviors and phenomena that the integrative account attempts to explain.

### Social learning

Learning can be social in a variety of ways. First, children could learn with another person present but without attending to or directly interacting with them. Research in social psychology shows that the mere presence of other people can facilitate the performance of simple tasks and impair the performance of complex tasks [@uziel2007individual; @cottrell1968social]. Second, children could learn by looking to others as a guide and observing or imitating their behavior. Children's capacity for faithful imitation has been argued to be a critical feature separating human from non-human learning [@call2005copying]. Finally, children could both attend to the person and directly interact with them, entering a communicative learning context that engages psychological reasoning processes that alter the course of learning [@shafto2012learning; @frank2014inferring; @goodman2016pragmatic]. 

For the integrative account discussed in this chapter, we define a social context as a learning environment where another agent is present. This definition includes all of the social learning behaviors -- observation, imitation, and learning from direct interaction -- discussed above. This broad definition highlights the diverse pathways through which social information could interact with children's active learning. Moreover, this definition captures the variety of contexts in which children develop, i.e., in some cultures children experience high amounts of child-centered interactions while in others they are often expected to learn through observation of older peers and adults [@rogoff1993guided].

Social learning theories emphasize that children's rapid conceptual development is facilitated by the uniquely human capacity to transmit and acquire information from other people. A primary benefit of learning from others is that children gain access to knowledge that has accumulated over many generations; information that would be too complex for any individual to figure out on their own [@boyd2011cultural]. In addition to the cumulative effects, social contexts facilitate in-the-moment learning since more knowledgeable others can provide input that is most useful for children [@shafto2012learning; @kline2015learn] and communicate information that is likely to generalize to other contexts [@csibra2009natural].

There is a large body of empirical work showing the effects of social input in a variety of domains, including language acquisition, causal learning, and concept learning. For example, newborn infants prefer to look at face-like patterns compared to other abstract configurations [@johnson1991newborns; @farroni2002eye], to listen to speech over non-speech [@vouloumanos2007listening], their mother's voice over a stranger's [@decasper1987human], and infant-directed speech over adult-directed speech [@cooper1990preference; @pegg1992preference; @fernald1987acoustic]. Moreover, these attentional biases lead to differential learning in the presence of another person. 4-month-olds show better memory for faces that gazed directly at them [@farroni2007direct], for an object if an adult gazed at that object during learning [@reid2005adult; @cleveland2007joint], and perform better at tasks such as segmenting words from infant-directed speech compared to adult-directed speech [@thiessen2005infant]. @kuhl2007speech refer to these effects as "social gating" phenomena since the presence of another person activates or enhances children's underlying learning mechanisms. 

In addition to enhancing attention and memory, social contexts can facilitate learning by generating useful information tailored to the child's current developmental stage [@vygotsky1987zone]. Empirical work shows that caregivers alter their communication style when speaking to children (e.g.,exaggerating prosody, reducing speed), which in turn can help children learn vowel sounds [@adriaans2017prosodic; @de2003investigating], segment the speech stream [@fernald1991prosody; @thiessen2005infant], recognize familiar words [@singh2009influences] and learn new lexical concepts [@graf2013infant]. Additional evidence comes from @goldstein2008social's study where they found that infants modified their babbling to produce more speech-like sounds after interacting with caregivers who provided contingent responses, suggesting that contingent, social input was particularly useful because it was closer in time, making it easier to compare discrepancies between the child's vs. adult's speech sound. Finally, converging support comes from research on children's early word learning, which shows that social partners actively reduce the complexity of the visual scene by selecting actions -- gaze, points, holding -- that make a single object dominant in the visual field [@yu2013joint; @yu2005role] and by producing labels for objects that children are already attending to [@tomasello1986joint].

Another feature of social interactions is that other people's actions are not random; instead, other people intentionally select actions for some goal (e.g., to communicate information). And if children are sensitive to *why* someone performed a behavior, they can use this information to facilitate learning. Recent empirical and modeling work has formalized this idea as a process of belief updating in Bayesian models of cognition [@shafto2012learning; @frank2014inferring; @goodman2016pragmatic]. For example, adults are more likely to think that pressing both buttons is necessary to activate a toy if that action was demonstrated by someone who knew how the toy worked as compared to someone accidentally pressing both buttons [@goodman2009cause]. @shafto2012learning interpret these results as a psychological reasoning process: "if the other person were knowledgeable and wanted to generate the effect, then he would perform both actions." This finding also suggests that learners assume that others' goal-directed behaviors will be efficient and they should avoid performing unnecessary actions.

Similar effects of psychological reasoning on inference occur in word learning [@xu2007word; @frank2014inferring], selective trust in testimony [@shafto2012epistemic], tool use [@sage2011disentangling], and concept learning [@shafto2014rational]. Moreover, there is evidence that even young learners' inferences are sensitive to the presence of goal-directed behaviors. For example, @yoon2008communication showed that 8-month-olds tend to encode an object's identity when their attention was directed by a communicative point, but they will encode an object's spatial location if directed by a non-communicative reach. And @senju2008gaze found that infants are more likely to follow another person's gaze when it was accompanied by relevant, communicative cues (e.g., infant-directed speech or direct eye contact). 

Finally, several accounts of cultural learning argue that an assumption of *generalizability* is fundamental to social learning via communication, allowing for the accumulation of cultural knowledge across generations [@csibra2009natural; @kline2015learn; @boyd2011cultural]. In these explanations, adults generate ostensive signals such as direct gaze, infant-directed speech, and infant-directed actions, which, in turn, direct infants' attention and bias them to expect generalizable information. Experimental work testing predictions of this "Natural Pedagogy" hypothesis shows that children tend to think that information presented in communicative contexts is generalizable [@yoon2008communication; @butler2012preschoolers], and corpus analyses show that generic language (e.g., "birds fly") is common in everyday adult-child conversations [@gelman2008generic].

The work on social learning reviewed in this section highlight several points that are important for theories of cognitive development. First, from an early age, children are surrounded by other people who know more than they do. Moreover, these more knowledgeable others are invested in children's development and can provide useful learning opportunities. Second, children are motivated to interact with other people, and these interactions engage and guide attention to relevant information. Finally, social contexts can trigger a set of psychological reasoning mechanisms that lead to stronger inferences, allowing children to get more information out of the same evidence.

Social learning accounts, however, often reflect a relatively passive construal of the learner. And it is evident that children are not just passive recipients of information from the world or other people. Instead, they actively process information and select behaviors that change their learning experience. A growing body of research on children's active learning has developed alongside social learning theories.

### Active learning 

Learning can also be active in a variety of ways. First, a child could be physically moving, and these actions could change the way they process information. Research on embodied cognition has explored the effects of action experience on infants' learning (see @kontra2012embodied for a review), showing results such as infants who physically hold and manipulate objects will outperform a control group on measures of object attention and exploration [@needham2002pick ].  Second, active learning could refer to children's active internal monitoring and processing of incoming information. For example, young learners do not just accept other people's claims and will reject answers that conflict with their knowledge [@pea1982origins], and children engage in self-generated explanations that can lead to changes in how they process and retain the same incoming information [@lombrozo2006structure]. Finally, active learning could refer to a decision-making process where children take actions that control the sequence and pace of their learning experiences.

For the integrative account discussed here, we focus on active learning effects that arise via children's decisions about what action to take next. The key assumption is that active learners take actions that maximize the amount of information they can get while minimizing the costs of effort and time. By limiting the account to active decisions, I do not aim to ignore the importance of other types of active learning; instead, the goal is to constrain the space of connections between active and social learning theories. Moreover, children's action selection captures a rich set of behaviors, including pointing, eye movements, verbal question asking, and causal interventions. Finally, focusing on active decisions connects work on children's learning to a rich tradition of computational and experimental research in the fields of machine learning, decision theory, and statistics.

The idea that children's actions are important for cognitive development has also been an influential aspect of both classic [e.g., @bruner1961act; @berlyne1960conflict; @piaget1952origins] and modern [@schulz2012origins; @gopnik1999scientist] theories of learning. Moreover, the effects of active processes have been studied in education [@grabinger1995rich; @prince2004does], machine learning [@settles2012active; @ramirez2017active], and cognitive psychology [@castro2009human; @chi2009active]. A common thread across these diverse bodies of work is that active contexts lead to different (and often more rapid) learning outcomes because they (a) enhance learners' attention and memory and (b) allow learners to structure experiences that are tuned to their own goals, beliefs, and capabilities (see @markant2016enhanced for a review).

One compelling example of how to explore the effects of self-directed choice comes from @markant2014deconstructing's study on "deconstructed" active learning. Adults were asked to memorize the identities and locations of objects hidden in a grid and given different levels of control. They could select: (1) next location to search, (2) item to reveal, (3) duration of the trial, or (4) time between trials. @markant2014deconstructing also included a "yoked" control group who saw the same training data that was generated by the active learning group, thus equating the experience while varying the level of control. Across all conditions, there was a memory advantage for active control, providing evidence for the benefits of being able to coordinate the timing of information with internal attentional processes.

Research on language comprehension has also varied levels of active control to tease apart attentional vs. informational effects. For example, @schober1989understanding asked participants to use language to direct another person on how to arrange a set of geometric objects (that did not have familiar labels) in a 4x4 matrix. Critically, the listener could either: (1)  talk to the director, (2) listen to a recorded conversation and pause the recording, or (3) listen to the recording but not stop it.  Adults who participated in conversation performed better than participants in both passive listening contexts. And the capacity to control the timing of the recording did not improve accuracy, suggesting that active participation in conversation provides an informational advantage such that people could clarify intended meanings before misunderstandings became an issue for later comprehension.

Developmental experiments have found active learning advantages. For example, @ruggeri2016active found that control over the timing of new information led to better spatial memory in 6- to 8-year-olds [@ruggeri2016active]; @partridge2015young showed similar effects in the domain of word learning (see also @kachergis2013actively for evidence in adults); and @schulz2012origins found that active learning supports preschoolers' understanding of new causal structures. Finally, 16-month-olds show better memory for objects they pointed to compared to an object that they had not actively engaged with [@begus2014infants] (see also @stahl2015observing) and adults tend to produce more labels for objects that their infants point to [@wu2015caregivers], providing additional evidence that even young infants can generate actions that elicit information to support their learning.

Research on infants' selective visual attention provides a final compelling example of children's capacity to select useful information.  For example, @kidd2012goldilocks found that 7- and 8-month-olds' prefer to direct gaze at stimuli with intermediate levels of complexity, looking away when the stimulus was either highly predictable or highly surprising (see also  @kidd2014goldilocks for evidence in the auditory domain).  Moreover, @gerken2011infants found that 17-month-olds increase attention to a stream of input that was learnable but would disengage if the input did not have any stable structure to extract.  

### The scope of the integrative account

In sum, the empirical work reviewed above shows that both social and active processes can influence learning by enhancing attention/memory, changing inferential processes, and by generating useful learning input. The rest of this chapter presents an integrative account that we scope to focus on children's active learning *decisions* within social contexts. We argue that this is a useful step forward because it allows researchers to ask how specific pieces of social learning affect separate underlying components of decision making.

One major challenge for integrating these two proposals is the large number of factors that could influence how active learning interacts with social reasoning, which in turn creates an extensive space of possibilities for researchers to test. One way to constrain this problem is to use a formal model of information seeking that take an ideal-observer approach [@geisler2003ideal]. The ideal-observer model defines the structure of the learning task and asks how well learners can take advantage of the information in the environment. This approach pushes researchers to explicitly specify the processes of active and social learning as separable, underlying components, which can then become targets for empirical work. 

Research in cognitive psychology has used the ideal-observer approach to understand human active learning. One particularly useful model has been a formal account of scientific reasoning named Optimal Experiment Design (OED). The OED model was initially designed to help scientists select the best experiment from the set of possible experiments, where "best" means the experiment leading to the most information gained. Researchers have used this formalization to ask whether people's information-seeking behaviors match predictions from OED models. 

Moreover, OED has the benefit of using the same mathematical framework as recently-developed models of social learning: Bayesian models of learning, teaching, and communication [@shafto2012epistemic; @frank2009using; @goodman2016pragmatic]. These parallel formalizations suggest a productive way to integrate active and social learning theories. This point is the primary focus of the integrative account that we present in [Part III](#active_social) of this chapter. Before discussing the details of the account, I briefly review the OED formalization and evidence for OED-like reasoning in human information seeking.  


## Part II: A formal account of active learning {#oed}

Optimal Experiment Design (OED) [@emery1998optimal; @nelson2005finding; @lindley1956measure] is a statistical framework for quantifying the usefulness of experiments. @lindley1956measure described the approach as a transition from viewing statistics as binary decision making to a practice of gathering information about the "state of nature" (p. 987). The concrete proposal is to design studies that maximize expected information gain (a measure borrowed from Information Theory and discussed in more detail below) and continue to collect data until the information gained reaches a pre-determined threshold.

The OED approach allows scientists to make design choices that maximize the effectiveness of their experiments, reducing inefficiency and cost. Consider the following toy example borrowed from @ouyang2016practical where a researcher is interested in designing the best experiment to figure out whether people think a coin is fair or biased (i.e., a trick coin). Here the researcher's hypotheses correspond to different models of the coin [$M_{fair}: Bernoulli(p = 0.5)$] and [$M_{bias}: Bernoulli(p)$ where $p \sim Uniform(0,1)$] and the experiments correspond to different sequences of coin flips that she could select as stimuli. Imagine that the researcher has limited time or resources and can only show a sequence of four coin flips, creating a space of 16 possible experiments. An OED model allows the researcher to select the best experiment that maximally differentiates the two hypotheses. For example, OED provides an answer to the question: how much better would it be to use [$HHHH$] versus [$HTHT$]? Here, [$HHHH$] is more informative because both the bias and the fair coin models make the same predictions for the [$HTHT$] experiment, meaning we would not learn much from this test.

```{r word-learn-schematic, fig.cap = "Schematic of an active word learning context using the decomposition of Optimal Experiment Design. Social input (hearing a new word) triggers an inquiry goal. Then the learner considers potential hypotheses for the candidate word-object links, weighting each hypothesis by its prior probability. In this case, the learner thinks that the new word is less likely to refer to the familiar object BALL. Next, he considers possible queries (actions) and the potential outcomes of those actions. In the word learning context, the child must direct queries towards a social partner, which provides the learner with more possible queries: both verbal (questions) and nonverbal (eye gaze; pointing). If the learner selects the action to maximize expected utility, then he would ask the most informative question, which removes all uncertainty for the meaning of 'Dax' -- 'What's that called?' If he does select the relatively less informative action of asking about a single object, he would be unlikely to ask about the familiar object BALL since there is less information to be gained from this query based on his prior beliefs.", fig.scap="Schematic of an active word learning context."}

grid::grid.raster(png::readPNG(here::here(intro_figs_path, "word_learn_schematic.png")))
```

@nelson2010experience demonstrate the usefulness of taking an OED approach for differentiating competing theories of information seeking in adults' category learning. They created an OED model of their task, which included the design choices (what combination of features to show participants) and the relevant behavioral hypotheses (the different theories of category learning). They used the model to simulate the outcomes of using different stimulus sets, allowing them to choose stimuli for which the competing theories made different predictions, and thus speeded the rate of learning from their experiments.

@coenen2017asking provide a thorough review of the OED framework and its links to human information seeking. They describe the four parts of an OED model, which are necessary to compute the expected value of an action: (1) hypotheses, (2) queries, (3) a generative model of the types of answers that each query could elicit, and (4) a way to score each answer with respect to the learning goal. There are also two components that are external to the utility computation but important for an account of human inquiry. First, having a learning goal, which instantiates the process of reasoning about hypotheses, questions, and answers. And second, having a stopping rule, which refers to a threshold that causes the learner to stop seeking information and generate an action. Part III defines each component of the OED model, and the mathematical details can be found in the Appendix for this chapter.

### Evidence of OED-like reasoning in human behavior

A growing body of psychological research has used the OED framework as a metaphor for active learning. The proposal is that people make decisions, they engage in a similar process of evaluating the usefulness of different actions relative to their learning goals. Using this evaluation process, learners can then select behaviors that maximize the potential for gaining information. One of the successes of the OED account is that it can capture a wide range of information seeking behaviors, including verbal question asking [@ruggeri2015children], planning interventions in causal learning tasks [@cook2011science], and decisions about where to look during scene understanding [@najemnik2005optimal]. Figure\ \ref{fig:word-learn-schematic} shows a schematic overview of how OED principles shape the learning process for the task of word learning.

One compelling use case of OED metaphor as a model of human behavior comes from @nelson2005finding's study of eye movements during concept learning. Their model combined Bayesian probabilistic learning, which represents current knowledge as a probability distribution over concepts, with an OED model that calculated the usefulness of different patterns of eye movements. They modeled eye movements as question-asking to gather visual information about the target concept. @nelson2005finding found that participants' eye movements aligned with predictions from the OED model. Specifically, participants changed the dynamics of eye movements depending on how well they learned the target concepts. Early in learning, when the concepts were unfamiliar, the model generated a broader, less efficient distribution of fixations to explore all candidate features that could be used to categorize the stimulus. However, after the model began to learn the target concepts, eye movement patterns shifted to become more efficient and focused on a single stimulus dimension to maximize accuracy. This shift from exploratory to efficient eye movements matched adult performance on the task, suggesting that people's behavior was sensible given the structure of the learning problem and the uncertainty in the context.

Developmental work has used OED models to ask whether children are capable of selecting useful behaviors that maximize learning goals. For example, @legare2013use found that 4- to 6-year-old children consistently asked yes/no questions to figure out the identity of an object hidden in a box. Children produced a high proportion of questions that generated useful, constraining information (e.g., "Is it red?") as opposed to questions that provided redundant information (see also  @mills2011determining; @mills2010preschoolers). 

Children are also capable of generating efficient actions to learn about the causal structure of objects. For example, @cook2011science found that preschoolers were capable of designing good tests for successfully distinguishing between different hypotheses for how to activate a music box. Moreover, children's behaviors suggested that they were reasoning about a decision that would influence their future opportunity to generate useful information, providing a compelling example of OED-like reasoning in early learning.

Although the OED approach has provided a formal account of seemingly unconstrained information seeking behaviors, there are several ways in which it falls short as an explanation of self-directed learning. @coenen2017asking argue that OED models make several critical assumptions about the learner and the learning task, including (1) the hypotheses/questions/answers under consideration, (2) that people are actually engaging in some expected utility computation in order to maximize the goal of knowledge acquisition, and (3) that the learner has sufficient cognitive capacities to carry out the calculations. 

In the next section, I argue that the limitations of the OED approach can be productively reconstrued as opportunities for understanding how learning from other people could scaffold children's active learning. We focus on integrating research and theory on social learning with five critical components of the OED model: goals, hypotheses, questions, answers, and stopping rules (see Figure\ \ref{fig:integrative-schematic} for a schematic overview of the account). 

## Part III: Information seeking within social contexts {#active_social}

Why connect active learning processes with social learning effects? First, children do not re-invent knowledge of the world, and while they can learn a tremendous amount from their actions, much of their generalization and abstraction is shaped by input from other people. Moreover, social learning can be the only way to learn something (e.g., first language acquisition). Finally, children are often surrounded by parents, other adults, and older peers – all of whom may know more about the world than they do, creating contexts where the opportunity for social learning is ubiquitous. 

Second, there is a body of empirical work showing that active learning can be biased and ineffective in systematic ways. For example, work by @klahr2004equivalence found that elementary school-aged children were less effective at discovering the principles of well-controlled experiments from their self-directed learning, but were capable of learning these principles from direct instruction. @markant2014better showed that active exploration provided no benefit over passive input in category learning when there was a mismatch between the target concept and adults' prior hypotheses going into the learning task. And @mccormack2016children found that 6-7 year-olds showed no benefit from active interventions on a causal system compared to observing another person perform the interventions.

In a comprehensive review of the self-directed learning literature, @gureckis2012self point out the learner’s understanding of the task determines the quality of active exploration: if the representation is weak, then self-directed learning will be biased and ineffective. @coenen2017asking pursue this line of argument even further, proposing a set of specific challenges for research on active learning. Here is a sample of those open questions that are most relevant to the ideas in this chapter:

  *  What triggers inquiry behaviors in the first place?
  *  How do people construct a set of hypotheses?
  *  How do people generate a set of queries?
  *  What makes an answer good?
  *  How do people generate and weight possible answers to their queries?
  *  How does learning from answers affect query selection and belief change?

\noindent
In this section, I argue that ideas from research on social learning can address these challenges. We start from the OED model and use it as a conceptual tool to integrate social contexts and active learning. The contribution of this formalization is that it makes the different components of active learning explicit while highlighting the aspects that might be particularly challenging for young learners. Moreover, the "challenges" to the OED account can be reconstrued as opportunities for understanding the benefits of learning from other people. In each of the following sub-sections, I define the challenge for active learning, discuss how social contexts could address it, and highlight prior or future empirical work that connects active and social learning accounts (see Figure\ \ref{fig:integrative-schematic} for an overview).

```{r integrative-schematic, fig.cap = "Schematic of active learning within a social context. Each panel shows how social information could influence a different component of the active learning process. These social effects occur in-the-moment of learning or over developmental time. Also, the cause of the social effect varies from the mere presence of another person to triggering a sophisticated psychological reasoning process about others' goal-directed behaviors. Note that the panels correspond to the different sub-sections in Part IV of the text.", fig.scap="Schematic of the integrative account of active learning within a social context."}

grid::grid.raster(png::readPNG(here::here(intro_figs_path, "integrative_schematic.png")))
```

### Goals

In the OED framework, an inquiry goal refers to the underlying motivation for information seeking. Researchers often operationalize these goals as a search for the target hypothesis amongst a set of candidate hypotheses. Some examples of inquiry goals that children might hold are:

  * What is this speaker referring to? (word learning)
  * What types of objects are called "daxes?" (category learning)
  * How does this toy work? (causal learning)
  * Is this person reliable? (selective learning)

\noindent
Specifying learning goals is essential since without them the learner will struggle to evaluate whether an action leads to progress. @coenen2017asking illustrate this point by saying,

> The importance of such goals is made clear by the fact that in experiments designed to evaluate OED principles, participants are usually instructed on the goal of a task and are often incentivized by some monetary reward tied to achieving that goal. Similarly, in developmental studies, children are often explicitly asked to answer specific questions, solve a particular problem, or choose between a set of actions. (p. 32-33)

\noindent
Characterizing children's goals, however, is not trivial since they could consider a range of goals at any moment with no guarantee that learning progress is one of them. One line of theorizing about the OED hypothesis argues that useful information seeking should only occur in the presence of precise tasks and goals. Consider the example of a parent handing their child a new toy with several buttons on it and saying, "Let's figure out how this toy works!" In this case, it becomes possible to ask whether the child selects actions that are more or less useful for increasing their knowledge of the toy's causal structure. 

This example illustrates how other people can trigger learning goals. Empirical work shows how the actions of a social partner can increase children's tendency to detect their uncertainty (see @lyons2010metacognitive for a review). The upshot of this research is that children's ability to realize when they do not know something is relatively slow to develop. For example, @markman1979realizing showed that elementary school-aged children were unable to detect apparent inconsistencies in written paragraphs (e.g., "fish can't see without light, and there's no light at the bottom of the ocean, but some fish at the bottom of the ocean only know their food by its color."). Interestingly, if the experimenter gave children an explicit warning or challenge to find a problem with the essay, then they were more likely to monitor their uncertainty and asked more clarifying questions. This finding can be reconstrued as an effect of the social context, shifting children's expectations, highlighting the learning goal, and facilitating their information seeking actions. Converging evidence comes @kim2016young, who showed that 3- to 4-year-olds are more likely to monitor their uncertainty about the contents of an opaque box when they were told that they would have to teach another person about the contents of the box (see also @lombrozo2006structure). In this case, the anticipation of social interaction may have increased children's tendency to focus on their goal to learn the identity of the objects.   

In addition to triggering inquiry goals, social partners can directly communicate the *value* of learning goals relative to the other goals that children may pursue. This connection draws on theoretical and empirical work exploring how children's environments can shape their intuitive frameworks for processing information and generating goals [@dweck1988social]. Under these accounts, children's beliefs about the malleability of traits influence whether they focus on taking actions that increase their competence (prioritize learning) or that demonstrate their fixed abilities (prioritize performing). Empirical work shows that when adults use language to emphasize a learning goal (e.g., "If you pick the task in this box, you'll probably learn a lot of new things." vs. "If you pick this box, although you won't learn new things, it will really show me what kids can do."), then children tend to select the more difficult task [elliott1988goals]. Moreover, both lab-based experiments and observational work provide evidence that the language adults use when praising children influences their tendency to adopt inquiry goals [@cimpian2007subtle; @gunderson2013parent]. 

While social partners can emphasize learning, the presence of another person can also engage learners' psychological reasoning about their mental states. This reasoning process can then elicit social goals that take priority over learning goals. Consider the "Goals" panel of the schematic active-social learning context shown in \@ref(integrative-schematic). If the learner is worried about what his social partner thinks of him, then he might prioritize actions that reduce the chance of appearing unknowledgeable and choose not to ask about the novel objects. Moreover, he could seek out easy tasks that demonstrate his competence at the expense of selecting actions that help him learn. The OED framework typically focuses on informational goals with progress measured as a reduction in uncertainty over candidate hypotheses. However, recent empirical and modeling work has begun to move beyond information-specific utility functions to include other goals that learners may hold (e.g., saving time, money, or cognitive resources) [meder2012information]. 

Recent work in modeling pragmatic communication ^[Rational Speech Act (RSA) framework for pragmatic reasoning. The RSA approach models language comprehension and production as, "a process of recursive reasoning about what speakers would have said, given a set of communicative goals" (p.819) [@goodman2016pragmatic]] provides a way to integrate social goals within the OED framework. For example, @yoonwon modeled speakers' decisions to use polite speech as opposed to direct speech (e.g., indirect language such as "we don’t think that dress looks phenomenal on you" as opposed to "It looks terrible") as a tradeoff between maximizing informational and social goals, showing that speakers are balancing these two when deciding what to say. 

In both OED and RSA, people are assumed to select actions that maximize utility, but the politeness model allows social information to play a role in the utility computation. Future research could adapt this utility-theoretic approach and model the effects of social contexts as changes to the weight children place on social goals, which, in turn, leads to selecting easier tasks where they can appear competent (see @yoon2018balancing for an example of this type of approach). This integration builds on the goal-orienting accounts reviewed above [@dweck1988social] since behavior is as an output of a mixture of goals as opposed to children holding either a performance or a learning goal.

Another open question about learning goals is how often children experience contexts where these goals are apparent or emphasized in their everyday experience. We do not yet have a reliable estimate of the prevalence of situations that would lead children to generate learning goals. One exception, however, is research on *guided participation*  by @rogoff1993guided provides evidence that parents from a diverse set of cultural backgrounds produce high rates of structuring and goal-orienting behaviors during activities such as cooking, shopping, working, etc. It is interesting to consider whether variability in children's exposure to goal-orienting behaviors could influence children's tendency to generate learning goals spontaneously.

### Hypotheses

Once children have a learning goal, the next step in the OED model is to figure out what hypotheses to consider. Intuitively, a hypothesis is a candidate explanation for how the world works. For example, consider the schematic learning context shown in \@ref(word-learn-schematic). Here, the child might generate the following hypotheses about the meaning of a new word "Dax": (1) Dax = object A, (2) Dax = object B, or (3) Dax = object C. ^[This hypothesis space is simplified since it only considers the possibility of one-to-one word-object mappings and that the new word refers to the co-occurring visual context.] 

The set of hypotheses under consideration is critical for quantifying effective self-directed learning in the OED account. The usefulness function of expected information gain (see Appendix A for details) works by comparing the learner's uncertainty over hypotheses before and after they see an answer. Without a defined hypothesis space, however, it is challenging to select the best action to reduce uncertainty. Put another way; the OED framework does not readily deal with situations where learners might have to consider a large space of hypotheses or might perform actions without considering any hypotheses at all. These challenges are especially relevant for developmental accounts that draw on OED principles since these scenarios are plausible for young learners. Social partners, however, can address this challenge by providing children with a constrained set of hypotheses that facilitate the comparison of different information-seeking actions.

Consider the case of children's early word learning where even the simplest of words, concrete nouns, are often used in complex contexts with multiple possible referents, which creates the potential for an (in principle) unlimited number of hypotheses that children could entertain when trying to figure out word meanings [@quine19600]. Social-pragmatic theories of lexical development often start from the idea that adults constrain the learning task by providing social cues (eye gaze, pointing, etc.) that connect words to their referents during labeling [@clark2009first; @hollich2000breaking; @bloom2002children]. Some of our empirical work shows that the number and fidelity word-object hypotheses that learners store tracks with the strength of social cues available during the labeling moment [@macdonald2017social]. Other empirical work has found that children as young as 16 months prefer to map novel words to objects that are the target of a speaker’s gaze and not their own [@baldwin1993infants]. And analyses of naturalistic parent-child labeling events shows that young learners tended to retain labels accompanied by clear referential cues, which served to make a single object dominant in the visual field [@yu2012embodied]. 

Social input can also shape the hypotheses that children generate by revising their intuitive theories about the world. @gerstenberg2017intuitive describe an intuitive theory as, "an ontology of concepts, and a system of (causal) laws that govern how the different concepts interrelate..." (p. 3). Importantly, these theories shape how children interpret incoming information and, in turn, the set of candidate explanations they could explore. Empirical work on conceptual change across development has studied the ways that children integrate input from other people with their current theories [@gelman2009learning]. For example, elementary school-aged children tend to hold a mixture of beliefs about the shape of the earth, ranging from a flat earth theory to the adult-like, sphere model [@vosniadou1992mental]. Interestingly, some children hold intermediate beliefs such as a theory where there are two earths, suggesting that they actively integrate aspects of their initial theory with the information they get from other people (see @opfer2004revisiting for another example from intuitive theories of biological concepts). 

In sum,  children's candidate hypotheses can be shaped by social information. This effect can occur during the moment of learning (e.g., referential gaze during word learning) and over a developmental timescale (e.g., intuitive theory revision). Critically, social partners can facilitate active learning by constraining the set of hypotheses under consideration, which makes comparing the utility of information-seeking actions more tractable. An open question is how children's information seeking changes as a function of the size of the hypothesis space. Moreover, similar to the research on children's goals, it would be useful to move beyond lab-based studies and towards observational research that measures how children's everyday social interactions constrain the hypotheses they decide to target with their exploration behaviors. 

### Queries

Queries refer to the set of experiments that a scientist could conduct to gather information about their hypotheses. In children's active learning, queries are the set of actions they could take to collect information from the world. Empirical work on active learning has explored a variety of behaviors, including verbal questions, pushing a button to figure out how a toy works, and decisions about where to look. One of the strengths of the OED account is that it provides general principles that could explain such a wide range of behaviors. 

The challenge for young learners, however, is to discover what behaviors are available and figure out which of those actions are useful for learning. One way to address this challenge is for children to look to older peers and adults to figure out what actions can help them learn. Moreover, social learning contexts can change the space of possible queries by adding the option of seeking information from a social partner, which expands the set of possible learning-related actions children could take.

Research on children's verbal questions provides insight into how social partners could model useful queries. First, it is a truism that asking a question in natural language requires that children have acquired a conventionalized symbolic system, which must have been learned from social input. Second, both experimental work and corpus analyses provide evidence that children's question-asking becomes more varied and productive over the first years of life as they get exposed to more complex language input. Finally, observational studies have found that that parents' use of wh-questions predicts children's later vocabulary and verbal reasoning outcomes [@rowe2017going], and children of parents who were trained to ask "good" questions during book reading episodes at home had children who asked better questions during book reading sessions at school [@birbili2009helping]. One explanation for these associations is that wh-questions led children to produce more complex responses that build verbal abilities. Another intriguing causal pathway, however, is that the frequency and type of parents' questions provided children with a template for how to ask useful questions. 

Even if children can generate different queries, they still have to evaluate the relative usefulness of each action concerning their learning goal. Empirical work with adults shows a substantial gap between people's question-generating and question-evaluation skills. For example, @rothe2015asking used an OED model to measure the expected information gain of adults' natural language questions in a modified "Battleship" game and found that people rarely produced high information gain questions. In a follow-up experiment, however, @rothe2015asking showed that when a different group of adults had access to the list of questions generated by the participants in the unconstrained version, they were quite good at recognizing questions that would generate good information.

Developmental work provides additional evidence of this production-comprehension asymmetry in question asking. For example, children younger than the age of three have difficulty generating useful verbal questions compared to their older peers in lab-based experiments [@mills2011determining; @mills2010preschoolers], but even the youngest children in those studies are capable of comprehending information elicited by others' questions to succeed at parallel tasks [@mills2012little]. Moreover, @mills2011determining manipulated whether children were pre-exposed to adults who modeled useful queries and found that this led to even the youngest children producing useful questions at a much higher rate. Finally, converging evidence comes from research showing that direct instruction (i.e., understanding the objectives of inquiry and identifying useful questions) is necessary for elementary-school-aged children to develop skill in designing informative experiments for learning about physics concepts [@kuhn2008needs].

In addition to providing a model of queries, social contexts also expand the set of possible questions by adding a social target for information seeking actions. That is, the child has an additional choice: to gather information from the non-social world or other people. The "Questions" panel in Figure 3 shows a child playing with a set of concrete objects. If there is no social partner present, they could still interact with the objects to learn about their shape, texture, or functional properties. But if another person is present, the child now has the option to ask verbal questions or to seek information from the other speaker by gathering their nonverbal cues (e.g., pointing, eye gaze, or facial expressions). 

Recent empirical work has explored the factors that influence children's decisions to seek information from other people. For example, @fitneva2013development showed that children know when to query other people to gain information that they could not get on their own (e.g., invisible properties of a novel social category). Additional evidence comes from work by @lockhart2016could where they showed that 5- to 11-year-olds could reliably determine the kinds of things a person "growing up on their own" could learn from personal experience (that the sky is blue) vs. required interactions with other people (that the earth is round). Finally, work on children's help-seeking behaviors shows that both preschoolers and even infants seek help systematically when completing a task, turning to a social target to request information or acting on the world depending on which information source was more likely to help them achieve their current goal [@gweon201116; @vredenburgh2016young].

Some of our work has investigated how the presence of a social partner changes the set of information seeking behaviors available to the learner. By measuring changes in children's eye movements during familiar language processing, we asked how real-time information seeking adapts to support comprehension. We found that children who were learning a visual-manual language gathered more information before generating a language-driven gaze shift away from a signer as compared to children processing spoken language while fixating on a speaker [@macdonald2017info]. This result suggests that sign language learners were sensitive to the higher value of fixations in a visual-manual language where disengaging from the signer reduces access to any following linguistic information. We found a similar adaptation of information seeking in both children and adults' processing of spoken language within noisy acoustic environments where looking to a speaker's face provided visual information that could support the comprehension of the less reliable acoustic signal. Critically, listeners would not have had access to this information seeking action outside of a face-to-face, social interaction (e.g., listening to a noisy audio recording).

### Answers

Once the learner generates a set of possible queries, they can simulate the set of possible answers they could get in return. In the OED framework,  an answer is useful if it decreases the learner's uncertainty about their hypotheses. The challenge for the child as an active learner is two-fold: (1) figure out what which answers are likely for each query and (2) decide how much to update their beliefs after seeing an answer. In this section, we discuss how social contexts can affect each component of the answer-evaluation process.

Defining a "good" answer is challenging. Intuitively, a good answer provides the learner with information that they did not already know, that they were interested in learning, and that is likely to be useful beyond the current context. Even within the formal OED framework, there have been a variety of ways to instantiate this utility function (e.g., information gain, probability gain, and Kullback-Leibler divergence) [@nelson2005finding]. These information-theoretic utility functions take into account the learner's prior beliefs, which are represented as probability distributions over hypotheses and compute the effect of each answer on the learner's beliefs represented as a conditional probability distribution.

Social learning theories often start from the idea that interactions with other people increase the probability of getting useful information. For example, evolutionary models argue that knowledge transfer between generations allows for the gradual accumulation of small improvements that eventually led to sophisticated tools, beliefs, and practices that would be difficult, if not impossible, for any individual to discover on their own [@kline2015learn]. @boyd2011cultural provide the example of a hunter stumbling across the link between the color/texture of ice and its stability, saying that this type of rare information would be much harder for individuals to re-discover on their own. But social transmission allows humans to pass these discoveries down to subsequent generations, allowing humans to move beyond the information that the world is likely to provide.

@csibra2009natural's theory of "Natural Pedagogy" argues that an assumption of *generalizability* is a fundamental component of the answers that children get when they interact with adults. Under their account, when adults provide ostensive cues (eye gaze or child-directed speech) to signal generalizable knowledge children update their beliefs differently. Empirical work shows that infants are more likely to generalize the valence of an object to a new person when learning in the presence of an ostensive, pedagogical cue [@gergely2007pedagogy]. Moreover, infants are more likely to encode the stable features of an object, as opposed to its location in space, if a communicative signal such as a point guided their attention to that object [@yoon2008communication].

In addition to an increased chance of seeing generalizable information, features of the social context can also modulate the way active learners evaluate possible answers. This link is one of the more developed connections between the OED and social learning accounts. That is, researchers have made progress in modeling the influence of different assumptions that a learner could make about the process through which other people generate answers. @shafto2012learning describe these different sampling assumptions, placing them along a continuum that varies regarding how much a learner should update their beliefs:

  * *Weak sampling*: answers generated at random from the set of all possible answers (independent of target hypothesis)
  * *Strong sampling*: answers generated at random from the set of answers that are true of the correct hypothesis (linked to target hypothesis)
  * *Pedagogical sampling*: answers generated that maximize the learner’s belief in the correct hypothesis (linked to target hypothesis and consider alternative hypotheses)
  
\noindent
If the learner assumes strong or pedagogical sampling, then they can make stronger inferences that speed learning. For example, if we see someone press two buttons to activate a device, we are more likely to think that both buttons were necessary if that person knew how the machine worked and wanted to communicate to us how it worked. Otherwise, if one of the buttons would have been sufficient, then it would not make sense for them to perform the less efficient action of pressing both buttons. The effects of these sampling assumptions are fundamentally psychological. They require the learner to reason about others' goals and to reason about whether other people are thinking about their intentions. ^[See the "Answers" panel of Figure\ \ref{fig:integrative-schematic} for an illustration of this recursive reasoning process within an active learning context.]

Empirical support for the pedagogical sampling account comes from a range of domains/tasks, including word learning [@frank2009using], pragmatic inference [@frank2012predicting], and causal reasoning [@bonawitz2011double]. These empirical findings connect directly to the OED model. Consider @xu2007sampling's finding that when a knowledgeable teacher generates object labels, learners assumed the examples indicated the true word meaning, making it more likely that the teacher would draw three samples from the broader, basic category (as opposed to the smaller subordinate category). They modeled this effect by modifying the likelihood function in a Bayesian cognitive model. In this case, the likelihood function for the teacher-driven condition was designed to capture the idea that learners should prefer more restrictive hypotheses if they are confident that the teacher generated labels based on the actual word meaning. This formalization makes direct contact with the OED model of human inquiry since learners consider how much answers will update their beliefs, capturing the idea that responses generated with the goal to teach carry more information.

Another line of empirical work has focused on children's decisions about whom to learn from. Even young infants are capable of *selective* learning, rejecting answers that conflict with their knowledge [@pea1982origins] and seeking information from people who tend to provide useful information in the past [@koenig2004trust]. For example, @chow2008see found that 14-month-olds are less likely to follow the gaze of a person who had consistently directed gaze towards an empty location. Moreover, children prefer to learn from familiar rather than unfamiliar adults [@corriveau2009choosing], adults rather than peers [@rakoczy2010bigger], and ingroup rather than outgroup members [@macdonald2013my]. Moreover, @gweon2014sins found that 14-month-olds explore objects more after interacting with a teacher who had been under-informative in their previous demonstrations, providing evidence of an early ability to link the quality of answers to active learning decisions. 

Interestingly, the outcome measures in these studies of selective learning --  whom to direct questions towards or how long to explore a novel toy -- are information-gathering decisions. While this is an implicit link to the OED account, researchers have modeled selective learning phenomena as modifications to the likelihood function in Bayesian cognitive models. For example, @shafto2012epistemic developed a model in which children reason about both the helpfulness and knowledgeability of speakers when deciding whom to learn from and were able to capture several qualitative findings from the selective trust literature. This approach parallels the word learning and pedagogical sampling models reviewed above, highlighting how social reasoning could change the utility of the answers learners get from other people.

One candidate for future research is to ask how social contexts change children's decisions about whether to initiate information seeking behaviors in the first place. That is, if their social partners are unlikely to provide useful answers, then active learning (even if children are capable of selecting informative actions) becomes less valuable. The dual consideration of costs and benefits in active learning has been the focus of much research in machine learning, which tries to select the set of questions to ask taking into account how long it will take a human to respond [@haertel2008return]. Moreover, recent lab-based studies and theorizing in social cognition suggest that children are capable of "intuitive utility maximization" reasoning that others take actions to increase rewards while minimizing costs regarding time, effort, etc. [@jara2015children]. It would be interesting to bring these cost-based approaches to bear on questions about how social contexts modify children's active learning.

### Stopping rules

A stopping rule is a threshold that when exceeded causes the learner to stop gathering information and generate an action. These rules fall into two categories: information or time-based. For example, when searching for information on the internet, a learner might create the time-based stopping rule -- spend one hour searching -- or the information-based rule -- explore until we find the definitions that we need. The function of a stopping rule is to balance information gained with reducing unnecessary time/effort put into the search task. 

The challenge for both the child as active learner and researchers interested in explaining stopping rules is both operationalizing and estimating the critical pieces needed for developing a stopping rule: the rate of information gain and the cost of information search. To address this challenge, researchers have used ideas from theories of animal foraging to model adults' decisions of when to stop gathering information [@pirolli1999information]. For example, @manohar2013attention used a "patch" model to explain the timing of adults' decisions about when to fixate and re-fixate on one of two symbolic gambles displayed on a computer monitor. They proposed that fixating on an item results in a leaky gain in precision and that people should shift their gaze once their information gain rate falls below a pre-defined threshold (see also @hills2012optimal for evidence from semantic memory). Moreover, much progress has been made by modeling perceptual decisions as a noisy evidence accumulation process with responses generated when information crosses a pre-defined threshold [@ratcliff2008diffusion].

Social partners play a key role in children's decisions to stop information seeking since they are a valuable resource of information. Empirical work has primarily focused on how children persist in seeking information from social partners if their initial request is not satisfied. For example, @frazier2009preschoolers used a corpus analysis of parent responses to children's *how* and *why* questions and found that preschoolers were more than twice as likely to re-ask a question after getting a non-explanatory response (e.g., CHILD: "Why you put yogurt in there?" ADULT: "Yogurt's part of the ingredients") compared to an explanatory answer (e.g., CHILD: "How do you get sick?" ADULT: "we don't know.") (see also @deborah2004children). These studies suggest that even toddlers are sensitive to when they have gathered sufficient information to address their information seeking goals within social contexts. 

In addition to providing information, social partners can take actions that shape children's decisions about whether to persist in exploration. For example, @bonawitz2011double showed that preschoolers spend less time exploring an object and are less likely to discover alternative object-functions after an adult explicitly taught a single function [@bonawitz2011double]. Children's stopping behavior is reasonable since their social partner communicated that there was no other information to be gained by taking actions on the object. Moreover, @butler2012preschoolers showed that an adults' pedagogical demonstration led to an increase in children's object exploration when testing whether a hidden property (magnetism) generalized to a new but similar looking object. These results highlight the complex ways social interactions can modulate children's thresholds for ending their information search.

Our work on where children choose to look during real-time language comprehension could be construed as an effect of social contexts on children's stopping decisions [@macdonald2018noise]. We found that both adults and children fixate more on a speaker's face when processing familiar words in a noisy auditory environment, an adaptation that resulted in a higher proportion of gaze shifts to the named referent. We used a cognitive model of decision making (Drift-Diffusion Model @ratcliff2008diffusion) to provide evidence that an increase to listeners' decision thresholds, and not processing efficiency, best explained the behavioral results. This approach provides an example of bringing cognitive models of decision making into contact with empirical questions about children's language comprehension within face-to-face social interactions.

Another promising approach for future research is to ask how children's developing capacity to reason about the cost of actions changes their active learning behaviors. In the OED framework, cost (e.g., monetary value of running an additional experiment) is critical to deciding when to stop gathering additional information, but this is complex to operationalize in human information seeking. However, there has also been a growing interest in developing "cost-sensitive" active learning algorithms in the field of machine learning [@haertel2008return], with researchers beginning to define costs in increasingly sophisticated ways. For example, @settles2008active point out that the cost of information gathering should not be measured as a reduction in the number of training trials if those training trials vary in length because specific questions are more challenging to answer. 

An important next step to understanding children as efficient active learners is to explore who they balance the desire want to ask questions that maximize information gain while taking into account the cost incurred by others (e.g., time or mental effort) to provide that information. This idea is fundamentally psychological in that it expands the utility computation to include some measure of how our behavior affects others' actions and mental states. This line of research falls directly out of an integrated active-social learning framework.

## Conclusions: Eye movements as a case study

In this chapter, we presented concrete definitions of active and social learning and described a unifying framework of information seeking within social learning contexts. We used Optimal Experiment Design (OED) as a theoretical tool to propose that the presence of another person can affect children's information seeking by:

  1. instantiating learning goals, communicating the value of learning goals, or triggering social goals
  2. constraining the hypothesis space
  3. modeling useful queries
  4. providing useful answers
  5. changing thresholds for stopping information seeking

\noindent
The account described in this chapter argues that the social and active learning theories have much to be gained from considering the other. Active learning accounts will benefit by understanding how learners incorporate social information into their decision making, allowing researchers to develop more sophisticated utility functions that might better capture what people care about when learning something new. This approach seems especially crucial for characterizing children's active learning since observational studies of learning environments suggest that opportunities to learn from social interaction are ubiquitous. 

On the other hand, researchers interested in social learning phenomena can benefit from advances in the study of active learning by connecting their ideas to the rich traditions of machine learning, decision theory, and statistics. Moreover, research on social learning phenomena often uses information-seeking decisions as dependent variables in experiments. Thus, a secondary benefit would be a better understanding of the factors that influence the measurement of social learning effects.

Finally, the evidence reviewed in this chapter shows that research has mostly focused on lab-based experiments where social and active learning effects are measured in isolation during highly constrained task settings. An important next step is to estimate the presence of learning goals, tractable hypothesis spaces, and the quality of answers in children's everyday experiences. This line of inquiry will require a shift from relying on highly-controlled lab experiments to leveraging large-scale, observational datasets. And while this approach adds complexity, I think that the benefit will be a far greater understanding of how children's active learning operates over fundamentally social input.  

The rest of this thesis presents a series of empirical studies of familiar language comprehension and novel word learning, which we situate within the integrative framework presented in this chapter. The majority of the experiments use eye movements as a case study of children's early information seeking. Eye movements are well-suited for studying the connection between active processes and social contexts because (1) visual attention is important for early lexical learning, (2) control over gaze is earlier to develop as compared to other forms of information seeking (e.g., verbal question asking), and (3) there is already a body of work that had characterized visual fixations as a form of question-asking in research on goal-based vision [@hayhoe2005eye]. 

At the beginning of each chapter, I show a schematic overview of the link between the integrative framework and each case study, and I highlight the relevant piece of the broader framework that the empirical work addresses. Chapter 2 investigates how children decide where to look while comprehending a visual-manual language (American Sign Language: ASL). In the grounded, sign processing context, children must use visual fixations to gather information about the referents and the linguistic signal, creating competition for visual attention (i.e., queries) that is not present in spoken language comprehension. 

Chapter 3 builds on the sign language work and directly compares the gaze dynamics of children learning ASL to children learning spoken English during familiar language processing. Specifically, we measure when children decide to stop fixating on a social partner to seek named referents in the visual world (i.e., stopping rules). Chapter 3 also describes a study of English-learning children and adult's eye movements in noisy auditory contexts, which could make the visual information gathered from looks to a social partner (i.e., answers) more useful for language understanding.

Chapters 4 and 5 explore how the information seeking framework generalizes to processing words in the context of social cues to reference. In Chapter 4, we present a series of large-scale word learning experiments, showing that the presence of a social cue modulates how much information (i.e., answers) adults remember from labeling events. Finally, Chapter 5 describes a set of eye-tracking studies that measure how children's decisions to stop gather information from a social partner (i.e., stopping rules) changes as a function of (a) whether the social partner provides a cue to reference (i.e., answers) and (b) their knowledge of the word-object mappings (i.e., hypotheses). 

The goal of the empirical work is to ask how children's gaze patterns adapt to a diverse set of contexts that change the value of seeking information from social partners. The common thread across this research is that children's real-time visual information seeking is quite flexible and can adapt to the informational structure of the environment to support efficient language processing.