```{r, include=FALSE}
knitr::opts_chunk$set(echo = F, cache = T, warning=F, message=F, 
                      fig.width=4, fig.asp = 0.618, out.width = "95%", 
                      fig.align = 'center', fig.pos = 't')

source(here::here("index/disseration_helpers.R"))
intro_figs_path <- "index/chapter_child_rmds/Active-social/figs/"
```

## Introduction

The rate of children's early cognitive development is remarkable. Consider that children, despite limitations on their processing capabilities and ambiguity in the input, rapdily acquire new lexical concepts, eventually reaching an adult vocabulary ranging from 50,000 to 100,000 words [@bloom2002children]. And they accomplish this all while also developing motor skills, learning social norms, and building causal knowledge. How can we explain children's prodigious learning abilities?  

Social learning accounts point out that children do not solve these problems on their own. Instead, they are typically surrounded by parents, other knowledgeable adults, or older peers -- all of whom are likely to know more than they do and want to facilitate their learning. Social learning accounts also emphasize how social contexts can bootstrap children's learning via several, distinct mechanisms. For example, work on early language acquisition shows that social partners provide input that is tuned to children's cognitive abilities [@fernald1987acoustic; @eaves2016infant], that guides children's attention to important features in the world [@yu2007unified], and increases levels of sustained attention, which results in better learning outcomes [@yu2016social; @kuhl2007speech]. 

Social contexts can also change the inferences that support children's learning from evidence. Recent work in the fields of concept learning and causal intervention suggests that the presence of another person engages a set of psychological reasoning where the learner thinks about *why* other people performed specific actions. The critical insight comes from knowing that another person has intentionally selected examples, which allows children to make stronger inferences that speed learning [@frank2009using; @bonawitz2016computational; @shafto2014rational]. For example, children learn at different rates after observing the same evidence depending on whether they thought the actions that generated that evidence were accidental (less informative) or intentionally selected (more informative). Moreover, adults and children will make even stronger inferences if they believe that another person selected their actions with the goal of helping them to learn (i.e., teaching) [@shafto2012learning].

However, children are not passive recipients of information -- from people or the world. Instead, they actively select behaviors -- for example, asking questions or choosing where to allocate visual attention -- that can change the content, pacing, and sequence of their learning experience. Recent theories of cognitive development have proposed the metaphor of the "child as scientist" and characterized early learning as a process of exploration and hypothesis testing following principles of the scientific method [@gopnik1999scientist; @schulz2012origins]. Moreover, empirical work across a variety of domains -- education [@grabinger1995rich], machine learning [@settles2012active; @castro2009human], and cognitive science [@markant2014better] -- has directly compared learning trajectories in self-directed contexts (active learning) as compared to settings where the learner has less control (passive learning). The upshot of this work is that active contexts often lead to faster learning because of enhanced attention and arousal or because the learners selects information that is closely linked to their current goals, beliefs, and interests (see @gureckis2012self for a review). 

Thus, children are capable of selecting actions that support their own learning, and a large body of work shows that social partners can create particularly good contexts for learning. This research, however, has often proceeded in parallel, focusing on the isolated effects of either active or social processes on children's learning. This stands in contrast to the ecological context in which language acqusition unfolds. That is, children acquire their first language from interactions with other people. And in these social interactions, they they are able to select actions -- where to look, where to point, what question to ask -- that influence the content and pacing of conversation. Taken together, these facts about the ecological context in which children learn highlight the need for integration across the active and social theoretical accounts. 

But how can we begin to integrate these two proposals, which often contain definitional issues and a lack of formal foundations? In this chapter, I argue that a formal integrated account of active learning within social contexts is an important step towards a more complete account of early cognitive development. To connect the active and social learning proposals, I use the computational frameworks of Optimal Experiment Design [@emery1998optimal; @lindley1956measure] and Bayesian models of social reasoning [@@goodman2016pragmatic]. The key insight is that the presence of another person can modulate the *availability* and *usefulness* of different actions that the active learner could select. Specifically, social interactions can shape learners' goals, hypotheses, actions, answers, and decisions about when to stop gathering information.

The chapter is organized as follows. First, I provide definitions of active and social learning to clarify the behaviors and phenomena that the integrative account can address ([Part I](#scope)). Then, I review the theory of Optimal Experiment Design (OED) ([Part II](#oed)), highlighting its role as a formal framework for understanding human active learning. I also discuss the behavioral evidence for OED-like reasoning in both adults' and children's learning. Finally, I conclude by presenting an integrative account of how social contexts can shape active learning ([Part III](#active_social)). In the final section, I also highlight a series of novel links between the social and active accounts, which present a way forward for empirical work that could shed light on how children's active learning processes operate over fundamentally social input.

## Part I: Learning on your own and learning from others {#scope}

A diverse set of scholars, theories, and empirical work has considered the contributions of active and social processes to children's learning. One consequence of this range of approaches is that the terms "active" and "social" have become associated with a vareity of meanings. Before integrating the two accounts, it is worth defining what we mean by active learning and social contexts. By providing definitions, this section aims to clarify the behaviors and phenomena that the integrative account attempts to explain.

### Social learning

Learning can be social in a variety of ways. First, children could learn with another person present but without attending to or directly interacting with them. Research in social psychology shows that the mere presence of other people can facilitate performance of simple tasks and impair the performance of complex tasks [@uziel2007individual; @cottrell1968social]. Second, children could learn by looking to others as a guide by observing or imitating their behavior. In fact, children's capacity for faithful imitation is a critical feature separating human from non-human learning [@call2005copying]. Finally, children could both attend to the person and directly interact with them, entering a communicative learning context that engages  psychological reasoning processes that alter the course of learning [@shafto2012learning; @frank2014inferring; @goodman2016pragmatic]. 

For this integrative account, I define a social context as a learning environment where another agent is present. This definition includes all of the social learning behaviors -- observation, imitation, and learning from direct interaction -- discussed above. This broad definition highlights the diverse pathways through which social information could interact with children's active learning. Moreover, this definition captures the diverse set of ecological contexts in which children develop, where in some cultures children experience high amounts of child-centered interactions while in others contexts they are expected to learn mostly through observation [@rogoff1993guided].

Social learning theories emphasize that children's rapid conceptual development is facilitated by the uniquely human capacity to transmit and acquire information from other people. A primary benefit of learning from others is that children gain access to knowledge that has accumulated over many generations; information that would be far too complex for any individual to figure out on their own [@boyd2011cultural]. In addition to the cumulative effects, social contexts facilitate in-the-moment learning since more knowledgeable others can select input that is most useful for children's learning [@shafto2012learning; @kline2015learn] and information that is likely to generalize beyond the current context [@csibra2009natural].

There is a large body of empirical work on social learning across a variety of domains including language acquisition, causal learning, and concept learning. For example, newborn infants prefer to look at face-like patterns compared to other abstract configurations [@johnson1991newborns; @farroni2002eye], to listen to speech over non-speech [@vouloumanos2007listening], their mother's voice over a stranger's [@decasper1987human], and infant-directed speech over adult-directed speech [@cooper1990preference; @pegg1992preference; @fernald1987acoustic]. Moreover, these attentional biases lead to differential learning in the presence of another person. 4-month-olds show better memory for faces that gazed directly at them [@farroni2007direct], for an object if an adult gazed at that object during learning [@reid2005adult; @cleveland2007joint], and perform better at tasks such as word segmentation from infant-directed speech compared to adult-directed speech [@thiessen2005infant]. @kuhl2007speech refer to these effects as "social gating" phenomena since the presence of another person activates or enhances children's underlying computational learning mechanisms. 

In addition to enhancing attention and memory, social contexts can facilitate learning by generating useful information that is tailored to the child's current developmental stage [@vygotsky1987zone]. Empirical work shows that caregivers alter their communication style when speaking to children (e.g.,exaggerating prosody, reducing speed), which in turn can help children learn vowel sounds [@adriaans2017prosodic; @de2003investigating], segment the speech stream [@fernald1991prosody; @thiessen2005infant], recognize familiar words [@singh2009influences], and learn new lexical concepts [@graf2013infant]. Additional evidence comes from @goldstein2008social's study where they found that infants modified their babbling to produce more speech-like sounds after interacting with caregivers who provided contingent responses, suggesting that contingent, social input was particularly useful because it was closer in time and easier to compare discrepancies between the child's vs. adult's speech sound. Finally, converging support comes from research on children's early word learning, which shows that social partners actively reduce the complexity of the visual scene by using gaze/pointing/holding actions to make a single object dominant in the visual field [@yu2013joint; @yu2005role] and by producing labels for objects that children are already attending to (i.e., "follow-in" labeling) [@tomasello1986joint].

Anbother feature of social interactions is that other people's actions are not random; instead they are intentionally selected with respect to some goal (e.g., to communicate information). And if children are sensitive to *why* someone else performed an action, they can use this information to facilitate learning. Recent empirical and modeling work has formalized this idea as a process of belief updating that is dependent in Bayesian models of cognition [@shafto2012learning; @frank2014inferring; @goodman2016pragmatic]. For example, adults are more likely to think that pressing both buttons is necessary to activate a toy if that action was demonstrated by someone who knew how the toy worked as compared to the same action but demonstrated by someone accidentally pressing the buttons [@goodman2009cause]. @shafto2012learning interpreted these results as a psychological reasoning process such as: "if the other person were knowledgeable and wanted to generate the effect, then he would perform both actions." This finding also suggests that learners assume that others' goal-directed behaviors will be efficient and they should avoid performing unnecessary actions (e.g., pressing two buttons when pressing one would have been sufficient). 

Similar effects of psychological reasoning on inference occur in word learning [@xu2007word; @frank2014inferring], selective trust in testimony [@shafto2012epistemic], tool use [@sage2011disentangling], and concept learning [@shafto2014rational]. Moreover, there is evidence that even young learners' inferences are sensitive to the presence of goal-directed behaviors. For example, @yoon2008communication showed that 8-month-olds encode an object's identity if attention was directed by a communicative point, but they will encode an object's spatial location if attention was directed by a non-communicative reach. And @senju2008gaze found that infants will follow another person's gaze only if the gaze event was preceded by relevant, communicative cues (e.g., infant-directed speech or direct eye contact). 

Finally, information learned from other people is more likely to generalize beyond the current context. Several accounts of cultural learning argue that an assumption of *generalizability* is fundamental to the human communication system and allows for the accumulation of cultural knowledge [@csibra2009natural; @kline2015learn; @boyd2011cultural]. In these explanations, adults generate ostensive signals such as direct gaze, infant-directed speech, and infant-directed actions, which, in turn, direct infants' attention and bias them to expect generalizable information. Experimental work testing predictions of a "Natural Pedagogy" account shows that children tend to think that information presented in communicative contexts is generalizable [@yoon2008communication; @butler2012preschoolers], and corpus analyses show that generic language (e.g., "birds fly") is common in everyday adult-child conversations [@gelman2008generic].

The work on social learning reviewed in this section highlight several points that are important for theories of cognitive development. First, from an early age, children are surrounded by other people who know more than they do. Moreover, these more knowledgeable others are invested in children's development and can provide good learning opportunities. Second, children are motivated to interact with other people, and these interactions engage and guide attention to relevant information. Finally, social contexts can trigger a set of psychological reasoning mechanisms that lead to stronger inferences, allowing children to get more information out of the same amount of input. 

However, social learning accounts often reflect a relatively passive construal of the learner. It is clear that children are not just passive recipients of input from the world or other people. Instead, they actively process information and select behaviors that change what they learn. A parallel body of research on this topic -- under the umbrella term of "active learning" -- has developed alongside social learning theories.

### Active learning 

Learning can be active in a variety of ways. First, a child could be physically active, and this movement could change what information they extract from the experience. There is a large body of research that explores the effects of action experience on infants' learning (see @kontra2012embodied for a review of work on embodied cognition). One classic example from @needham2002pick shows that infants who physically hold and manipulate objects will outperform a control group on measures of object attention and exploration. Second, active learning could refer to children's contribution to processing incoming information. For example, young learners do not just passively accept other people's claims and will reject answers that conflict with their knowledge [@pea1982origins]. Third, children might engage in self-generated active explanations. @lombrozo2006structure review evidence that 'self-explanation'can lead to better learning. Finally, active learning could refer to a decision-making process where children select, sequence, and pace their own learning experiences.

For the integrative account, I focus on active learning effects that arise via children's decisions about what action to take next. The key assumption is that active learners are trying to take actions that maximize the amount of information they can get in return. By scoping the account to decisions, I do not aim to ignore the importance of other types of active engagement; instead, the goal is to constrain the space of connections between active and social learning theories. Moreover, children's action selections capture a rich set of behaviors, including pointing, eye movements, verbal question asking, and causal interventions. Finally, focusing on active decisions connects work on children's learning to a rich tradition of computational and experimental research in the fields of machine learning, decision theory, and statistics.

The idea that children's actions are important for cognitive development has been an influential aspect of both classic [e.g., @bruner1961act; @berlyne1960conflict; @piaget1952origins] and modern [@schulz2012origins; @gopnik1999scientist] theories of learning. Moreover, the effects of active processes have been studied in education [@grabinger1995rich; @prince2004does], machine learning [@settles2012active; @ramirez2017active], and cognitive psychology [@castro2009human; @chi2009active]. One common thread across these diverse literatures is that active contexts lead to different (and often more rapid) learning outcomes because they (a) enhance learners' attention and memory and (b) allow learners to structure experiences that are tuned to their own goals, beliefs, and capabilities (see @markant2016enhanced for a review).

One compelling example of how to study these kinds of effects related to self-directed choice comes from @markant2014deconstructing's study of "deconstructed" active learning. Adults were asked to memorize the identities and locations of objects hidden in a grid and given different levels of control. They could select: (1) next location to search, (2) item to reveal, (3) duration of the trial, and/or (4) time between trials. @markant2014deconstructing also included a "yoked" control group who saw exactly the same training data that was generated by the active learning group, thus equating the experience while varying the level of control. Across the board, there was a memory advantage for active control, providing evidence for the benefits of being able to coordinate the timing of information with internal attentional processes.

Developmental experiments have shown similar active learning advantages. For example, @ruggeri2016active found that active control over the timing of new information led to better spatial memory in 6- to 8-year-olds [@ruggeri2016active]; @partridge2015young showed similar effects in the domain of word learning (see also @kachergis2013actively for evidence in adults); and @schulz2012origins found active learning benefits for preschoolers' understanding of new causal structures. Even 16-month-olds show better memory for objects they pointed to compared to an object that they had not actively engaged with [@begus2014infants].

### The scope of the integrative account

In sum, the empirical work reviewed in this section shows that both social and active processes can change learning by enhancing attention, memory, and inferential processes and by generating particularly "useful" learning data. The integrative account that I present in the rest of this chapter is scoped to focus on children's active learning *decisions* within social contexts. I argue that this is a useful step forward because it allows researchers to ask how specific pieces of social learning affect separate underlying components of decision making.

One major challenge of integrating these two proposals is that there are a large number of factors that could influence how active learning interacts with social reasoning, which in turn creates a large space of possibilities for researchers to test. One way forward is to constrain the space of hypotheses by using a formal model of information seeking and taking an ideal-observer approach [@geisler2003ideal]. The ideal-observer model allows researchers to focus on defining the structure of the learning task and asking how well learners can take advantaqge of the information available in the environment. Moreover, this approach forces researchers to explicitly define the processes of active and social learning as separable, underlying components, which can then become targets for empirical work. 

Research in developmental and cognitive psychology has used the ideal-observer approach to understand active learning. One particularly useful model has been a formal account of scientific reasoning that falls under the umbrella term: Optimal Experiment Design (OED). The OED model was orginally designed to help scientists select the best experiment from the set of possible experiments, where "best" is defined as the experiment that leads to the highest amount of information gained. Using this formalization, researchers have been able to ask whether people's intuitive information seeking looks similar to predictions from OED models. 

Moreover, OED uses the same mathematical framework as recently-developed models of social learning: Bayesian ideal-observer models of psychological reasoning during learning and communication [@shafto2012epistemic; @frank2009using; @goodman2016pragmatic]. These parallel formalizations suggest a way ot integrate active and social learning theories. This point is the primary focus of the integative account that I present in [Part III](#active_social) of this chapter. Before discussing the details of the account, I provide a brief overview of the OED formalization.  

## Part II: A formal account of active learning {#oed}

Optimal Experiment Design (OED) [@emery1998optimal; @nelson2005finding; @lindley1956measure] is a statistical framework for quantifying the usefulness of experiments. @lindley1956measure described the approach as a transition from viewing statistics as binary decision making to a practice of gathering information about the "state of nature" (p. 987). The concrete proposal is to design studies that maximize expected information gain (a measure borrowed from Information Theory and discussed in more detail below) and continue to collect data until the information gained reaches a pre-determined threshold.

The OED approach allows scientists to make design choices that maximize the effectiveness of their experiments, reducing inefficiency and cost. Consider the following toy example borrowed from @ouyang2016practical where a researcher is interested in designing the best experiment to figure out whether people think a coin is fair or biased (i.e., a trick coin). Here the researcher's hypotheses correspond to different models of the coin [$M_{fair}: Bernoulli(p = 0.5)$] and [$M_{bias}: Bernoulli(p)$ where $p \sim Uniform(0,1)$] and the experiments correspond to different sequences of coin flips that she could select as stimuli. Imagine that the researcher has limited time or resources and can only show a sequence of four coin flips, creating a space of 16 possible experiments. An OED model allows the researcher to select the best experiment that maximally differentiates the two hypotheses. For example, OED provides an answer to the question: how much better would it be to use [$HHHH$] versus [$HTHT$]? Here, [$HHHH$] is more informative because both the bias and the fair coin models make the same predictions for the [$HTHT$] experiment, meaning we would not learn much from this test.

\afterpage{
```{r word-learn-schematic, fig.cap = "Schematic of an active word learning context using the decomposition of Optimal Experiment Design. Social input (hearing a novel word) triggers an inquiry goal. Then the learner considers potential hypotheses for the candidate word-object links, weighting each hypothesis by its prior probability. In this case, the learner thinks that the new word is less likely to refer to the familiar object BALL. Next, he considers possible queries (actions) and the potential outcomes of those actions. In the word learning context, the child must direct queries towards a social partner, which provides the learner with more possible queries: both verbal (questions) and nonverbal (eye gaze; pointing). Note that the social partner must interpret the goal of the child's nonverbal queries. If the learner selects the action to maximize expected utility, then he would ask the most informative question, which removes all uncertainty for the meaning of 'dax' -- 'What's that called?' If he does select the relatively less informative action of asking about a single object, he would be unlikely to ask about the familiar object BALL since there is less information to be gained from this query based on his prior beliefs.", fig.scap="Schematic of an active word learning context."}

grid::grid.raster(png::readPNG(here::here(intro_figs_path, "word_learn_schematic.png")))
```
\clearpage
}

@nelson2010experience demonstrate the usefulness of taking an OED approach for differentiating competing theories of information seeking in adults' category learning. They created an OED model of their task, which included the design choices (what combination of features to show participants) and the relevant behavioral hypotheses (the different theories of category learning). They used the model to simulate the outcomes of using different stimulus sets, allowing them to choose stimuli for which the competing theories made very different predictions, speeding the rate of discovery.

@coenen2017asking provide a thorough review of the OED framework and its links to human information seeking. They outline the four critical parts of an OED model that are necessary to compute the expected value of an information seeking action: (1) a set of hypotheses, (2) a set of queries (i.e., actions) to learn about the hypotheses, (3) a generative model of the types of answers that each query could elicit, and (4) a way to score each answer with respect to the learning goal. ^[See Appendix A for the mathematical details of the OED model.] There are also two components that are external to the utility computation but important for an account of human inquiry. First, having a goal to learn, which instantiates the hypotheses, questions, and answers that a learner considers. And second, having a stopping rule, which refers to a threshold that causes people to stop seeking information and generate a response.

### Evidence of OED-like reasoning in human behavior

A growing body of psychological research has used the OED framework as a metaphor for active learning. The idea is that when people make decisions, they engage in a similar process of evaluating the usefulness of different actions relative to their learning goals. Using this evaluation process, learners can then select behaviors that maximize the potential for gaining information. A success of the OED account is that it can capture a wide range of information seeking behaviors, including verbal question asking [@ruggeri2015children], planning interventions in causal learning tasks [@cook2011science], and decisions about where to look during scene understanding [@najemnik2005optimal]. Figures 1 and 2 present schematic overviews of how OED principles could shape the learning process for two of these domains -- causal learning (Figure 1) and word learning (Figure 2).

One compelling use case of OED metaphor as a model of human behavior comes from @nelson2005finding study of eye movements during novel concept learning. Their model combined Bayesian probabilistic learning, which represents current knowledge as a probability distribution over concepts, with an OED model that calculated the usefulness of different patterns of eye movements. Here, eye movements were modeled as a type of question-asking behavior that gathered visual information about the target concept. @nelson2005finding found that participants' eye movements aligned with predictions from the OED model. Specifically, participants changed the dynamics of eye movements depending on how well they learned the target concepts. Early in learning, when the concepts were unfamiliar, the model generated a broader, less efficient distribution of fixations to explore all candidate features that could be used to categorize the stimulus. However, after the model began to learn the target concepts, eye movement patterns shifted to become more efficient and focused on a single stimulus dimension to maximize accuracy. This shift from exploratory to efficient eye movements matched adult performance on the task, suggesting that people's behavior was sensible given the structure of the learning problem and the uncertainty in the context.

Recent developmental work has used OED models to ask whether children are capable of selecting efficient behaviors that maximize learning goals. For example, @legare2013use used a modified question asking game where 4- to 6-year-old children saw 16 cards with a drawing of an animal on them. The animals varied along several dimensions, including type, size, and pattern. Children could ask the experimenter yes/no questions to figure out which animal card was hidden in a box. @legare2013use coded questions as constraint-seeking (narrowing the set of possible cards by gathering information about a particular dimension (e.g., "Is it red?"), confirmatory (questions that provided redundant information), or ineffective that did not provide any useful information (e.g., "Does it have a tail?"). All children produced a high proportion of the more useful, constraint-seeking questions. Moreover, the number of constraint-seeking questions was correlated with accuracy in guessing the identity of the hidden card. @legare2013use interpreted these results as evidence for OED-like reasoning in children's question asking. Other work using the question-game finds that children prefer to direct questions to someone who is knowledgeable compared to someone who is inaccurate or ignorant, providing additional support for the OED hypothesis [@mills2011determining; @mills2010preschoolers].

Another developmental example comes from @cook2011science study of causal learning . They showed preschoolers a device that played music when beads were placed on top of it and manipulated the usefulness of different actions that children could take to test the device. Half of the children saw evidence that all types of beads could make the machine work, while the other half learned that only specific types of beads (defined by color) could make it go. Next, children could choose one of two sets of beads to test the machine. In one set the beads were stuck together, in the other, they could be separated. Children who learned that only some of the beads worked were twice as likely to select the separable beads. This finding suggests that children were reasoning about the amount of information they could gain by choosing the detachable beads since this choice would allow them to test each bead independently. In contrast, the children who believed that all beads worked had less to gain by picking the separable set. This result is compelling because it provides evidence that children's were reasoning about a decision (separable vs. stuck together beads) that would influence a future opportunity to generate useful information. 

Although the OED approach has provided a formal account of seemingly unconstrained information seeking behaviors, there are several ways in which it falls short as an explanation of human self-directed learning. @coenen2017asking argue that OED models make several critical assumptions about the learner and the learning task, including (1) the hypotheses/questions/answers under consideration, (2) that people are actually engaging in some expected utility computation in order to maximize the goal of knowledge acquisition, and (3) that the learner has sufficient cognitive capacities to carry out the calculations. 

In the next section, I argue that limitations of the OED approach can be productively reconstrued as opportunities for understanding how learning from other people could scaffold children's active learning. I focus on integrating research and theory on social learning with five key components of the OED model: goals, hypotheses, questions, answers, and stopping rules (see Figure \@ref(integrative-schematic) for a schematic overview of the account). 

## Part III: Active learning within social contexts {#active_social}

Why should we situate active learning within research on the effect of social learning contexts? First, children do not re-invent knowledge of the world, and while they can learn a tremendous amount from their own actions, much of their generalization and abstraction is shaped by input from other people. Moreover, social learning can be the only way to learn something (e.g., first language acquisition). Finally, children are often surrounded by parents, other adults, and older peers – all of whom may know more about the world than they do, creating contexts where the opportunity for social learning is ubiquitous. 

Second, there is a body of empirical work showing that active learning can be biased and ineffective in systematic ways. For example, work by @klahr2004equivalence found that elementary school-aged children were less effective at discovering the principles of well-controlled experiments from their self-directed learning, but were capable of learning these principles from direct instruction. @markant2014better showed that active exploration provided no benefit over passive input in category learning when there was a mismatch between the target concept and adults' prior hypotheses going into the learning task. And @mccormack2016children found that 6-7 year-olds showed no benefit from active interventions on a causal system compared to observing another person perform the interventions.

In a comprehensive review of the self-directed learning literature, @gureckis2012self point out that the quality of active exploration is linked to the learner’s understanding of the task: if the representation is poor, then self-directed learning will be biased and ineffective. @coenen2017asking continue this line of argument and propose a series of specific challenges for research on active learning. Here is a sample of those open questions that are most relevant to the integrative account proposed in this chapter:

  *  What triggers inquiry behaviors in the first place?
  *  How do people construct a set of hypotheses?
  *  How do people generate a set of queries?
  *  What makes a "good" answer?
  *  How do people generate and weight possible answers to their queries?
  *  How does learning from answers affect query selection and belief change?

\noindent
In the rest of this chapter, I argue that ideas from research on social learning can address these challenges. I start from the OED model, and use it as a conceptual tool to integrate social contexts and active learning. The contribution of this formalization is that it makes the different components of active learning explicit, highlighting the aspects that might be particularly challenging for young learners. Moreover, the "challenges" to the OED account can be reconstrued as opportunities for understanding the benefits of learning from other people. In each of the following sub-sections, I first define a challenge for active learning. Then, I discuss how social contexts could address each challenge, highlighting prior empirical work that connects active and social learning accounts (see \@ref(integrative-schematic) for an overview).

\afterpage{
```{r integrative-schematic, fig.cap = "Schematic of active learning within a social context. Each panel shows how social information could influence a different component of the active learning process. These social effects occur in-the-moment of learning or over developmental time. Also, the cause of the social effect varies from the mere presence of another person to triggering a sophisticated psychological reasoning process about others' goal-directed behaviors. Note that the panels correspond to the different sub-sections in Part IV of the text.", fig.scap="Schematic of the integrative account of active learning within a social context."}

grid::grid.raster(png::readPNG(here::here(intro_figs_path, "integrative_schematic.png")))
```
\clearpage
}

### Goals

In the OED framework, an inquiry goal refers to the underlying motivation for information seeking. This is often operationalized as a search for the target hypothesis amongst a set of candidate hypotheses. Some examples of inquiry goals that children might hold are:

  * What is this speaker referring to? (word learning)
  * What types of objects are called "daxes"? (category learning)
  * How does this toy work? (causal learning)
  * Is this person reliable? (selective learning)

\noindent
Learning goals are important since without them the learner will struggle to evaluate whether an action leads to learning progress. @coenen2017asking illustrate this point by saying,

> The importance of such goals is made clear by the fact that in experiments designed to evaluate OED principles, participants are usually instructed on the goal of a task and are often incentivized by some monetary reward tied to achieving that goal. Similarly, in developmental studies, children are often explicitly asked to answer certain questions, solve a particular problem, or choose between a set of actions. (p. 32-33)

\noindent
Characterizing children's goals is not trivial they could consider a range of goals at any moment with no guarantee that learning progress be one of them. In fact, one line of theorizing about the OED hypothesis argues that effective information seeking should only occur in the presence of precise tasks and goals. Consider the situation where a parent gives their child a new toy with several buttons on it and says, "Let's figure out how this toy works!" In this case, it becomes possible to ask whether the child selects actions that are more or less useful with respect to understanding the toy's causal structure. 

This scenario illustrates how interactions with other people can trigger learning goals and information seeking. Empirical work shows how the actions of a social partner can increase children's tendency to detect their own uncertainty (see @lyons2010metacognitive for a review). The upshot of this research is that children's ability to realize when they do not know something is relatively slow to develop. For example, @markman1979realizing showed that elementary school-aged children were unable to detect obvious inconsistencies in written paragraphs (e.g., "fish can't see without light, and there's no light at the bottom of the ocean, but some fish at the bottom of the ocean only know their food by its color."). Interestingly, if the experimenter gave children an explicit warning or challenge to find a problem with the essay, then they were more likely to monitor uncertainty and asked more clarifying questions. This finding can be reconstrued as the social context shifting children's expectations, highlighting the learning goal, and facilitating their information seeking actions. Converging evidence comes @kim2016young, which showed that in an "opt-out" task, 3- to 4-year-olds who were told they woulid have to teach another person about the contents of a opaque box showed higher rates of uncertainty monitoring compared to children who were not expecting to interact with anyone else (see also @lombrozo2006structure). 

In addition to triggering inquiry goals, social partners can communicate the *value* of learning goals relative to other goals that children may pursue. This connection draws on theoretical and empirical work exploring how children's environments can shape their intuitive frameworks for processing information and generating goals (i.e., intuitive theories) [@dweck1988social]. These accounts propose that if children believe that abilities are malleable, they will want to increase their competence (prioritize learning goala) as opposed to demonstrate their fixed abilities (prioritize performance goals). Empirical work shows that when adults emphasize a learning goal (e.g., "If you pick the task in this box, you'll probably learn a lot of new things." vs. "If you pick this box, although you won't learn new things, it will really show me what kids can do."), children tend to seek out the more difficult task [elliott1988goals]. Moreover, both lab-based experiments and observational work provide evidence that the language adults use when praising children influences their tendency adopt inquiry goals [@cimpian2007subtle; @gunderson2013parent]. 

While social interactions can emphasize learning, they can also engage psychological reasoning about others' mental states and elicit social goals that take priority over learning goals. Consider the "goals" panel of the schematic active-social learning context shown in \@ref(integrative-schematic). If the learner is worried about what his social partner thinks of him, then he might prioritize actions that reduce the chance of making mistakes and may not even ask for a novel label. Moreover, he could seek out easy tasks that demonstrate his competence at the expense of selecting actions that help him learn. The OED framework typically focuses on informational goals with progress measured as reduction in uncertainty. However, recent empirical and modeling work has begun to move beyond informations-specific utiilty functions to include other goals learners may have (e.g., saving time, money, or cognitive resources) [meder2012information]. 

Recent work modeling pragmatic communication ^[Rational Speech Act (RSA) framework for pragmatic reasoning. The RSA approach models language comprehension and production as, "a process of recursive reasoning about what speakers would have said, given a set of communicative goals" (p.819) [@goodman2016pragmatic]] provides a way to integrate social goals within the OED framework. For example, @yoonwon model speakers' decisions to use polite speech as opposed to direct speech (e.g., indirect language such as "I don’t think that dress looks phenomenal on you" as opposed to "It looks terrible") as a tradeoff between maximizing informational and social goals, showing that speakers are in fact balancing these two goals when deciding what to say. 

In both OED and RSA, people are assumed to select actions that maximize utility, but the politeness model allows social information in the utility computation. An intriguing possibility for future research would be to adapt the utility-theoretic approach used by @yoonwon to model information seeking behaviors in social contexts that vary how much they emphasize learning goals. The presence of another person could be modeled as an increase in the weight that children place on maximizing social goals, leading children to select easier tasks where they can appear competent(see @yoon2018balancing for an example of this approach in causal learning). Moreover, this builds on the goal-orienting accounts reviewed above [@dweck1988social] since behavior is modeled as an output of a mixture of goals as opposed to chlidren holding either a performance or a learning goal.

Another open question for research on children's learning goals is how often children experience contexts where learning goals are apparent or emphasized in their everyday experience. We do not yet have an estimate of the prevalence of situations that would lead children to generate learning goals. One exception, however, is research on *guided participation*  by @rogoff1993guided provides evidence that parents from a diverse set of cultural backbgrounds produce high rates of structuring and goal-orienting behaviors during activities such as cooking, shopping, working, etc. It is interesting to consider whether variability in children's exposure to goal-orienting behaviors could influence children's tendency to spontaneously generate learning goals.

### Hypotheses

Once a learing goal is established, the next step of inquiry is to decide what hypotheses to consider. Intuitively, a hypothesis is a candidate explanation about how the world works. For example, consider the schematic learning contexts shown in Figures 1 and 2. In the casual context, the hypotheses for how the toy works could include: (1) Button A, (2) Button B, (3) Buttons A and B simultaneously. In the word learning context, the child might think the new word "dax" means: (1) dax = object A, (2) dax = object B, or (3) dax = object C. ^[Note that this hypothesis space is simplified since it only considers the possibility of one-to-one word-object mappings.] 

The set of hypotheses under consideration is critical for quantifying effective self-directed learning in the OED account. The usefulness function of expected information gain outlined in [Part III](#p3) works by comparing the learner's uncertainty over hypotheses before and after she sees an answer ($U(a) = ent(H) - ent(H|a)$). Without knowing the conents of the hypothesis space, it becomes challenging to select the best choice for reducing uncertainty. Put another way; the OED framework does not readily deal with situations where learners might have to consider a large space of hypotheses, might hold the wrong hypotheses, or might perform actions without considering any hypotheses at all. This is an especially important challenge for developmental accounts that draw on OED principles since these scenarios seem quite plausible for young learners.

However, one useful function of social learning contexts is that they can provide a clear set of possible explanations for the actual state of the world. In practice, adults and older peers who have access to the correct hypothesis can constrain the space of children's hypotheses to facilitate information seeking. This effect of social context parallels the discussion of the role of social partners in constraining goals in the previous section. 

One relevant case study comes from work on children's early word learning. The challenge for a young word learner is that even the simplest of words, concrete nouns, are often used in complex contexts with multiple possible referents, which in turn have many conceptually natural properties that a speaker could talk about. This ambiguity creates the potential for an (in principle) unlimited amount of hypotheses that children could consider when trying to figure out the meaning a novel word. Remarkably, word learning proceeds despite this massive uncertainty, with estimates of adult vocabularies ranging from 50,000 to 100,000 distinct lexical concepts [@bloom2002children]. 

It does not seem plausible for children to entertain all hypotheses about possible word-object links. But which ones should they consider? One proposed solution is that word learners only consider a single word-object link at a time [@trueswell2013propose; @medina2011words]. Under this account, the child makes an initial guess about the word meaning, and then only stores that word-object link until she receives sufficient evidence that her initial hypothesis was incorrect. If she does see enough counter-evidence, then she will switch to a new, single hypothesis that better matches the statistics in the input. ^[This "propose-but-verify" account parallels work by @bonawitz2014win in the domain of causal learning, which suggests that a "Win-Stay, Lose-Sample" algorithm (inspired by efficient sampling procedures in computer science) provides a better explanation of children's hypothesis testing behaviors compared to an algorithm that enumerates the entire hypothesis space.] However, another influential account of early word learning, inspired by basic associative learning principles, argues that word learners store more than a single hypothesis. Under this theory, children's  hypothesis spaces are reduced gradually via the aggregation of word-object co-occurrence statistics across multiple labeling events [@siskind1996computational; @yu2012modeling]. Support for this account comes from experimental work showing that both adults and young infants can use word-object co-occurrence statistics to learn word meaning from individually ambiguous naming events [@smith2008infants]. Moreover, adults show evidence of being able to recall multiple word-object links from an initial naming event [@yurovsky2014algorithmic]. 

The critical difference between these proposals is how much information learners store in the hypothesis space. Some of our own work provides evidence that the social context can modulate the content of the learner's hypothesis space [@macdonald2017social]. Inspired by ideas from Social-pragmatic theories of language acquisition that emphasize the importance of social cues for word learning [@clark2009first; @hollich2000breaking; @bloom2002children], we showed adults a series of word learning contexts that varied in ambiguity depending on whether there was a useful social cue to reference available (a speaker's gaze). We then measured learners' memory for alternative word-object links. People flexibly responded to the amount of ambiguity in the input, and as uncertainty increased, they tended to store more word-object hypotheses. Moreover, we found that learners stored representations with different levels of fidelity as a function of the reliability of the social cue. When the speaker was a less reliable source of information, learners distributed attention and memory broadly, storing more hypotheses.

These results provide evidence that the content of learners' hypothesis spaces changed as a function of social information. Further suppport for this idea comes from experimental work showing that even children as young as 16 months prefer to map novel words to objects that are the target of a speaker’s gaze and not their own [@baldwin1993infants], and analyses of naturalistic parent-child labeling events shows that young learners tended to retain labels accompanied by clear referential cues, which served to make a single object dominant in the visual field [@yu2012embodied]. One important direction for future research is to measure the full causal pathway from variation in social information through children's hypothesis spaces to their information seeking behaviors. For example, it would be interesting to know whether learners' subsequent questions or decisions about where to allocate attention would be affected by the social context in which they were first exposed to a new word.

A second case study that illustrates the importance of considering the learner's hypothesis space comes from work by @lucas2014children where they compared children and adult's capacity for learning different kinds of causal structures. In the task, participants saw a series of events that consisted of a training phase where an experimenter placed objects on a box that either played or did not play music. The participant's goal was to learn which objects, or combination of objects, made the box work. In the disjunctive condition, only single objects (A or C, but not B) made the toy play music. In the conjunctive condition, only the combination of two different objects (A **and** C) would make the toy play music. After seeing several demonstrations, both children and adults were tested on ambiguous events where they could either infer a disjunctive or conjunctive causal relationship. Only children learned the conjunctive relationship, even though the evidence favored this interpretation. The authors speculate that adults were biased towards the disjunctive hypothesis since it is a more common causal relationship in everyday experience; whereas children have accumulated less experience and have diffuse prior beliefs, which caused them to update their beliefs faster when they saw evidence in favor of the conjunctive hypothesis. ^[Figure 1 illustrates a version of the active causal learning scenario. In this case, the learner believes that pressing both buttons to activate the toy is a less likely hypothesis. As a result, the query to test the conjunctive hypothesis "press both buttons" becomes less useful for gaining information since it would produce confounded evidence concerning her other, disjunctive hypotheses.]

The striking difference between adults and children in the @lucas2014children study suggests that it is not trivial to know what hypotheses children bring to the learning task. Moreover, features of the immediate social context could bias the content of children's hypothesis space. In fact, @lucas2014children suggest that, 

> Most of the time, adults do not need to dramatically change their beliefs or abandon their hypotheses for dramatically different ones. Indeed, doing so would be a liability: adults are expected to make accurate predictions and good decisions, not bold inductive leaps. Adults are also unlikely to have caregivers to correct their errors and save them from poor choices. (p. 295)

\noindent
This proposal makes a testable prediction: that contexts in which learners "feel" safe to make mistakes would lead children to consider and test a broader range of hypotheses. Another effect of the social context highlighted in @lucas2014children's study is that the experimenters scaffolded children and adults consideration of the disjunctive and conjunctive hypotheses. That is, their actions constrained the hypothesis space to isolate learning and information seeking effects. The "Hypotheses" panel of Figure 3 presents a schematic illustration of how social partners can constrain hypotheses in the moment of learning. Similar to the research on goals, the majority of the work on hypotheses has focused on lab-based studies. Thus, it is an open question as to how much of role adults play in communicating relevant hypotheses during children's daily experience.

Social information can also shape children's hypothesis space by providing the necessary input to revise children's incorrect intuitive theories about how the world works. Research on conceptual change provides evidence that children integrate social input with their current hypotheses [@gelman2009learning]. Conceptual change refers to a "radical" reconstruction of an intuitive theory about how the world works. For example, elementary school-aged children tend to hold a mixture of beliefs about the shape of the earth [@vosniadou1992mental]. These theories range from a flat earth theory that matches children's everyday perceptual experiences (i.e., walking on flat ground) to the adult-like, sphere model, which reflects the actual state of the world. Interestingly, some children hold intermediate beliefs such as a dual-earth theory where there are two earths: "a round one which is up in the sky and a flat one where people live" (p. 550). The fact that some children entertain a dual-earth theory suggests that they are actively integrating aspects of their initial theory with the information they get from other people who already hold the correct, sphere theory. Moreover, for children to hold the sphere model at all, they must have learned it from social input. 

Additional evidence for the role of social input comes from work on children's reasoning about biological concepts. For example, the concept of "alive" takes years to fully develop, with younger children (under ten years of age) often claiming that only animals, and not plants, are alive. @opfer2004revisiting tested the hypothesis that evidence of goal-directed movement is critical for children's extension of the "alive" concept. In their study, 5-year-olds' were trained in different ways to think about the concept of a "living thing" and then asked whether they believed that plants were alive. Children either learned that plants were capable of goal-directed movement (e.g., "The house plant is growing this way. It needs the sunlight over here."), that plants were capable of growth, or that plants need water to survive. Children in the goal-directed movement condition showed the most significant theory revision, saying that plants were also living things more consistently on a post-intervention categorization task. Converging evidence comes from research on the links between language experience and performance on various cognitive tasks. For example, empirical work shows that deaf children without access to a natural language perform worse on Theory of Mind tasks [@peterson2000insights]; that Korean speakers perform better than English speakers on tasks that require categorizing based on tight vs. loose distinctions, which are lexicalized in Korean [@mcdonough2003understanding]; and that exposure to a first language reduces infants' capacity to detect non-native phonetic contrasts [@maurer2014perceptual].

One conclusion from the work on children's conceptual change is that certain hypotheses are more primitive and children require social input to revise them (flat earth -> spherical earth). Taken together, the case studies reviewed in this section illustrate several points relevant to the integrative active-social learning account. First, the set of hypotheses that children consider are likely to be quite different from adults (and possibly different from what the experimenter thinks the child is considering). Second, children generate hypotheses using a mixture of prior knowledge, expectations about the task, and social input. Third, there are (at least^[We could make a further distinction between the developmental and the cultural timescales, where developmental refers to information acquired from interactions with others in the child's lifetime (e.g., disjunctive causal structures are more likely to occur in the world) and cultural refers to information that has accumulated throughout human evolutionary history (e.g., access to natural language or concepts such as the spherical earth.)]) two timescales through which social learning can shape hypotheses. An in-the-moment timescale where others' behavior constrains hypotheses for the current task -- for example, referential gaze indicating candidate word-object mappings or an adult suggesting a disjunctive (one-block) vs. a conjunctive (two-block) theory for how to make a toy work. And a developmental timescale where prior interactions with other people and cultural learning modify the hypotheses that children bring to the learning task (e.g., the conceptual change and language effects reviewed above). 

### Queries

Queries in the OED framework refer to the experiments that a scientist could conduct to gather information about their hypotheses. Queries in human information seeking can refer to a variety of actions, including verbal questions, pushing a button to figure out how a toy works, and decisions about where to look. One of the strengths of the OED account is the fact that it provides general principles that explain such a broad range of behaviors.

However, the challenge for the young learner is to discover what behaviors are available and of those actions which might be particularly useful for gathering information. In this section, I illustrate how the social learning context provides valuable input to this learning process via demonstrations of useful actions that learners could take to gather information. I suggest that this process involves adults' modeling useful information seeking and children recognizing and imitating these behaviors.  

It seems obvious that children would look to older peers or adults to learn what actions are useful. However, a large body of empirical work suggests that even young infants will not imitate every action that they see. Instead, children show evidence of "rational imitation" and will look for cues about others' goals and use this information to selectively imitate. For example, @gergely2002developmental measured how often 14-month-old infants imitated an adult's actions -- turning on a light with her head (less efficient) instead of her hands (more efficient) -- as a function of whether there was a relevant explanation for selecting the less efficient action (whether the adult's hands were occupied). They found a substantial difference in imitation rates across conditions (69% in the hands-free vs. 21% in the hands-occupied), suggesting that children recognized the reason for the inefficient action and chose to ignore the means and focus on the goal of turning the light on in the most efficient way possible.

The high rates of imitation in the hands-free condition highlight another component of learning from others' actions: that children tend to overimitate behaviors even when these actions are not directly relevant to the task. For example, @call2005copying compared imitation behaviors of 2-year-old children after they watched someone demonstrate how to open a tube using only the necessary actions or using the actions plus a style component unrelated to opening the tube (e.g., removing the tube's cap with an exaggerated twisting motion). Almost all children (93%) imitated the causally irrelevant action, providing evidence that they were focused on reproducing each of the experimenter's actions and not just reproducing the outcome of opening the tube.  Other empirical work shows that social factors matter for children's decisions to imitate. @carpenter1998fourteen showed that 14- and 18-month-olds were less likely to mimic an adult's action if the action was marked verbally as a mistake (e.g., "Whoops!"). @buchsbaum2011children provide evidence that the children are more likely to overimitate when the adult is described as a "knowledgeable teacher" as opposed to "naive." And @carpenter2002understanding showed that giving children explicit information about another person's goals before a causal demonstration leads to an increase in imitation and learning of the correct casual structure. Together, the work on imitation suggests that children could use others' goal-directed, information seeking behaviors as input to help them learn what queries are useful.

Research on verbal question asking provides insight into how social input guides children's developing information seeking. First, consider that the very act of asking a question in natural language requires that children have acquired a conventionalized symbolic system, which must have been learned from social input. Second, both experimental work and corpus analyses provide evidence that children's question-asking becomes more varied and productive over the first years of life as they get exposed to more complex language input (see @chouinard2007children and @legare2013use studies reviewed in [Part II](#p2)). Moreover, as children develop, they improve the timing of their turn-taking during question-answer exchanges, reducing the length of gaps between turns [@casillas2014turn]. Interestingly, @casillas2014turn also showed that adults were sensitive to children's developing question-answering skills, waiting to ask more difficult questions until children were older, and modifying their questions if children were confused (e.g., "Who is this? -> What’s he called? -> Who is he? -> What is his name?").  

The majority of research on children's question asking has focused on aspects of the child's behavior, exploring how the type, content, and effectiveness of questions changes as children develop. However, several studies have measured children's exposure to questions in their input. For example, @yu2017peagogical coded parent-child interactions from the CHILDES database to measure the amount of "pedagogical" questions in children's input. They differentiate "pedagogical" from "information seeking" questions by coding whether the adult already knew the answer. For example, "What’s that called?" would be pedagogical; whereas,  "What did you do at school?" would be information seeking. Approximately 30% of parents' questions were pedagogical, 60% were information seeking, and 10% were rhetorical (i.e., not intended to be answered verbally). Parents also directed a smaller proportion of pedagogical questions to older children. @yu2017peagogical speculate that the function of pedagogical questions is to help children learn. 

It is interesting to consider how children might internalize adults' question asking behaviors (modifications, pedagogical questions) and incorporate them as part of their own question asking repertoire. However, more work is needed to understand the link between adults' question-asking practices and children's behaviors. This research could be especially interesting since observational studies have found that that parents' use of wh-questions predicts children's later vocabulary and verbal reasoning outcomes [@rowe2017going] and children of parents who were trained to ask "good" questions during book reading episodes at home also asked better questions during book reading sessions at school [@birbili2009helping]. One explanation for these associations is that wh-questions challenge children to produce more complex responses that build verbal abilities. However, another intriguing causal pathway is that the frequency and type of questions that parents shape children's information seeking skills by providing templates for useful questions.

After children generate a set of possible questions, they have to evaluate the relative usefulness (i.e., utility) of the different queries. But how do children learn the features of a good question? One solution is for children to observe other people's question asking behaviors, recognize which questions are useful, and leverage their imitation skills to model those behaviors. In fact, there is evidence from work with adults showing a substantial difference between people's question-generating (harder) and question-evaluation (easier) skills. For example, @rothe2015asking asked a group of adults to play a modified "Battleship" game where they had to find the location of three ships that consisted of 2-4 tiles and could be oriented in either the vertical or horizontal direction on a 6x6 grid. Participants gathered information sequentially by uncovering one tile at a time. At different points in the task, the game would stop, and participants could ask any question using natural language. @rothe2015asking used a formal OED model to measure the expected information gain of each question, and people rarely produced high information value questions. However, in a follow-up experiment @rothe2015asking had a different group of adults play the Battleship game, but this time participants had access to the list of questions generated by participants the free-form version, In this contexts, adults were quite good at recognizing and selecting high information value questions.   

Developmental work provides additional evidence of this production-comprehension asymmetry. For example, children younger than the age of three have difficulty generating appropriate verbal questions compared to their older peers in "Twenty Questions" style tasks that are designed to measure question-asking skills [@mills2011determining; @mills2010preschoolers]. However, when @mills2012little tested 3- to 5-year-old's capacity to learn from observing third-party question-answer exchanges, they found that even the youngest children were capable of using information elicited by others' yes/no questions to identify the contents of a box. Interestingly, children recognized the value of others' question-answer exchanges, paying more attention to them as compared to third-party exchanges that did not include question-answer exchanges. These results suggest that even at an age where generating questions "from scratch" might be difficult, children can observe and learn from questions that occur in their social environment. @mills2011determining also explored this phenomenon by directly manipulating whether children were exposed to a training phase where adults modeled useful questions before playing the question asking game. They found that even though the youngest children were not successful at constructing good questions, they were able to ask useful questions at a much higher rate following exposure to explicit modeling.
  
Work with elementary-school-aged children in the domain of scientific inquiry also shows that generating a good question is a challenging aspect of inquiry skills. One relevant example comes from @kuhn2008needs's intervention study comparing children trained on scientific inquiry skills (e.g., understanding the objectives of inquiry and identifying questions) to a group of slightly older students who had not participated in the direct instruction training. Children in the training group showed progress. In contrast, children in the comparison group failed to develop these formal scientific inquiry skills in the absence of a particular kind of input. kuhn2008needs summarizing the key results, 

> Consistent with the findings of Kuhn and Dean (2005), identifying a question appears to play a key role in making the rest of the inquiry cycle productive ... Like other components of the inquiry process, this skill is not one a student learns once and has mastered. (p. 555)

Another way that social contexts influence the set of possible queries is by adding a "social target" for information seeking. 
That is, the child now has an additional choice: to gather information from the non-social world or other people. The "Questions" panel in Figure 3 shows a child trying figure out how a toy works. If there is no social partner present, they could still try actions that test the system directly and seek information from the world. But if another person is present, the child now has the option to ask verbal questions or to seek help via nonverbal cues (e.g., pointing, facial expressions). 

Recent empirical work has explored the factors that influence children's decisions to seek information from other people. For example, @fitneva2013development measured 4- to 6-year-old's decisions about how to learn the features of  a novel social category: "moozles." Critically, the target concept was either visible (hair color) or invisible (knowledge of a foreign language). Children could choose to look directly at the moozle or ask a moozle expert. Children tended to "look" for the visible property and "ask"  for the invisible property. These results suggest that children have some meta-understanding of the kinds of information that is particularly useful to learn from social partners. 

Additional evidence comes from work by @lockhart2016could. They asked 5- to 11-year-old children whether a person "growing up on their own" could learn facts that varied along a dimension of learnability based on direct perceptual experience (that the sky is blue vs. that the earth is round). Children of all ages performed quite well, showing that could verbally articulate the kinds of information that would require interactions with other people. The items in this study did not test children's appreciation for more indirect forms of social learning: that is, to learn that the sky is blue relies on having a conventional language system for referring to concepts. @gelman2009learning refers to this as "a hidden level of cultural input" (p. 2). The critical point is that even in learning contexts that appear entirely self-directed, children's massive amounts of accumulated experience with other people shape the hypotheses and questions that children consider.

Another set of relevant examples comes from work on children's help-seeking behaviors. @vredenburgh2016young had children build toys that required multiple steps, and on each step, children were given the opportunity to ask for help from the experimenter. Each step varied in difficulty and children naturally varied in their toy building skill. Children asked for help when the step on more challenging steps, suggesting that preschoolers sought help systematically. Moreover, work by @gweon201116 found that 16-month-old infants are selective help-seekers, turning to a social target to request information or acting on the world depending on which information source was more likely to help them achieve their current goal. In this case, the infants' goal was to make a malfunctioning toy produce music, and the critical manipulation was whether children saw evidence that explained the likely cause of failure being the toy versus their capacity for making the toy play music. When the toy was likely to be broken, they reached for a new object (queried the world), but in contrast, when the evidence suggested that the child was the issue, then they sought help from a nearby adult. 

Some of our work has explored how the presence of another person changes the set of information seeking behaviors available [@macdonald2017info]. Inspired by theories of natural vision that characterize eye movements as an information seeking mechanism, we asked whether children and adults would allocate more visual attention to a speaker when the linguistic signal was noisy to support the goal of rapid language understanding. We used an eye-tracking task to measure participants' gaze patterns while they processed clear or degraded speech (speech with brown noise added). Both children and adults spent more time fixating on the speaker in the degraded speech context. Interestingly, children and adults were also more accurate in word recognition even though the speech was noisy and difficult to process. This result suggests that listeners were compensating for the uncertainty in the auditory channel by gathering visual information from the speaker. Critically, listeners would not have been able to gather this information if the speaker was not present (e.g., listening to a noisy recording) and in clear view.

In sum, queries provide the tools for information seeking. However, more research is needed to understand the link between children's input and the set of questions they consider . One proposal is that children use their powerful imitative learning abilities to model the question-asking behaviors demonstrated by more knowledgeable others. Moreover, social contexts can fundamentally change the set of actions available to the learner by providing a social target for information seeking behaviors.  

### Answers

In the OED framework, answers refer to possible states of the world after the learner generates a query. An answer is useful if it results in a substantial decrease in uncertainty about the actual state of the world. The challenge for the active learner can be separated roughly into two parts: (1) figure out what which answers are likely and (2) decide how much you should learn from an answer after seeing it. The social context plays a role in each component and is the focus of the current section.

Defining the specific features of a "good" answer is challenging. Intuitively, a good answer gives the learner information that they did not already know, that they were interested in learning, and that is likely to be useful beyond the current context (i.e., to generalize). Even within the formal OED framework, there have been a variety of ways to instantiate the utility function (e.g., information gain, probability gain, and Kullback-Leibler divergence) to compute the value of an answer (see @nelson2005finding). All of these information-theoretic utility functions take into account the learner's prior beliefs represented as probability distributions over hypotheses and calculate the impact that an answer would have on the learner's beliefs represented as conditional probability distributions. 

Several social learning accounts argue that a key function of social information is to provide useful answers. For example, evolutionary models of cultural learning argue that the human capacity for efficiently transferring knowledge between individuals allows for the gradual accumulation of small improvements that eventually lead to complex tools, beliefs, and practices that would be difficult, if not impossible, for any individual to discover on their own [@kline2015learn]. @boyd2011cultural provide the following example,

> For example, a rare chance observation might allow a hunter to associate a particular spoor with a wounded polar bear, or to link the color and texture of ice with its stability on windy days just after a thaw. Such rare cues allow accurate low-cost inferences about the environment. However, most individuals will not observe these cues, and thus making the same inference will be much more difficult for them. Organisms that cannot imitate must rely on individual learning, even when it is difficult and error-prone. They are stuck with whatever information that nature offers. (p. 10921)

\noindent
The fundamental idea is that communicating useful and difficult to acquire information enhanced evolutionary fitness. Thus, there is an a priori reason to expect that information from other people will be useful. 

This concept is critical to @csibra2009natural's theory of "Natural Pedagogy" reviewed in [Part I](#p1). Specifically, they argue that an assumption of *generalizability* is a fundamental component of adults' communication with children. Their account has three elements: adults transmit generic information, adults provide ostensive cues to signal generalizable knowledge, and children show sensitivity to these cues, treating information differently when they are present. Evidence for a bias towards generalizability comes from a set of empirical studies showing that infants will generalize more often when learning information accompanied by ostensive communicative cues such as eye gaze or child-directed speech. For example, infants are more likely to generalize the positive vs. negative valence associated with a specific object-person pairing to a new person if the valence was demonstrated with pedagogical cues [@gergely2007pedagogy]. Also,  infants are more likely to encode the stable features of an object, as opposed to its location in space, if a communicative signal such as a point guided their attention [@yoon2008communication].

Even if learning occurs in a social context with a default assumption of useful and generalizable information, not all answers are equally informative. Thus, the second challenge for information seekers is to evaluate possible responses to a query to figure out how much they would update beliefs. This challenge is perhaps one of the more developed connections between the formal social and active learning accounts. Researchers have made progress in modeling the influence of different assumptions that a learner could make about the generative process of answers. For example, @shafto2012learning lay out a continuum of sampling assumptions:

  * *Weak sampling*: answers generated at random from the set of all possible answers (independent of target hypothesis)
  * *Strong sampling*: answers generated at random from the set of answers that are true of the correct hypothesis (linked to target hypothesis)
  * *Pedagogical sampling*: answers generated that maximize the learner’s belief in the correct hypothesis (linked to target hypothesis and consider alternative hypotheses)
  
\noindent
Critically, if the learner assumes strong or pedagogical sampling, then they can make stronger inferences that speed learning. For example, if we see someone press two buttons to activate a device, we are more likely to think that both buttons were necessary if that person knew how the machine worked and wanted to communicate to us how it worked. Otherwise, if one of the buttons would have been sufficient, then it would not make sense for them to perform the less efficient action of pressing both buttons. The effects of these sampling assumptions are fundamentally psychological. They require the learner to reason about others' goals and to reason about whether other people are thinking about their goals. See the "Answers" panel of Figure 3 for a visual illustration of this recursive psychological reasoning process within the active learning context. 

Empirical support for the pedagogical sampling account comes from a range of domains/tasks, including word learning [@frank2009using], pragmatic inference [@frank2012predicting], and causal reasoning [@bonawitz2011double] (see the section on inferences and generalization in social learning Part I). We can also revisit these findings and connect them directly to specific components of the OED model of human inquiry. Consider @xu2007sampling finding: that learners are "sensitive" to the sampling process that generated the examples. When a knowledgeable teacher selected the examples, learners assumed the examples indicated the true word meaning. And if this were the case, then it would be surprising to see three examples drawn from the smaller subordinate category. Formally, they modeled sensitivity to sampling assumptions by changing the learner's belief in the probability of hearing a particular label ($l_i$) given a specific object ($o_i$) and word meaning ($m$), modifying the likelihood function in their Bayesian cognitive model: $p(x_i \mid m) \propto p(l_i \mid o_i, m)$. In this case, the likelihood function for the teacher-driven condition was designed to capture the idea that learners should prefer "smaller" or more restrictive hypotheses if they are confident that the teacher generated labels based on the actual word meaning.

This formalization provides a direct connection with the OED model of human inquiry. Specifically, when a learner simulates the possible answers, she considers how much each answer will update her beliefs. This reasoning process is modeled by computing the difference between the learner's prior and posterior uncertainty (i.e., entropy): $U(a) = ent(H) - ent(H|a)$. The learners' sampling assumptions naturally enter the information seeking calculus through the posterior entropy term $ent(H|a) = -\sum_{h\in H}{P(h|a)logP(h|a)}$. Intuitively, this part of the model captures the idea that not all answers are equally useful, and answers that are generated to help us learn are more informative and should lead to a stronger change in the learner's beliefs.

The approach of building more sophisticated likelihood functions has also been used to capture another aspect of evaluating the utility of an answer: that not all social partners are equally reliable sources of information. When learning from the testimony of others, there is always a possibility that the information could be inaccurate or misleading. This reasoning process might be especially important for young learners who acquire much of their information via interactions with others. A growing body of evidence suggests that even very young infants are capable of *selective* learning, rejecting answers that conflict with their knowledge [@pea1982origins] and seeking information from people who tend to provide good answers in the past [@koenig2004trust]. 

For example, empirical work shows that preschoolers track and integrate a speaker's prior instances of accuracy to figure out if they are trustworthy and will use this information to guide subsequent learning from that speaker’s future claims [@koenig2004trust]. In these studies, children evaluate a speaker’s current testimony after the speaker establishes a record of reliability or unreliability by labeling or mislabeling familiar objects. Across these studies, preschoolers are consistently less likely to direct questions towards and learn from a previously unreliable person. Moreover, @chow2008see found that 14-month-olds are less likely to follow the gaze of a person who had been unreliable in the past, i.e., someone who had consistently directed gaze towards an empty location in space. Finally, children's selective learning appears sensitive to external cues, preferring to learn familiar over unfamiliar teachers [@corriveau2009choosing], adults over peers [@rakoczy2010bigger], and ingroup over outgroup members [@macdonald2013my].

Converging evidence comes from @gweon2014sins work on children's exploration behavior after seeing pedagogical demonstrations of varying quality. In this study, children played with toys that either had a single or multiple functions (e.g., spinning globe or flashing light) until they independently discovered the correct number of functions. Then, depending on condition assignment, they saw a puppet either teach all of the functions (informative teacher) or a subset of the functions (under-informative teacher). Finally, the puppet teacher introduced a new toy to the participant and demonstrated a single novel function. Critically, when the puppet teacher had been under-informative in their previous teaching, children spent more time exploring the object functions that the teacher did not demonstrate. That is, children did not make the stronger inference that there were no other functions to discover. 

The upshot of the selective learning literature is that children are not entirely credulous when they encounter information. Instead, they actively reason about features such as expertise and helpfulness avoiding people that they think are unreliable. Interestingly, the typical outcome measures in studies of selective learning are children's information-gathering decisions: whom to direct questions towards and how long to explore a novel toy. These behaviors map directly onto the decisions in the OED model of human inquiry and suggest that children consider the expected utility of others' answers when deciding to gather information.

Similar to the pedagogical reasoning effects, the selective learning phenomena have also been modeled by modifying the likelihood function in a Bayesian cognitive model. For example, @shafto2012epistemic proposed that selective learning in object labeling scenarios can be explained as children reasoning about both the helpfulness and knowledgeability of speakers when they produce a given label, $l$. Here the child's goal is to select a speaker that increases the chance that they get good information that matches the true state of the world ($label=correct$). Formally, they specify this likelihood function as: 

$$P(l \mid s,k,h) = \sum_b P(l \mid b,h)P(b \mid k,s)$$

\noindent
This function captures the idea that the probability of a label depends on the true state of the world and features of the speaker: their knowledge ($k$) and helpfulness ($h$). This is decomposed into two parts: (1) the speaker's belief ($b$) about the label $P(b|k,s)$, which depend on their knowledge ($k$) and the true label ($s$), and (2) the speaker's probability of producing a label that matches their belief, which depends on their helpfulness ($h$). Using this model, @shafto2012epistemic captured several qualitative findings from the selective trust literature, including children's demonstrated preference for accurate over inaccurate speakers. While the precise mathematical details of the model are less important, the key takeaway is that the same modeling approach can account for children's behavior in different domains.   This parallel suggests that children reason about the utility of answers before deciding to seek information from a social partner and after having received information from another person.

One consequence of the ideas discussed in this section is that features of the individuals who are present in a social learning context can change whether information seeking occurs at all. If a child is in a setting that is unlikely to provide useful answers, then generating an information-seeking behavior, even if the action has the potential to return useful information, becomes less valuable. Thus, a challenge for the self-directed learner is to figure out whether helpful answers are likely to occur. However, this is a less-developed area of research, and more work is needed to understand whether the expected usefulness of answers within a *context* might reduce information seeking because the costs in mental energy or time are too high. The dual consideration of costs and benefits in active learning has been the focus of recent advances in machine learning [@haertel2008return] and children's developing social cognition [@jara2015children]. It would be interesting to merge these cost-based approaches with ideas from social learning theory to ask how social contexts modify the costs of different behaviors.

### Stopping rules

A stopping rule describes a threshold that causes people to cease information seeking and generate a behavior. The concept draws on ideas from probability theory that have been used to model how random variables change as a function of time. Rules can be information or time-based. For example, when researching for a paper, a student might generate the time-based stopping rule -- read for two hours -- or a more information-based rule -- read until I understand this concept. The learner's goal is to figure out the stopping rule that balances achieving the inquiry goal with reducing unnecessary time/effort put into the task.

Studies of children's information seeking have primarily focused on measuring whether children persist if their initial request is not satisfied. For example, @frazier2009preschoolers analyzed parent-child question-answer exchanges from the CHILDES database to see if children show evidence of seeking causal explanations when they ask *how* and *why* questions. To address this hypothesis, @frazier2009preschoolers measured the probability of children re-asking the same question and the likelihood of asking a different, follow-up question after receiving either an explanatory response (e.g., CHILD: "Why you put yogurt in there?" ADULT: "Yogurt's part of the ingredients") or a non-explanatory response (e.g., CHILD: "How do you get sick?" ADULT: "I don't know."). Children were more than twice as likely to re-ask a question after getting a non-explanatory response (24%) compared to an explanatory answer (9.4%), providing evidence that they continued to collect information until their inquiry goal was satisfied.  

Converging evidence comes from @deborah2004children's work exploring children's intended meaning when they ask "What is it?" about objects. Children's propensity for asking follow-up questions was measured after they were given either a name or a functional explanation in response to an ambiguous request ("What is it?" Or "What's this?"). Similar to @frazier2009preschoolers's findings, 2- to 4-year-olds asked more follow-up questions when adults provided an object label, suggesting that they intended to ask about the object's function and persisted to get this information. Children were also more likely to change the form of their ambiguous questions to more specifically target functional explanations in the object label condition. Together, these studies suggest that young children are sensitive to when they have gathered sufficient information to address their questions. In the majority of this work, the social context influenced children's stopping decisions by giving them the information they desired. 

However, social contexts can shape children's stopping decisions in other ways. A recent body of research shows that adults' demonstrations of pedagogy directly influence children's decisions about whether to persist in exploration. For example, @bonawitz2011double showed that preschoolers spend less time exploring an object and are less likely to discover alternative object-functions after an adult explicitly taught a single function [@bonawitz2011double]. The explanation for this effect is similar to the pedagogical inference work reviewed in the "Answers" section. A pedagogical demonstration by a knowledgeable teacher provides evidence for that function and against the existence of other functions; otherwise, the teacher would have demonstrated the other features. We can reconstrue this finding as an effect of social input on children's stopping rules. When the social context indicates that there is less to learn, children adopt a lower threshold for ending their search.

It is not the case that information acquired in social contexts always reduces information search. In fact, @butler2012preschoolers study of children's inductive inferences provides evidence that a pedagogical demonstration leads to an increase in exploration. Preschoolers saw an unfamiliar object and learned a novel causal property (that the object could magnetically pick up paper clips). In one condition, the experimenter demonstrated the property with a pedagogical framing ("Look, watch this!"). In the other condition, it was an accidental demonstration ("Oops!"). After the pedagogical demonstration, children spent more than twice as much time exploring the objects and generated three times as many attempts to make the objects pick up the paper clips. 

These are seemingly contradictory effects of pedagogy on children's stopping rules. However, they both arise because socially transmitted information is more informative and warrants stronger inferences. In the causal learning case, the stronger inference is about the lack of alternative object-functions, leading to less exploration. In the inductive inference case, the stronger inference is about the generalizability of the causal property, leading to more exploration. These findings also highlight the useful distinction between social information available in the moment and social input acquired from previous interactions.

Understanding why children decide to stop gathering information is a promising area for future research. Studies could focus on children's developing capacity to reason about the cost of actions for themselves and others. This cost term is critical to deciding when it is not worth gathering additional information. In fact, recent theorizing in the field of social cognition proposes that intuitive reasoning about the costs/benefits of others actions is the core of our social cognition. @jara2016naive describe this idea as a Naive Utility Calculus where, "... human social cognition is structured around a basic understanding of ourselves and others as intuitive utility maximizers." (p. 589). 

There has also been a growing interest in developing "cost-sensitive" active learning algorithms in the field of machine learning [@haertel2008return], with researchers beginning to define costs in increasingly sophisticated ways. For example, @settles2008active point out that the cost of information gathering should not be measured as a reduction in the number of training trials if those training trials vary in length because specific questions are more challenging to answer. Thus, an efficient active learner should want to ask questions that maximize information gain, but they should also take into account the cost incurred by others (e.g., time or mental effort) to provide that information. This idea is fundamentally psychological in that it expands the utility computation to include some measure of how our behavior affects others' actions and/or mental states. Another open question is how children develop skill in reasoning about more complex costs (e.g., reputation management), and how children integrate their costs with the costs incurred by others.  

## Conclusions

In this chapter, I proposed a way forward for integrating active and social learning theory. I argued that the formal framework of Optimal Experiment Design (OED) is a useful way to characterize the effects of social contexts on children's active learning. The OED framework defines information seeking as a process of expected utility maximization for gaining information. There are four model components -- goals, hypotheses, questions, and answers -- and other factors that are important but exist outside the model such as stopping rules. I used the OED decomposition to bring social learning phenomena into contact with active learning theory, and I suggested that the social context can influence children's active learning by: 

  1. communicating and/or triggering a diverse set of goals both informational and/or social
  2. shaping the content of children's hypothesis spaces both in-the-moment and/or over a developmental timescale
  3. serving as a model of possible and useful queries for children to imitate
  4. providing useful and generalizable answers to children's queries
  5. modulating when children decide to stop collecting information 

The heart of this proposal is that an integrative account of active learning within social contexts represents a valuable step towards understanding cognitive development. I have tried to argue that the social and active learning accounts have much to be gained by considering the other. Active learning accounts benefit by understanding how learners function within social contexts. This social information can allow researchers to create more sophisticated utility functions that take into account the social goals that people consider when deciding what to learn. This seems especially important for characterizing children's active learning since observational studies of learning environments suggest that opportunities to learn from social interaction are ubiquitous.  On the other hand, researchers interested in social learning can benefit from advances in the field of active learning by connecting their ideas to the rich traditions of machine learning, decision theory, and statistics. Moreover, children's information seeking decisions are often used as dependent variables in studies of social learning phenomena. Thus, a secondary benefit would be a deeper understanding of the factors that influence the measurement of social learning effects.

Finally, I think research on active learning could move beyond studies that lack a social context and begin to document the presence of learning goals, constrained hypothesis spaces, and the quality of answers in children's everyday experiences. This line of inquriy falls out of the integrative approach emphasized In this chapter. It will require a shift from relying on highly-controlled lab experiments of children's active learning skill to leveraging large-scale, observational datasets. And while this approach adds complexity to our experiments and models, I think that the benefit will be a far greater understanding of how children's active learning operates over fundamentally social input.  
