```{r, include=FALSE}
knitr::opts_chunk$set(echo = F, cache = T, warning=F, message=F, 
                      fig.width=4, fig.asp = 0.618, out.width = "90%", 
                      fig.align = 'center', fig.pos = 't')

source(here::here("index/disseration_helpers.R"))
intro_figs_path <- "index/chapter_child_rmds/ch1_goal_account/figs/"
table_path <- "index/chapter_child_rmds/ch1_goal_account/tables"

```

## Introduction

Imagine that a stranger on the street approached you and asked: 
“I’m sorry to bother you, but could you tell me the way to the city hall?”
Regardless of your answer, you probably would not feel puzzled or offended by the way in which the stranger decided to seek information that he needs. 
This is in contrast with a different situation where the stranger said to you instead: “Tell me the way to the city hall.” 
In such case you would immediately notice the lack of politeness in his utterance, and your response to him may be negatively affected by the irritating oddity of the situation. 
Now imagine another context where a person was wearing a new, flashy dress, and her friend thought the dress was hideous. 
It may actually be more surprising if the friend truthfully said "Your new dress is ugly," than if the friend decided to lie and say "Your new dress is gorgeous!"
But why? Why are people expected to speak politely, when there are alternative utterances that can convey information about the world or the speaker’s intention more directly (“Tell me the way”) or truthfully (“Your dress is ugly”)?
					
Language is a virtuous tool that serves many functions. 
Through language, people communicate information about the world, but also form their social relationships and establish their identity within their society. 
On one hand, some theories of language functions describe language as a transmission device for transferring from a sender to a receiver information that reflects context or the state of affairs [@buhler1934; @shannon1948; @jakobson1960]. 
The importance of informativity is further emphasized in more recent, influential theories on pragmatics of natural language, which explain how meanings beyond literal meanings of utterances arise [@grice1975; @searle1975]. 
On the other hand, some linguistic theories, especially those with references to language development, identify social roles of language that people use to make contact with others and form relationships [@halliday1975; @ervin1967]. 
These theories underscore how linguistic rules that language users tend to follow represent the norms and structure of the community using the language [@ervin1969].

Could polite speech reflect both the informational and the social roles of linguistic communication? 
Previous theoretical accounts of polite speech vary in their focus on informational versus social aspects of polite language. 
Some theories view polite speech as reflecting social rules and norms [@watts1992], 
some as abiding by communicative maxims that people are expected to follow in conversations, to be both as informative and as affirmative of their conversational partner as possible [@lakoff1973; @leech1983], 
and yet some others as performing face management, or trying to maintain interactants’ good public self-image or reputation [@brown1987].

In this Chapter, I propose that that polite speech highlights both informational and social uses of language: 
Polite speech reflects a principled tradeoff between the informational, epistemic content a speaker wants to convey (e.g. “I want you to tell me the way to the city hall”) and other social concerns, such as prosocial or self-presentational goal that the speaker wants to express for herself and others (“I’m not rudely commanding you to tell me the answer, but making a request in a respectful way”). Thus, my goal is to unify previous theoretical frameworks in one, goal-driven account of polite speech. 
In what follows, I will describe the goal-based account of polite speech in detail (Part I), and summarize previous models and theories of polite speech and situate them within the framework of the current goal-driven account (Part II). 
Then I will examine empirical evidence for goal-driven approach to polite speech: In Part III, I will focus on empirical work on adult production and comprehension of polite speech which show that adults reason about speaker goals in polite speech; and in Part IV, I will probe empirical evidence from developmental work that children’s production and understanding of polite speech advance as they grow older. In doing this I will show that children’s production and comprehension of polite speech is related to the relative complexity of polite speech based on its goal tradeoff.

## Part I: A Goal-based account of politeness

What does it mean to speak politely? 
Common instances of polite speech that occur to one’s mind probably include the simplest politeness markers, such as “please,” “thanks,” and “sorry.” 
More complicated examples would involve ways in which, for example, a person make a request: under normally conceivable circumstances, 
it would certainly be more polite to ask “Would it be too much trouble to ask you to complete this survey when you’re not too busy?” than to say “Do this survey now.” 
The word "polite" can sometimes carry a negative undertone in its meaning, as in “she was just being polite,” which is likely to mean the speaker was hiding her genuine beliefs or intentions to make the listener feel good. 
From these examples, we can identify a few characteristics that a polite utterance may exhibit: observance of social rules, relatively high degree of elaborateness or indirectness, and dishonesty or disingenuousness in the interest of others’ feelings or reputations.
					
More formal definitions of the term politeness also reveal common features that polite speech shows. Cambridge and Oxford Dictionaries respectively define what it means to be polite: “behaving in a way that is socially correct and shows respect for other people’s feelings”; and “courteous, behaving in a manner that is respectful or considerate of others; well-mannered” [@oxfordPolite; @cambridgePolite]. 
Similar to the previous examples of polite speech, these definitions suggest politeness involves (1) observance of social expectations and (2) respect for others. 
@boyer1702’s The English Theophrastus: of the Manners of the Age, compilation of texts describing the English life in the early eighteenth century, identifies a purpose in trying to be polite: “Politeness may be defined as a dextrous management of our Words and Actions whereby *men make other people have a better Opinion of us and themselves* [emphasis added].” Thus, according to the Theophrastus definition, speakers speak politely in order to boost the self-images of the interactants (both the speakers themselves and their addressees).
					
These common themes of politeness have been identified by previous theoretical accounts of polite speech (reviewed in detail in Part II). But each of the accounts only focused on certain aspects of polite speech but disregarded others, and their explanations for politeness have been viewed as largely disparate. 
Here I make a unification proposal, where these existing approaches to polite speech can be united under a single goal-based account of polite speech.

I propose that polite speech reflects a tradeoff between different communicative goals, three of which I describe here^[I do not intend to argue that this list of goals or their definitions are exhaustive; I come back to the possibility of other relevant speaker goals in Conclusion.]: informational, prosocial, and (self-)presentational. 
*Informational goal* has to do with the speaker’s desire to convey the most accurate information in the most efficient manner. 
*Prosocial goal* is about the speaker’s desire to retain the listener's acceptable self-image as a decent individual and as a reputable member of society. 
*Presentational goal* reflects the speaker's desire to present the speaker herself in a good light, to appear to be a kind and helpful individual. Below I describe each goal in more detail.

### Informational goal

A speaker’s informational goal, i.e. to prioritize information transfer in communication, may involve two closely related notions: informativity and truthfulness. 
Informativity is the notion of conveying the intended meaning in the most efficient and precise manner possible. 
The idea of informativity here is similar to @grice1975’s notion of cooperativity: 
A speaker will cooperatively choose utterances such that the listener can understand her intended message. 
Thus, the current notion of informativity that I adopt will encompass the whole Cooperative Principle (CP) that Grice posited (“Make your contribution such as required by the purposes of the conversation at the moment”), and especially the Maxim of Quantity (“Make your contribution as informative as is required”), 
though Maxims of Relevance (“Be relevant”) and Manner (“Be perspicuous”; i.e. be brief, orderly, and unambiguous) can also be relevant to the notion of informativity as I discuss in this Chapter.
					
The idea of informativity has been formalized in probabilistic (Bayesian) models as a utility function of a speaker with particular goals in mind. The “rational speech act” (RSA) theory of language understanding (see @goodman2016 for a review) assumes that listeners expect speakers to aim to be helpful yet parsimonious, choosing their utterances approximately optimally based on a communicative goal (e.g., inform the listener) and interpret an utterance by inferring what the helpful speaker meant based on the utterance and any other relevant information about the world. The theory defines a standard, informative utility as the amount of information a literal listener ($L_0$) would still not know about world state ($s$) after hearing a speaker’s utterance ($w$):
					
$$U_{epistemic}(w; s) = ln(P_{L_0}(s | w))$$
					
where the utterance choice is approximately rational (i.e., in proportion to the expected utility gain) and $w$ is chosen from a set of alternative, relevant utterances.
					
For example, if Bob asked Alice “How was my cookie?” and Alice said to Bob “It was good,” with only the goal to be informative in mind, Bob would think that Alice was being maximally informative by using the word “good” instead of another relevant, stronger word such as “amazing,” and infer that Ann meant “good but not amazing” because otherwise Ann would have used the word “amazing” instead.
					
I note here that Ann’s speech act could be analyzed as having observed the Gricean Maxim of Quantity, by making her utterance maximally informative, and Bob’s inference as being based on such assumption that Ann’s utterance is as informative as is required to meet Bob’s needs. But as the comparison between the former goal-directed analysis and this latter maxim-based analysis may reveal, the maxim-based account is difficult to formalize [@hirschberg1985] whereas the goal-directed view allows for quantitative account of factors contributing to the linguistic phenomena at hand [@goodman2016]. 
From here on, I take the goal-directed view rather than the Gricean maxim-based view of the speaker; 
thus, analyses of speakers and their utterances will be based on speakers’ communicative goals to convey information, etc., rather than their observation or violation of Gricean maxims.
					
Informational goal can also involve truthfulness: the meaning that accessed by the listener should match the true state of the world as closely as possible. 
In other words, the speaker will want to convey what is true (to the extent of her knowledge), not what is false. 
For example, if Bob baked some cookies and they tasted terrible, and Alice had the goal to be truthful, she would want to convey what matches the true state of the world as closely as possible (“Your cookies tasted terrible”). On the other hand, if Alice remarked to Bob about his cookies “Your cookies tasted good,” with goal to be informative and truthful, the true state of the world must be such that Bob’s presentation was truly good (but probably not amazing, because otherwise Alice would have said that it was amazing), and not bad or terrible.
					
As for when speakers decide not to tell the truth, there is a difference between violating versus flouting of truthfulness (which Grice also discusses; see @grice1975, p. 49, 53). 
Flouting involves contradicting common knowledge shared between the speaker and listener about the true state of the world, such that the listener notices that the utterance meaning does not match the true state. 
For example, after Alice and Bob together watch a movie that was obviously gory and disturbing to both of them, 
if Bob says “well, that was a really happy, fluffy movie!” then his utterance would be flouting truthfulness goal, 
and Ann would recognize Bob’s utterance as an ironic one. 
On the other hand, violating truthfulness does not hold assumption of such common knowledge of the true state of the world, and thus the listener may not notice the mismatch between the utterance meaning and true state of the world, although the listener can potentially access it through other means (e.g. realizing that the speaker had reasons to lie). 
Here I will mainly focus on violation, not flouting, of truthfulness, for example when speakers tell white lies (i.e., when the speakers do not intend that the listeners know what the truth is).
					
Speakers’ informational goal to be informative and truthful may encompass communicative cooperation in both locutionary and perlocutionary senses. A locutionary goal deals with conveying the intended meaning of the utterance within a conversation, whereas a perlocutionary goal involves achieving the speaker’s ultimate goals toward the listener [@attardo1997]. 
What could be an informational goal in its perlocutionary sense? 
In being truthful, speakers may ultimately want to maintain their moral obligation to tell the truth to others. This obligation is in line with Western philosophers’ argument throughout the history that it is morally wrong to lie [@augustine1952; @kant1949], although there have been debates on whether the degree of wrongness may depend on context [e.g., if the speaker was telling a white lie; @sweetser1987]. 
For example, if Alice said to Bob “Your cookies were good,” Alice’s locutionary goal would be to convey to Bob her intended meaning that his presentation was good (but perhaps not amazing), whereas her perlocutionary goal would be for Bob to think that the presentation was good, which was (apparently) the truth; Alice thereby upholds her moral obligation to tell the truth to Bob. Alice’s goal to be truthful, then, is achieved in both locutionary and perlocutionary senses.

Besides an informational goal, a speaker may also want to address concerns that are social in nature: having to do with interacting and maintaining good relationships with other people. 
Below I describe two related but different goals that speakers may want to accomplish for social reasons: prosocial and presentational. 

### Prosocial goal

A prosocial goal involves the speaker’s desire to to follow social norms and make others feel happy and respected. 
Speakers can try to accomplish the prosocial goal in several ways, one of which is social norm observance: abiding by social norms and expectations. 
There may be simple rules such as “say please when you make a request” or “say thanks to express gratitude,” but sometimes the norms can be more complex.
Speakers should avoid saying utterances that are *too* polite, to the extent that the utterances become marked and are no longer considered “optimally polite.” 
For example, a request for opening a window by saying “Sorry, could you open that window behind you? Thanks.” would be a normal, socially expected way to make the request; 
but a request such as “I’m so terribly sorry to bother you with this irritating request, but if you don’t mind, would you care to open that window behind you, only if it’s not going to be too much trouble for you?” would be a signal to the addressee that something in the situation is odd and marked; 
either that the request involves a higher cost than is normally expected for opening a window, or the speaker is unusually afraid of incurring a debt to the addressee, etc.
This principle of social norm observance is then parallel to Grice’s Cooperative Principle, in that the CP outlines normative expectations for a speaker who wants to convey information as efficiently as possible, whereas the current principle of social norm observance deals with normative expectations for a speaker who wants to maintain social order. Thus, if the CP is a principle of information transfer, social norm observance is a principle of social order. Both principles call for unmarkedness of utterances, and when the utterances are marked due to a violation of its rules, then the listener will try to infer reasons for such violation.

Speakers may also try to be prosocial through face management. 
*Face* is a notion introduced by @goffman1967, and represents an individual’s publicly manifest self-esteem. 
He argued that people perform interpersonal rituals whereby face maintenance is a fundamental condition of the interactions. 
Goffman identified two kinds of faces that people want to maintain: *positive face*, or the want for solidarity or approval from others, and *negative face*, or the want to be free from imposition. Interactants will always want to preserve each other’s face, and so potential face threats will somehow have to be modified. 
@brown1987 suggested that a strategy for such facework is politeness, which they defined as deviation from Gricean informativity (described in detail in Part II).

For example, a request such as “You couldn’t possibly pass the salt, could you?” would be an example of negative politeness strategy [i.e. a strategy to save negative face; @brown1987, p. 136] as the speaker is being pessimistic about the compliance of her request and not assuming that the listener has to be willing or able to do any acts predicated of him. 
On the other hand, utterances that emphasize the common ground between the speaker and listener (i.e. that the speaker and listener share the same goals, values, knowledge, etc.), and address the fulfillment of the listener’s want are positive politeness strategies; for example, “What a beautiful vase this is! Where did it come from?” [@brown1987, p. 103] saves the listener’s positive face by attending to the listener’s wants and interests. 
When face management is in conflict with informational goals, the meaning of utterance would differ depending on which goal the speaker decided to prioritize. As described earlier, if Ann said to Bob, “Your presentation was good,” and she wanted to prioritize informational goals only, then her utterance would indicate that Bob’s presentation was truly good (though perhaps not amazing). 
However, if Ann spoke with a prosocial goal to save Bob’s face and wanted to boost his self-image instead, then Bob’s presentation actually could be bad rather than good.

### Presentational goal

Language also reflects a speaker’s goal to present themselves in a good light, thereby saving the speaker's own face. 
This last goal is related to the informational and prosocial goals previously described,
in that speakers must be mindful of the listener's want to be informed or to maintain his positive self-image, 
but instead of actually *being* maximally informative or prosocial, presentational goal concerns *appearing* to care about these goals.
Thus, a speaker may engage in a recursive reasoning about a listener who thinks about a speaker who wants to be informative and/or prosocial, 
and then can produce utterances to make the listener *think* that the speaker is being informative, being prosocial, or both of those things. 

The pursuit of self-presentational goal can often lead to the same outcome as the pursuit of informational or prosocial goals. 
For example, if the listener asks for feedback about his performance that was truly good, all three goals - namely, informational goal to give the listener accurate information, social goal to make the listener feel good, and self-presentational goal to appear to be an informative and kind speaker - align such that they can lead to production of similar utterances, such as “Your talk was amazing.”

There are however situations in which each of the three goals has different consequences: if the listener’s performance was truly bad, then the speaker would need to consider which goal to prioritize. The pursuit of informational goal would lead to informative but harsh utterances such as “Your talk was bad.” Prosocial goal would yield nice-sounding but misleading utterances such as “Your talk was great.” 
On the other hand, a speaker who wanted to *appear* to be informative and kind at the same time may produce a different utterance, such as “Your talk wasn’t bad,” or “It’s hard to give a good talk.” 
The speaker could thereby convey to the listener that there were reasons she could not produce a simpler, more direct utterance, and make the listener think that his performance was probably unexciting but the speaker was too kind to say it explicitly 
(see Chapter 4 for the formal definition and more detailed description of the presentational goal). 

## Part II: Previous theoretical accounts of polite speech
					
In Part II, I aim to (i) describe different classes of theoretical approaches to the understanding of polite speech; (ii) for each class, explain how the approach can be situated within the current proposal for the goal-based account for polite speech; and (iii) discuss what advantages the goal-based account can offer beyond the existing approaches. 
Summary of prominent theories and their implications within goal-based framework can be found in Table\ \ref{tab:litRevTable}.

\newpage
\blandscape

```{r litRevTable, results = 'asis'}
lit_rev <- read_csv(here::here(table_path, "lit_review.csv"))

lit_rev %>%
  replace(is.na(.), "") %>%
  kable("latex", 
        booktabs = T, 
        caption = "Summaries of previous theoretical approaches to polite speech and their implications within the current goal-based framework.",
        caption.short = "Review of existing theories of polite language") %>%
  kable_styling(latex_options = "scale_down") %>% 
  row_spec(row = 0, bold = TRUE) %>% 
  column_spec(column = 4, width = "8cm") %>% 
  column_spec(column = 3, width = "8cm") %>% 
  column_spec(column = 2, width = "5cm") %>% 
  column_spec(column = 1, width = "3cm") 
```

\elandscape

### Politeness as observance of communicative maxims

One approach to polite speech is largely based on the Gricean perspective, and claims that conversation is driven by general communicative principles, and politeness is a maxim (or made up of maxims) that accompanies other principles. Whereas Grice focused on principles that speakers follow to make their speech maximally ecient for information transfer, he also noted: “There are ... all sorts of other maxims ..., such as ‘Be polite,’ that are normally observed by participants in talk exchanges” [@grice1975, p. 47]. @searle1975 discussed conditions of performing indirect speech acts (e.g. “Can you pass the salt?”) for which, he claimed, “politeness is the chief motivation” (p. 76). Thus, Grice and Searle both identified politeness as a driving factor in communication, but the concept of politeness was largely undeveloped at the time.
					
The communicative maxim approach for polite speech expanded with proposals for conversational rules and principles that govern polite speech. 
@lakoff1973 suggested a set of rules (“Don’t impose,” “Give options,” “Be friendly”) that underlie utterances that are polite, and thus deviate from directly expressed meanings. 
@leech1983 developed a similar proposal to Lakoff’s in greater detail, proposing Politeness Principle (PP), which is complementary to the Gricean CP. Leech argued that the PP, like the CP, can be subclassified into more specific maxims: 
Maxims of Tact, Generosity, Approbation, Modesty, Agreement, and Sympathy. 
The primary postulate of the PP is that interactants prefer to express polite beliefs, which are beliefs that are favorable to the other person (and/or unfavorable to oneself). 
For example, Approbation Maxim states that a speaker observing the PP will minimize dispraise, and maximize praise, of the other person (e.g. “Your dress looks gorgeous!”), whereas Modesty Maxim states that a speaker will minimize praise, and maximize dispraise, to the speaker herself (e.g. “This is just a small gift, but I hope you like it” downplaying the value of the gift). 
@gu1990 proposes addition of “Balance Principle” to the set of politeness maxims,
where favors from A to B are balanced by favors from B to A, such that the PP can function to maintain social equilibrium.

Based on the goal tradeoff framework, it becomes possible to translate different politeness maxims and their utterance predictions in terms of the set of goals (informational, prosocial and presentational) that I argue for.
The Approbation Maxim expects a speaker to produce utterances that minimize dispraise such as "you could be more careful." This utterance can reflect that the speaker has: (1) informational goal to convey that the listener *should* or even *must* be more careful; (2) prosocial goal to not criticize explicitly (e.g., say "you are so careless"), which may hurt the listener's feelings; and (3) presentational goal to appear as someone who cares about both of these goals mentioned.

The Maxim of Agreement, a different maxim proposed by Leech, can also be re-interpreted in terms of goal tradeoffs. The Maxim of Agreement predicts speakers to "mitigate disagreement by expressing ... partial agreement" [@leech1983, p. 138], for example in a conversation where A says "The book is tremendously well written" and B follows, "Yes, well written as a whole, but there are some rather boring patches, don't you think?"
If we construe *agreement* as approval of one's opinion by otherss, which can boost one's self-image (face), then we can also translate the speaker B's desire behind her utterance as reflecting: (1) presentational goal to appear to agree with A ("True"); and (2) informational goal to convey some disagreement ("but...").
In this way, the goal tradeoff framework can help unify interpretation of utterances based on just a few underlying goals, instead of relying on many distinct categories of maxims to classify each utterance as its unique kind.

### Politeness as strategy for facework
					
Another approach to analysis of polite speech that has been highly influential is the model of politeness as face management, developed by @brown1987. The model is primarily based on the concept of face [@goffman1967] that deals with an individual’s public persona (introduced earlier in Part 1). @brown1987 take a strategic approach to politeness, and focuses on strategies that speakers employ in order to avoid, redress, or mitigate threats to face (either the addressee’s or the speaker’s own). Like the communicative maxim approach, @brown1987’s account also start at the assumption of the Gricean CP, and attribute the cause of a speaker’s deviations from the CP to the speaker’s desire to be polite. Thus, given a speaker’s desire to save face, the more an utterance deviates from maximal informativity, the more “polite” (face-saving) the utterance will be.
					
Within the goal-based framework, it can be said that @brown1987 recast the notion of a cooperative speaker as one who has both an informational goal to improve the listener’s knowledge state as well as a social goal to minimize any potential damage to the hearer’s (and the speaker’s own) face. With the idea of these conflicting goals, Brown and Levinson’s theory is conceptually closest to the current proposal among all theories to be discussed. Specifically, they primarily focus on the conflict between goals of social face management and epistemic informativity. For example, by saying “Can you please open the window?” instead of “Close the window,” the speaker decides to sacrifice informativity (i.e. maximally efficient transfer of the intention for the addressee to open the window) in order to save the addressee’s negative face (i.e. freedom from imposition or order from others). Another example of negative politeness (i.e. strategy to save negative face) is a speaker fronting his gift-giving by saying “This is just a small gift” in order to emphasize that the listener is not incurring too much debt to the speaker and thus not being imposed a burden to return the favor. On the other hand, positive politeness or act of saving positive face can be exemplified by utterances that emphasize approval of the listener’s interest or performance, e.g. “What a fantastic garden you have!” [@brown1987, p. 104].
					
One drawback in @brown1987 is that key elements required for analysis of speakers’ goals or intended meanings are ambiguous and difficult to formalize. The core assumption of Brown and Levinson’s analysis is that deviations from Gricean maxims (that prioritize the match between the literal and intended meanings) lead to increase in politeness. In order to estimate the degree to which speakers try to be polite, there should be a way to measure the degree of deviation from the Gricean maxims (i.e. the degree of mismatch between the utterance surface meaning, intended meaning, and true state of the world; see Section 1 for how these factors can be formalized e.g. in RSA). However, Brown and Levinson do not provide a way to formalize the literal or intended meaning or the state of the world. For example, it is unclear how much deviation from the Gricean maxim(s) occurred when a speaker produced an utterance such as the example previously mentioned: “What a fantastic garden you have!” Since the authors do not provide the true state of the world (i.e. how beautiful the garden actually was in the speaker’s opinion), it is difficult to define or quantify the speaker’s effort for politeness or the cost of face threat the message would have involved given an alternative utterance (“It is a mediocre garden you have.”) A clearer identification of the true state of the world, the speaker intended meaning, and the set of relevant alternative utterances, and a way to formalize these elements, will help with quantificational analysis of polite utterances.

Another issue is in @brown1987's construal of face, namely that it is difficult to distinguish between the speaker's desire to save the listener's face and their want to boost the speaker's own self-image. For example, by saying “What a fantastic garden you have!” the speaker is not only making the listener feel good, but also presenting the speaker herself as someone who is generous and likes to compliment others. 
Brown and Levinson's analysis did not explicitly differentiate the other-oriented versus self-oriented face-saving goals, but they can have important implications for situations in which the two goals lead to different choices. 
For example, if a speaker simply wants to save the listener's face, the speaker may produce an utterance that is unambiguously nice ("Your dress is gorgeous!"). 
However, if the speaker wants to inform the listener of some harsh truth but still wants to save his own face and *appear* to the listener to care about her feelings, the speaker might say something that is more indirect and vague, like "I thought your other dress was very beautiful, how about wearing that to the party?"
Distinguishing the other-oriented and self-oriented social concerns thus will help make more precise predictions for what speakers say and how listeners understand polite utterances. 

@spencer2000 put forward another theory based on Goffman’s notion of face; it is a more general model of rapport management, or management of interpersonal relations, distinguished from face management as proposed by Brown and Levinson. Spencer-Oatey challenges Brown and Levinson’s distinction between positive and negative face, and argues that the former involves the concept of face, or the positive social value claimed by a person, whereas the latter does not concern face but rather what she calls “sociality rights,” or a person’s entitlements in interactions with others. She then further proposes that face management and sociality rights management each has both personal components (concerning self-esteem and individual identity) and social components (concerning social role and entitlements within relations with others). Spencer-Oatey then largely focuses on speakers’ attempt to balance between general epistemic goals and both face management and social expectations. Thus, in saying “This is just a small gift, but I hope you like it” the speaker may not only be concerned about the speaker’s and the listener’s faces as individuals but also the conventional social obligations associated with gift-giving that the speaker and listener are expected to follow through. However, similar to Brown and Levinson’s analysis, Spencer-Oatey’s analysis is limited in that it does not identify or formalize the epistemic knowledge (the speaker intended meaning and true state of the world) behind utterances, making it difficult to quantitatively analyze the goal tradeoffs.

### Politeness as social rules and norms

Another set of theories for polite speech relies on the notion that politeness deals with following social norms and expectations. One line of theory argues for the need to distinguish between marked, strategic polite behaviors versus unmarked, normative “politic” behaviors. @watts1989 defines “politic” behavior as “socio-culturally determined behavior directed towards the goal of establishing and/or maintaining in a state of equilibrium the personal relationships between the individuals of a social group, whether open or closed, during the ongoing process of interaction.” For example, “May I open the window behind you?” will be a normative, politic statement if used in a formal setting or said to a stranger, but can be considered marked, overly polite statement when said to a close family member.
					
@watts1992 posited that examples of polite speech in Brown and Levinson’s work, such as honorifics or indirect speech acts, will be considered “polite” only if they go beyond their normal usage as socio-culturally constrained forms of politic behavior. For example, according to Watts, responding to an offer “Would you like some more co↵ee?” by nonsaliently saying “Yes, please.” [@watts2003, p.186] should be considered a politic behavior. On the other hand, if the response is instead “Yes, please, that’s very kind, coffee would be wonderful.” @culpeper2011 is considered to be polite as it is “perceived to go beyond what is expectable” [@watts2003, p.19]. Based on these observations, @locher2005 claim that, a better approach than Brown and Levinson’s “facework” to encompass all degrees of polite speech will be a larger “relational work” that considers all-ranging levels of politeness from marked im/polite to unmarked politic utterances.

Watts and colleagues’ claim can be re-framed as calling for the need to consider wide-ranging informational-social tradeoffs. Watts’ distinction between politic versus polite speech lies in whether the addressee recognizes and pays attention to the divergence between speakers’ informational and social goals, as revealed by the discrepancy between literal versus intended meaning, and tries to infer the intended meaning. For politic utterances, the mismatch between literal and intended meaning is unmarked and thus remains unnoticed; For polite utterances, the mismatch is salient and the listener is called to pay attention to the reason for that mismatch, and to infer what a speaker was truly trying to say or what the speaker truly believed (i.e. the true state of the world).
					
One benefit of the current goal-based account over Watts et al.’s claim is that there is no need to classify different kinds of polite speech as different categories (polite vs. politic). Rather, by observing how subtle changes in the literal meaning, intended meaning, or the true state of the world can lead to changes in a speaker’s inferred goals or evaluation of politeness, one can examine the phenomenon as a whole. Watts et al.’s theory makes it rather difficult to know exactly what utterances count as polite vs. politic; for example, should the utterance “This is just a small gift, but I hope you like it” produced in a gift-giving act be considered politic or polite? The goal-based framework obviates this need and quantifies the relative degree of politeness in terms of goal tradeoff.

Other theorists have focused on speakers’ attempt to abide by societal obligations and expectations, explicitly distinguishing between their accounts and “strategic” approach to politeness based on individual goals [e.g., @brown1987]. @fraser1981 put forth an account for politeness based on the idea of “conversational contract” (CC), which posits that interactants bring a set of rights and obligations to the conversation. Observance of these obligations, according to these authors, are not strategic but rather “getting on with the task in hand in light of the terms and conditions of the CC” [@fraser1990, p.233]. Critiques of polite speech analysis based on facework by sociolinguists [@matsumoto1988; @ide1989; @mao1994] assert the importance of considering speakers’ desire to fulfill societal obligations. They go against Brown and Levinson’s notion of “negative face” as it is heavily loaded with the assumption of individuality as opposed to group identity, which especially becomes prominent in East Asian cultures and languages. Thus, they may argue that an utterance such as “This is just a small gift, but I hope you like it” in East Asian cultures may not reflect an attempt to save the listener’s negative face, but to follow convention based on their assigned role (e.g. within a hierarchical social structure).
					
The proponents of social obligation approach for politeness focus primarily on speakers’ prioritization of observance of social norms over informational goals. This approach rejects the assumption of universality of face management principles claimed by Brown and Levinson, and argues that in some cultures the need for face-work (especially for individuality) may be weak or non-existent. Instead, a speaker may desire to follow and reinforce social norms and expectations, and decide how to balance between that desire and the goal to transfer information. For example, if a professor is to accompany his long-time mentor to a restaurant, when it comes to time to pay, the professor may say “I insist, you should let me pay for this - please treat me next time” despite thinking that he doesn’t actually want to pay the bill, because it is more important to hide his genuine intentions to abide by what is expected of him as as a lower-status individual.
					
The goal-based framework aims to simultaneously acknowledge the importance of these theories identifying more subtle cases of politeness and unify them with the work for face-saving strategies [e.g., @brown1987] they largely argue against. Whereas the social obligation theories attempt to reject the facework-based accounts of polite speech, the current proposal is that speakers consider both social obligation and facework as potentially important social goals, and try to balance between these social goals and epistemic goals to convey their message. Thus, instead of presuming mutual exclusivity of speakers’ goals either to save face or to abide by social rules, the goal-based framework instead assumes that both goals can apply simultaneously, to different degrees depending on the cultural or conversational context.

### Politeness in the game-theoretic approach

Finally, there have been recent attempts to analyze polite speech from a game-theoretic perspective, which assumes that individuals interact with each other in an effort to achieve their own goals. A few proponents of game-theoretic approach have analyzed indirect speech as a whole, viewing polite indirect utterances as a subset. @franke2016 argue that indirect speech used for demands results in greater likelihood of compliance from the other party, as indirect speech suggests higher stakes for the listener in case the speaker’s wants are not fulfilled. For example, a mobster who is trying to take protection money from a restaurant owner could pose a veiled threat by saying: “Your little daughter is very sweet. She goes to the school in Willow Road, I believe” [@franke2016, p. 19]. This indirect speech is used to communicate that the restaurant owner’s stakes are high because his daughter can get hurt if he does not pay the money, whereas mobster’s stakes are low because he is free to do whatever he wants in the neighborhood. @franke2016’s account thus focuses on the reasons to be indirect to send the informational message more effectively in the interest of the listener’s observance of the speaker’s wants, though the scope of their explanation does not explicitly cover polite speech.

Addressing a broader set of indirect utterances, @pinker2008 describe three possible reasons for speaking indirectly: allowing for plausible deniability and thus preventing (legal) responsibility for the intended meaning (“Ocer, is there some way we could take care of the ticket here?”), avoiding emotional costs of mismatch (such as awkwardness) in perceived relationship between speaker and listener, and generating common reference point that is qualitatively different from direct literal meaning even when the intended meaning is clear to the interactants (“Would you like to come up and see my etchings?”).
					
Other game-theoretic accounts addressed polite indirect speech specifically, highlighting its rationality despite its potential cost.  @vanRooy2003 argues that polite utterances are costly “handicaps,” which incur a social debt and reducing the social status of the speaker, but which are rationally used to communicate good intentions to the addressee. @quinley2011 observes that politeness is a form of “trust game,” where making a polite request is rational when assumptions of reputation or observation are in place over multiple iterations of conversational turns.
					
Game-theoretic approach is similar to the current goal-based approach in that the theory is very much built on the notion of tradeoff of goals, but differs in that it is ultimately focused on the speaker’s goals for the self. In game theory, a speaker’s informational goals are centered around informativity, or effective transmission of the message, to ultimately gain the desired compliance from the other party [@franke2016]. Similarly, a game-theoretic speaker’s social goals involve face management, but less of the intent to save the listener’s face and more to save the speaker’s own face, to avoid being held responsible for disobeying the law or disrespecting someone (plausible deniability) and to prevent high emotional costs misunderstanding common knowledge assumed between speaker and listener [@pinker2008]. The current proposal differentiates between speakers' interest oriented toward others (i.e., a genuine desire to inform others or save others' face), and interest towards the speakers themselves (e.g., a desire to *appear* to be a particular way). I formalize the self-interest based on a recursive reasoning about the other-oriented goals: Speakers reason about listeners who imagine speakers to be genuinely informative or kind, and then the speakers produce utterances that can portray themselves to be such helpful individuals. 

## Part 3: Empirical work on polite speech in adults
					
In previous sections, I have recapitulated previous theoretical perspectives to make a unifying proposal that speakers consider tradeoffs between informational and social goals (e.g., prosocial, self-presentational). In this section, I review empirical evidence from adult interpretation, evaluation and production of polite speech that show their consideration of speaker’s informational and social goal tradeoff.
					
### Interpretation of polite speech
					
Empirical findings show that adults’ interpretation of polite utterance meanings is based on the epistemic-social goal tradeo↵ considered by the speaker. For example, people’s interpretation of seemingly irrelevant, ambiguous utterances reveal that listeners pay attention to the epistemic-social tradeoff, attributing politeness as a strong reason for apparent irrelevance. @holtgraves1998 examined interpretations of replies to someone asking for an opinion on some performance that he just gave (e.g. “What did you think of my presentation?”), where the replies seemingly did not directly address the questions and involved relevance violations (“It’s hard to give a good presentation”). The author found that people often assign face-threatening meaning to the indirect reply. Additionally, people spent longer coming up with an interpretation when the true state was positive (the addressee actually gave a good presentation) or when the literal meaning of the reply was in the positive direction (“It’s easy to give a good presentation”), which thus made face management an unlikely goal. These findings overall indicate that people identify face management as a key motivation for violating the informativity goal, and struggled when face management was no longer a valid reason for violation of the goal to be informative to the listener.

Another prominent example of polite speech interpretation in line with the idea of the speaker’s goal tradeoff consideration comes from empirical work on cancellation of pragmatic inferences that are normally in force in non-face-threatening, low-stakes contexts. People’s inferences change for non-literal meanings of various quantifiers depending on the presence or severity of face threat toward the listener. For example, the term “possibly” could be used to convey a probability greater than 0 and up to 1 in its literal sense, but usually people assume that it denotes a probability that is neither too high nor too low. This is because people assume that a speaker would use quantifiers in the most efficient, informative way possible [@grice1975], and if the speaker wanted to convey a greater certainty then she would have used a stronger term, such as “certainly.”
					
However, when the situation involves a potential face threat or a high stake for the listener, the speaker would have a reason to be more vague, to accommodate for face-saving or plausible deniability. Indeed, Bonnefon and colleagues found that people interpret the word “possibly” as implying a greater likelihood when it is used to describe a condition of a higher stake (e.g. “You will possibly suffer from deafness soon” or “Your pain is possibly going to increase”) than a lower stake (“You will possibly suffer from insomnia soon” or “Your pain is possibly going to decrease”; @bonnefon2006; @pighin2011).

Similarly, people’s interpretation of other quantifier phrases such as “some” and “A or B” differ depending on the contexts. People usually endow upper-bounded meanings to “some” and “A or B” in non-face-threatening contexts assuming speakers’ epistemic cooperativeness [e.g., @huang2009a; @breheny2006]: “I ate some of the cookies” is interpreted to mean “... some of the cookies but not all,” and “she ate the cake or the salad” to mean “... the cake or the salad but not both.” In situations involving face threat, however, people make different inferences: “some” and “or” in “some of the audiences hated your talk” and “We will cut your salary or take away your company car” are interpreted in their broader sense [“some and possibly all” and “A or B and possibly both”; @bonnefon2009; @feeney2013]. Furthermore, a long pause before the utterance, signaling expectation of bad news to the listener, heightened the effect for the polite interpretation of “some” [@bonnefon2015]. In sum, people infer different non-literal intended meanings depending on the context, since the speaker is expected to focus more towards social, face-saving goal than towards epistemic goal in the presence of potential face threats.

### Evaluation of polite speakers’ intentions

People’s evaluation of strategies to be polite is also based on the balance of epistemic-social tradeoffs. @clark1980 showed that people rate politeness of requests differently depending on how much the literal meaning of indirect requests would benefit the listener or reduce the cost to the listener. For example, requests that implied that the speaker asked for the listener’s permission (“May I ask you?”) were rated as relatively more polite, whereas those requests that assumed the listener’s obligation to reply to the speaker (and therefore incurs a cost for the listener; “Shouldn’t you tell me?”) were rated as more impolite. Thus, with the increase of the maintenance of the listener’s face, to be free of imposition or obligation in this case, relative to the degree of message transfer (i.e. access to the intended meaning that was assumed to be constant; e.g. “Tell me the way to Jordan Hall”), people’s judgment for politeness of requests also increased.
					
Interestingly, hints that seem to prioritize face-saving due to its relatively high degree of indirectness are not always evaluated as most polite. According to @brown1987’s rank ordering of polite strategies, hints (i.e. indirect speech with meanings that are “off the record”) are supposedly more polite compared to other politeness strategies. However, empirical evidence is divided on this issue [e.g., @pinker2008; @terkourafi2002; @yu2011]. For example, @blumkulka1987 found that people rate conventional indirect requests (e.g. “Would you mind moving your car?”) as more polite than direct orders (“Move your car”) or hints (“We don’t want any crowding”). Along similar veins, among possible replies to a question asking for an opinion on a newly bought dress, people perceive evasive replies (e.g. “It seems like clothes are getting terribly expensive”) to be better than direct utterances (“I don’t think it looks very good on you”) or hints that sound irrelevant [“I’m going to take my vacation next month”; @holtgraves1986].

One potential reason why hints and irrelevant remarks are not evaluated as best politeness strategies is that they focus too much on face-saving but not information transfer, leading to a poor balance in epistemic-social tradeoff. Indeed, based on the results of her study, Blum-Kulka concluded that politeness is “interactional balance achieved between two needs: The need for pragmatic clarity and the need to avoid coerciveness.” This is in agreement with the current argument that people consider both the epistemic and social goals as important in communication, and the balance between these two goals determines what is optimally “polite.”

### Production of polite speech
					
Adult production of polite utterances reveal their attempt to balance between epistemic and social goals. Adults spontaneously produce requests in polite forms that do not convey their message in the most direct manner [@clark1980]. Even in situations of conflict, people try to balance between their desire to convey their message and desire to control their politeness level; indeed, speakers exhibit politeness strategies even while arguing, preventing unnecessary offense to their interactants [@holtgraves1997].
					
Sometimes people decide to compromise the level of unambiguity or certainty that is communicated to the listener due to social reasons. @holtgraves2016 tested what degree of (un)certainty with which people would communicate potentially face-threatening information. They found that if the event referred to was more severe (and therefore there is greater face threat involved) or if the person whose face was under threat was the listener (as opposed a third party) participants used terms with greater uncertainty. Thus, when there is a greater risk for face threat, and therefore more reason to prioritize face management, speakers sacrifice information transfer and convey information more ambiguously.
					
Situational factors can also lead speakers to prioritize epistemic versus social goals differently. @brown1987 claimed that the degree of the face-threat of an act is determined by three factors: the listener’s power status with respect to the speaker; the degree of social distance between the speaker and the listener; and the degree of imposition of the act (which may be culturally determined). Thus, a speaker’s attempt to minimize face threat would increase as these three factors increase in magnitude. If their claim is true, within the goal-based framework, speakers would prioritize face-saving goal relatively more as the effect of these sociological factors increase.
					
Indeed, empirical evidence suggest that the lower power status of a speaker, and requests with greater imposition, lead to greater degree of face-saving [@blum-kulka1985; @holtgraves1992; @lim1991; @leichty1991]. For example, in @lim1991’s study, participants were asked to write down their probable utterances in an imaginary situation involving a potential face threat and varying degrees of power status of the listener. The results showed that participants produced more “tactful” utterances with more indirect expression of amount of imposition on the listener (e.g. “I’d greatly appreciate it if you could write the paper on behalf of the whole group”) in a scenario involving equal power between the speaker and listener than when the speaker had higher power than the listener (e.g. “I know it’s imposing a lot, but you gotta write the paper again”).
					
Empirical work on the effect of distance on politeness has been more inconsistent where some report results that are consistent with Brown and Levinson’s claim that greater distance leads to higher levels of politeness [@holtgraves1992], while others report the opposite [@baxter1984; @brown1989]. One potential reason for the inconsistency can be that social distance may be confounded with affect (i.e. how much the speaker likes the listener). Nonetheless, regardless of the directionality, all three variables of power, distance, and degree of imposition affect speakers’ politeness level; in other words, speakers consider these factors to determine how much priority they should place on social goal to save the listener’s face as opposed to epistemic goal to effectively convey their message.

In sum, empirical work with adults reveal that people interpret, evaluate, and produce polite speech in ways that are consistent with the notion of the epistemic-social goal tradeoff.
					
## Part 4: Empirical work on polite speech in children

In this section, I argue that children’s acquisition of polite speech shows a pattern consistent with the goal-based account: Children show early competence with polite speech that involves minimal conflict between speaker goals, and gradually learn to produce and understand polite speech with more complex patterns of competition between speaker goals.
					
### Rule-based polite speech
					
Theories on children’s sensitivity to conventional rules predict children’s early understanding of simple, rule-based politeness (i.e. that does not involve explicit conflict between a speaker’s epistemic and social goals). In the domain of morality, @turiel1977 argued that children’s early-emerging understanding of social conventions is primarily based on rules and actions enforced by social authorities, and then the development of a more flexible person-orientation occurs throughout childhood. In other words, children may first start by following simple moral rules such as “do not cheat” or “do not steal,” but as they grow older they may become more flexible as they consider more complex circumstances depending on the needs of the individuals and society involved. In the context of polite speech, children may show similar developmental trajectory: they could first faithfully follow rules such as “say please” or “do not lie,” but as they become more sensitive to intricate demands of different individuals and contexts, they may start to try to balance between different goals to satisfy those demands. According to this hypothesis, children should start to show mastery of rule-based polite utterances, such as syntactic politeness markers (e.g. “please”) and conventional request forms (e.g. “Can you ...”), earlier than other more complex forms of polite speech (e.g. white lies).

Indeed, children start producing rule-based polite utterances early. From very early on, parents teach children to be polite by following normative rituals to say “please”, “thank you”, “hello” and “good-bye” [@gleason1984]. Children start producing the simple polite marker “please” early at 2.5 years [@read1978] and request forms increase in their variety and frequency with age [@bates1976; @bates1977; @ervin1982; @bock1981; @nippold1982].

Young children learn to produce these utterances with appropriate levels of politeness depending on context [e.g., @snow1990; @ryckebusch2004]. For example, children use different forms of requests depending on how they are instructed to make the requests. At three years, children start using different forms of request when they are instructed to “tell” versus “ask” an addressee to give them a puzzle piece [@bock1981]. Similarly, five-year-olds are able to modify requests depending on whether they are asked to make a request in a nice versus bossy way [@becker1986]. @bates1977 showed that even two-year-olds were able to modify their requests to make them more polite, when they were instructed to make a request to an old lady and then ask her again “in the nicest way possible.” However, children as old as seven fail to differentiate the meaning of “ask” and “tell” when asked @ervin1977 which suggests that production of context-relevant polite speech seems to precede the precise, conscious understanding of goals for speaking politely or impolitely.

Children are also able to adjust the level of politeness based on the listener age and status. Even at two years, children use a polite form of request (e.g. “Can I have...”) to an adult but an imperative form (e.g. “Give me...”) to a peer [@corsaro1979; @shatz1973]. Children around 2.5 years were to found to use less polite language with their fathers compared to their mothers [@ervin1984; @ervin1990].
These production behaviors are consistent with Brown and Levinson’s prediction that a speaker’s need for politeness strategy will be heightened as the addressee’s power status increases.
					
Furthermore, children make polite requests based on the degree of imposition of their demands, and respond sensitively to the resistance to get what they want. By five years, children produce polite speech that matches the cost of the request they make, using more polite forms of requests for apparently more costly impositions [@ervin1990]. @james1978 showed that four-year-olds adjusted commands to make them more polite toward older addressees, whereas when they had to make requests for getting what they want (which places higher cost on the speaker if the request is not met) children made the utterances maximally polite regardless of the listener status. @axia1985 showed that seven-year-old Italian children were able to adjust the polite level of request depending on resistance. Additionally, children in preschool years and older have been observed to repeatedly use the word “please” in their pleading to resistant mothers and peers, as strategies to get what they want [@finley1974; @kyratzis2001; @wilson2004]. Thus, children use politeness as a strategy to gain compliance for their goal in the intended message.

Comprehension of rule-based polite speech also seems to emerge early, though evidence is more gradual and controversial compared to production. Initial evidence seemed to suggest that producing a request with “please” is judged to be polite by three years of age [@bates1976; @bates1977]. However, in a study by @nippold1982, this judgment of “please” as polite was only replicated starting at five years of age, but not younger. Furthermore, in the same study, children did not differentiate between requests that adults judged to differ in politeness level (e.g. “Give me some candy, please” vs. “Can you give me some candy, please?”) until seven years of age. But these initial studies have a few unresolved issues, including the lack of statistical tests to assess each age group’s performance and lack of systematic manipulation of cues other than syntax (e.g., voicing or facial expressions). Thus, more evidence is required to confirm early understanding of conventional polite requests, but preliminary evidence so far suggests that children start to show some understanding of these requests before preschool years.

### Indirect speech
					
Now I turn to children’s production and understanding of polite speech that is more complex than simple rule-based utterances and reflects a strategic tradeoff between speaker goals. First, what do we know about children’s understanding of indirect speech, where informativity is compromised for social goals?

Despite the wealth of studies looking at conventional indirect requests and simple polite markers (“please”), very few studies have looked at children’s understanding of non-conventional indirect requests (e.g. hints); there is only limited evidence that comprehension of under-informative indirect requests is more difficult and is acquired at a later age than conventional requests. Bernicot and colleagues have tested French-speaking children’s abilities to evaluate implications of requests for which the intended meaning is distinct from the literal meaning. @bernicot1987 tested children’s ability to understand implications of directives in different forms: direct directives (e.g. “Give me the spade”) versus nonconventional indirect directives (“I can’t make a castle with my hands”). They found that even by six years, children have difficulty judging what would be an appropriate reaction by the speaker when the addressee does not comply with the directives. @bernicot2007 found some evidence that by eight years, children are able to infer appropriate responses to nonconventional requests in the form of hints. Finally, ten-year-old children, similar to adults [as shown in @blumkulka1987], judge that conventional indirect requests are the “right thing to say” more often compared to direct orders or hints, whereas five- and seven-year-olds do not show this metapragmatic reasoning [@bernicot1991].

### White lies

Next I consider another category of polite utterances reflecting speakers’ goal tradeoff: white lies. Children start producing white lies early on. Talwar and colleagues have shown the earliest evidence of white lie-telling in children: They found that the majority of three- to seven-year-old child participants in their studies told white lies and stated that an adult “looks okay for the picture” even though she has a conspicuous mark of lipstick on her nose [@talwar2002], or lied to a gift-giver about her gift that they actually found undesirable [@talwar2007].
					
Though they produce white lies early, young children’s understanding of goals for production of white lies seems limited. When the participants in Talwar and colleagues’ studies were asked for reasons why they decided to tell white lies, many stated they did not know why. Similarly, Italian children of same age group struggled to predict what the protagonist of a story might say in a situation where telling truth would not be polite [@airenti2011]. Although there was an increase in the proportion of correct responses with age, even six-year-olds did not predict the correct response above chance unless they were given an additional cue to think about politeness-related reasons. Thus, despite the evidence of early spontaneous production of white lies in familiar situations, children seem to have limited understanding of goals behind white lie-telling.

Studies of comprehension and evaluation of white lies show that young children are more charitable toward prosocial lies compared to other kinds of lies. Evidence suggests that by four years, children perceive prosocial lies as better than malicious lies [@bussey1999], and they rate lies as nicer than truths in politeness situations [@song2014]. @heyman2009 observed that 7- to 11-year-old children rated lie-telling more favorably in politeness situations (e.g. a teacher gave the protagonist an undesirable gift) than in transgression situations (e.g. the protagonist damaged a library book). This tendency to rate prosocial lies positively increases with age [@walper1992].

Children’s favorable perception of white lies tends to depend on their recognition of speaker goals and reasons for white lie-telling. When @heyman2009 asked participants for explanations of their evaluation of the protagonist’s behavior (telling a lie or truth) in politeness context, the participants were more likely to rate lie-telling more favorably and truth-telling more negatively when their focus was on the impact of the statement on others rather than the veracity of statements. Studies in other countries have also found that children in elementary school years view lie-tellers more positively if the lie is told in a public, face-threatening situation [@ma2011], or is intended to benefit others rather than the speaker herself [@fu2015]. Overall these findings show children evaluate white lies and blunt truths differently based on which communicative goal or intention is prominent in the given context.

As they get older, children make more subtle inferential judgments about implications of white lies, which shows their ability to identify epistemic and social goals as separate intentions manifested in white lies. Children become able to differentiate between various traits of a speaker based on her goal tradeoff decision. @xu2013 told 7- 9- and 11-year-old Chinese children stories of lie-tellers and truth-tellers with either intent of helping or harming the addressee, and looked at their ratings of benevolence and trustworthiness of the speaker. The participants rated helpful characters (both lie-tellers and truth-tellers) as nice and harmful characters as mean; for trust evaluations, younger children relied more on honesty whereas older children relied more on the intentions. This finding reveals an interesting trend in which children of younger ages are more narrowly focused on the speaker’s truth-telling goal, whereas older children consider the goal tradeoff more holistically and gradually shift their preference toward the face-saving goal. Indeed, in another study by @xu2010, Chinese children from the same age group who considered both honesty and politeness issues in evaluating white lie-tellers tended to tell a white lie more often than those who focused on only one of the two issues.

### Summary

In sum, the development of production and understanding of polite speech show predicted trajectories based on the currently proposed goal-based account. A greater degree of conflict or tradeoff between the speaker’s informational and social goals leads to more challenging cases of polite speech that are more difficult to produce or comprehend. Thus, from early on, children produce and understand many instances of rule-based polite speech using simple markers of politeness, involving minimal conflict between epistemic and social goals. As for indirect speech and white lies, cases that reflect speakers’ decisions based on the goal tradeoff, younger children before elementary school years show only limited understanding of motivation behind these more complex utterances. Finally, school-year children become competent at identifying reasons for both truth-telling (for epistemic reasons) and prosocial lie-telling (for social reasons) and making informed evaluations of speakers based on their tradeoff decisions.

## Conclusions
					
In this Chapter I argued for a goal-based account of polite speech, in which speakers consider their competing social goals (informational, pro-social, and self-presentational goals) to speak politely. The goal-based approach provides a way to unify previous theoretical frameworks for polite speech, and is consistent with empirical evidence in adults’ and children’s production and comprehension of polite speech. 

In Chapters 2 through 4, I will present empirical evidence from adults and children to support the goal-based account of polite speech. 
Chapter 2 presents a formal model of how polite speech emerges. We explored how speakers are expected to speak politely in situations where they are asked to provide feedback for the addressee's performance (e.g., poem recital). We built a computational model based on the assumption that speakers should consider goals to be informational, pro-social and self-presentational in speaking politely (as addressed in Chapter 1), and we show that our model successfully captures important patterns of adult predictions for polite speech (e.g., white lies and indirect speech). 

Chapters 3 and 4 examine children's understanding of polite speech. 
In Chapter 3, we look at whether 2- to 4-year-old children are able to understand that speakers account for prosocial goals in their speech, by examining their evaluation of polite requests (e.g., "Can you please pour me more water?"). 
In Chapter 4, we investigate whether children reason about tradeoff between different goals (e.g., informativity vs. prosociality) by looking at their evaluation of white lies (e.g., "Your cookie was tasty") versus blunt truths ("Your cookie was yucky"). 

The primary goal of this dissertation, then, is to probe whether and how adults and children reason about polite speech as reflecting competing goals to be informative, to be kind to others, and to present oneself in a good light, and tradeoffs between these goals. 