```{r, include=FALSE}
knitr::opts_chunk$set(echo = F, cache = T, warning=F, message=F, 
                      fig.width=4, fig.asp = 0.618, out.width = "90%", 
                      fig.align = 'center', fig.pos = 't')

library(here); library(tidyverse); library(ggthemes); library(langcog); library(brms); library(stringr); library(lme4); library(knitr)

source(here::here("index/disseration_helpers.R"))
child_lies_image_path <- "index/chapter_child_rmds/ch3_polite_lies/figs"
child_lies_file_path <- "index/chapter_child_rmds/ch3_polite_lies/files"
```

```{r child_inf_data}
d1 <- read.csv(here(child_lies_file_path, "trupol_data_all.csv")) %>%
  mutate(order = fct_recode(order, "1" = "1_2", "4" = "3_4"))
d_age <- read.csv(here(child_lies_file_path, "trupol_v2_subject_log.csv")) %>%
  select(subid, consent, english, age_exact, sex)
d1 <- left_join(d1, d_age) %>%
  filter(age == "adult" | site == "India" | consent == "Y") %>%
  filter(age == "adult" | site == "India" | english > 50)
  
d1$age <- as.factor(as.character(d1$age))
d1$order <- as.factor(as.character(d1$order))
d1$site <- as.factor(as.character(d1$site))
d1$polite <- as.factor(as.character(d1$polite))
d1$q_kind <- as.factor(as.character(d1$q_kind))
d1$cond <- as.factor(as.character(d1$cond))
d1$subid <- as.factor(as.character(d1$subid))
d1$answer <- as.factor(as.character(d1$answer))

order_orig <- read_csv(here(child_lies_file_path, "trupol_v2_order.csv")) %>%
  mutate_if(is.numeric, as.character)

d_orig <- d1 %>%
  mutate(cond = fct_recode(cond,
    "expt" = "exp"
  )) %>%
  mutate(trial = substr(q, 6, 6)) %>%
  mutate(sample = "original") %>%
  rename(speaker = polite, qkind = q_kind, agebin = age, age = age_exact) %>%
  mutate(qkind = fct_recode(qkind,
                            "mean" = "meanness",
                            "nice" = "niceness",
                            "truth" = "truth-telling")) %>%
  left_join(., order_orig) %>%
  
  select(subid, site, sample, cond, age, sex, order, item, trial, qkind, speaker, answer, age, agebin)

d_raw <- read_csv(here(child_lies_file_path, "trupol_v3_data_reorg.csv"))

d_filter_by_practice <- d_raw %>%
  filter(practice1 == "Y", practice2 == "Y", practice3 == "Y",
         practice4 == "Y", practice5 == "Y", practice6 == "Y")

d_clean <- d_raw %>%
  filter(subid %in% d_filter_by_practice$subid) %>%
  select(-practice1, -practice2, -practice3, 
         -practice4, -practice5, -practice6) %>%
  gather(-order, -subid, key = trial, value = answer) %>%
  separate(trial, c("trial", "question"), extra="merge") %>%
  mutate(trial = substr(trial, 6, 6)) %>%
  mutate(question = case_when(
                               grepl("playWhy", question) ~ "Pwhy",
                               grepl("play", question) ~ "play",
                               TRUE ~ question
                               )
         )

order <- read_csv(here(child_lies_file_path, "trupol_v3_order.csv")) %>%
  mutate_if(is.numeric, as.character)

d_join1 <- left_join(d_clean %>% mutate_if(is.numeric, as.character), order)

log <- read_csv(here(child_lies_file_path, "trupol_v3_subject_log.csv")) %>%
  rename(subid = "Subject ID") %>%
  filter(Consent == "Y", English > 3, !grepl("pilot", Comments)) %>%
  select(subid, Age, Gender)

d_rep <- left_join(log, d_join1) %>%
  filter(!is.na(order)) %>%
  rename(age = Age, sex = Gender) %>%
  mutate(site = "US", sample = "replication") %>%
  mutate(qkind = case_when(
    !is.na(qkind) ~ qkind,
    TRUE ~ question
  )) %>%
  mutate(speaker = case_when(
    qkind == "play" | qkind == "Pwhy" ~ "NA",
    TRUE ~ speaker
  )) %>%
  mutate(agebin = case_when(
    age < 7 ~ "6",
    age >= 7 ~ "8"
  )) %>%
  mutate(answer = case_when(
    answer == "Y" ~ "1",
    answer == "N" ~ "0",
    TRUE ~ answer
  )) %>% 
  select(subid, site, sample, cond, age, sex, trial, order, item, qkind, speaker, answer, agebin)

d <- rbind(d_orig, d_rep) %>%
  mutate_if(is.character, as.factor)

d <- d %>%
  filter(site == "US") 

```

## Introduction

Imagine your friend bakes some cookies for you, but the cookies are hard and salty and simply taste terrible. If your friend asks how you like the cookies, must you admit, “these cookies taste terrible,” or is it acceptable to say: “They are delicious!”? The latter is misleading but gives the listener what she might want to hear—-in other words, it would be polite.

Politeness violates a critical principle of cooperative communication: exchanging information efficiently and accurately [@grice1975]. If information transfer was the only currency in communication, a cooperative speaker would find polite utterances undesirable because they are potentially misleading. People are polite, however, and speakers do produce polite utterances. 
Adults and children spontaneously produce requests in polite forms [@clark1980; @axia1985]. Speakers exhibit politeness strategies even while arguing, preventing unnecessary offense to their interactants [@holtgraves1997]. 
Listeners even attribute ambiguous speech to a polite desire to hide a truth that could hurt another’s self-image [e.g. @bonnefon2009]. 
In fact, it is difficult to imagine human speech that efficiently conveys only the truth. 
Intuitively, politeness is one prominent characteristic that differentiates human speech from stereotyped robotic communication, which may try to follow rules to say “please” or “thank you” yet still
lack genuine politeness.

Does this mean people are not cooperative communicators? 
@brown1987 recast the notion of a cooperative speaker as one who has both an informational goal to improve the listener’s knowledge state as well as a prosocial goal to minimize any potential damage to the hearer’s (and the speaker’s own) self-image, which they called *face.* 
In their analysis, if the speaker’s intended meaning contains no threat to the speaker or listener’s face, then the speaker will choose to convey the meaning in an efficient manner, putting it *on the record*. As the degree of face-threat becomes more severe, however, a speaker will choose to be polite by producing more indirect utterances.

One possible proposal based on this idea by @brown1987 is that people think about polite language as reflecting a tradeoff between information transfer and face-saving.
When you try to save face, you hide or you risk losing some information in your intended message by making your utterance false or indirect to some degree. 
When you prioritize truthfulness and informativity, you may risk losing listener’s (or your own) face.
In the current study, we examine whether and how children and adults may think about polite speech this way: 
Do they reason about polite speech as reflecting a tradeoff between the goals of information transfer and face-saving?

From very early on, children seem to understand both informational and social concerns behind language use.
Around one year of age, children already start to adjust their own informativeness in their communicative action depending on the listener needs [@liszkowski2008], and as they get older they correctly judge a speaker’s truthfulness and preferentially learn from informants who were previously accurate [@corriveau2009]. By 6 years they are able to readily judge whether teachers are being underinformative [@gweon2014].
Children also understand speakers' goals to be kind, as 3- to 4-year-olds reason that those who say "please" are nicer and more polite, and are likely to be better play partners [@yoon2019].

Even though previous research has suggested that children consider informational and social goals that speakers have, it is unclear how they might reason these goals together. 
For example, do children think of the goals to be informative and to be kind as separate, fixed *rules* to follow, or do they make *inferences* that accounts for both goals that the speaker may consider?
One possibility is that children have a rule-based approach to language: 
They may think about deterministic, separate rules such as "If you want something, then you should say *please*" and "If you see/feel/think *X*, then you should (truthfully) say *X.*"
Children can use these rules to both produce polite and truthful utterances themselves, and evaluate speakers based on whether they follow these rules or not ("She is nice because she said *please*"; or "She is bad/wrong because she said these cookies are tasty but they are actually salty and yucky.")

Whereas these straightforward rules can make language production and understanding easy and productive, speakers often do not follow these rules deterministically. 
For example, people sometimes tell the truth ("Those herbs are poisonous, you shoudn't eat them") but at other times they tell lies to be kind ("This is a very delicious salad that you prepared!").
Indeed, caregivers contradict their own teachings as they demand children to tell the truth in some contexts ("Who broke the vase? Be honest."), but reproach them for telling the truth in other contexts (Child: "This [meal that Grandma cooked] is yucky" Father:"Don't say that, you should be nice!").
Thus, language users ultimately need to learn that language reflects not only simple deterministic rules to follow, but also more nuanced tradeoffs between different goals that speakers might have depending on the situation. 

Do adults and children go beyond simple rules and engage in an *inference*-based reasoning to think about how speech reflects goal tradeoffs? 
Here we look at the case study of prosocial lies (versus blunt truths) to examine whether children understand the tradeoff between speakers' informational goals and prosocial goals. 
For example, if Alice asked Bob for feedback on her performance that was poor in quality (e.g., cookies she baked that were salty or a presentation she gave that was unintelligible), Bob would be in a bind: 
On one hand, he would want to be informative and convey accurate information, which would lead him to say "[Your cookies] were terrible." 
On the other hand, he would also want to be prosocial and kind, and make Alice feel happy and respected, by saying "[Your cookies] were delicious."
In such context, telling a lie would indicate that the speaker chose to prioritize the goal to be kind, whereas telling the truth would indicate the speaker's priority for the goal to be informative. 
Critically, however, Bob should have a good reason to lie; if Alice was asking about some cookies Bob himself got from a store instead of cookies that she baked, then Bob would have no reason to lie to Alice and say that the cookies were "delicious," which would only be misleading.
Thus, in order to reason about speaker intentions and goal tradeoff considerations correctly, people need to account for the context in which the utterance was produced.

Previous research suggests that children *produce* prosocial lies (utterances that are dishonest yet kind) appropriately depending on context from early on. 
There is evidence that by 3 years, children start to tell white lies, and e.g., say that an adult “looks okay for the picture” even though she has a conspicuous mark of lipstick on her nose [@talwar2002], or lie to a gift-giver about her gift that they actually found undesirable [@talwar2007].

But do children *understand* that prosocial lies reflect speakers' priority to be prosocial over being truthful and informative? 
Children do seem to be sensitive to speakers' prosocial intentions: 
By 4 years, children evaluate lies differently depending on whether the lies were told to be kind to the listener (e.g., "Your new hat looks great") or to hide their own misdeed ["Yes, I brushed my teeth"], judging the latter to be worse [@bussey1999].
7- to 11-year-old children also tend to rate lie-telling more favorably in politeness situations (e.g. a teacher gave the protagonist an undesirable gift) than in transgression situations [e.g. the protagonist damaged a library book; @heyman2009]. 

It is an open question, however, whether children evaluate the exact same lie differently depending on the perceived goal tradeoff.
For example, saying "your cookies were tasty" may be an acceptable lie if the listener baked those cookies as a gift for the speaker, but the same lie might only be misleading and not helpful if the listener did not bake the cookies himself but simply wanted to taste the cookies. Likewise, telling the truth "the cookies were yucky" may seem blunt and harsh if the speaker is talking to the person who baked the cookies, but the same utterance can be reasonable and even helpful if the listener simply wants to taste the cookies and is curious how the speaker liked them.
In the current study, we ask whether children are able to reason about polite liars versus blunt truth-tellers, on the dimensions of information transfer (being honest) vs. face-saving (being nice/mean).

## Method

```{r childInfSample, results = 'asis'}
child_lies_tab1 <- d %>% 
  group_by(cond, sample, agebin, subid) %>%
  summarise(n=n()) %>%
  group_by(cond, sample, agebin) %>%
  summarise(n=n()) %>%
  mutate(n = as.character(round(n)))

child_lies_tab2 <- d %>% 
  distinct(cond, sample, agebin, age, subid) %>%
  group_by(cond, sample, agebin) %>%
  summarise(mean=round(mean(age),2), sd=round(sd(age, na.rm=T), 2))

child_lies_tab3 <- d %>%
  group_by(cond, sample, agebin, sex, subid) %>%
  summarise(n=n()) %>%
  group_by(cond, sample, agebin, sex) %>%
  summarise(n=n()) %>%
  filter(sex == "F") %>%
  select(-sex) %>%
  rename(Female = n)

child_lies_tab <- left_join(child_lies_tab1, child_lies_tab3) %>%
  left_join(., child_lies_tab2) %>%
  ungroup() %>%
  mutate(cond = fct_recode(cond, 
                           "Control (no reason for dishonesty)" = "cont",
                           "Experimental (politeness reasons)" = "expt"
                           )) %>%
  mutate(agebin = fct_recode(agebin,
                             "5-6-yr" = "6",
                             "7-8-yr" = "8"
                             )) %>%
  rename('Total N'=n) %>%
  rename(Condition = cond) %>%
  rename(Sample = sample) %>%
  rename('Age group' = agebin) %>%
  rename('Mean age (years)' = mean, "SD age (years)" = sd)


# apa_table(child_lies_tab, caption = "Participant demographic information.", align = c(rep("l", 6)) %>%
#    column_spec(column = 5, width = "3cm")
   
child_lies_tab %>% 
  replace(is.na(.), "") %>%
  kable("latex", 
        booktabs = T, 
        caption = "Participant demographic information.",
        caption.short = "Participant demographic information") %>%
  kable_styling(latex_options = "scale_down") %>% 
  row_spec(row = 0, bold = TRUE) %>% 
  column_spec(column = 6, width = "2.2cm") %>% 
  column_spec(column = 7, width = "2.2cm") 

```
### Participants

We recruited parents and their children at Children's Discovery Museum of San Jose, and adults through Amazon's Mechanical Turk. We recruited two samples: a first, *original* sample and a second, pre-registered *replication* sample^[see https://osf.io/u4v7y/register/5771ca429ad5a1020de2872e for pre-registered method, hypotheses and analysis plans.]. Participant demographic information is shown in Table\ \ref{tab:childInfSample}. 

As part of the task, we included training trials where children and adults were tested on the meanings of important keywords such as "nice", "mean", and "truth." For example, participants were asked: "Nicole gave her friend a gift. Was Nicole nice? Was Nicole mean?" We excluded participants who gave wrong answers on these trials, which led to exclusion of 2 child participants from the original sample.

### Stimuli and design

We presented stories in which some characters (*speakers*) were asked to give evaluative feedback on something bad that they just experienced (e.g., a yucky cookie that they tasted, or a boring game that they played).
There were two different *context* conditions: 
In the *experimental* condition, speakers were asked by listeners to comment on something that the listeners themselves had created, which provides the speakers with politeness reasons to lie and hide the poor quality of the product in order to not hurt the listener's feelings.
For example, one story in the experimental condition read: "Look, this is Edward [the listener]!
One day, Edward decided to bake some cookies.
Edward brought his cookie to school and met his friend Mary [the speaker]. Edward said to his friend Mary, “Here, try my cookie!”
Mary tasted the cookie,
and she did not like the cookie at all — she thought the cookie tasted yucky!
Edward asked Mary, “Mary, how did you like my cookie?” Mary told Edward, “Edward, your cookie was tasty.”"
In the *control* context condition, speakers were asked by listeners to comment on something that they stumbled upon, not what the listeners created (and thus had no reasons to lie about the quality of the product). 
The cookie story in the control condition read:
"Look, this is Mary!
One day, Mary saw a free cookie.
Mary said, “It’s a free cookie, I’ll try it!”
Mary tasted the cookie,
and she did not like the cookie at all — she thought the cookie tasted yucky!
Mary’s friend Edward also wanted to taste the cookie. Edward asked Mary, “Mary, how did you like the cookie?” Mary told Edward, “Edward, the cookie was tasty.”"
For the original sample, each participant saw only one of the two conditions (i.e., context was a between-participants variable), whereas for the replication sample, each participant saw both conditions (within-participants).

Each story presented two episodes that each presented a different *speaker type*: one who told a lie and the other who told the truth. After presenting what each speaker decided to say, we presented three *question types*, asking participants to judge (1) whether the speaker told the truth; (2) whether the speaker was nice; and (3) whether the speaker was mean.
For the original sample, each participant heard two stories from the same condition (either experimental or control); for the replication sample, each participant heard four stories, two from each condition. 

After presenting the two episodes, we asked participants to compare the two speakers and select a better play partner ("Who do you want to play with more, Sally or Mary?") and the reason for their answer.
The order of context conditions, speaker types and question types was counterbalanced across participants. 
Training trials and full example stories are provided in Supplementary Materials.

### Procedure

For child participants, the experimenter read the storybook with children in a room in a children's museum. 
They were first introduced to the storybook with simple stories to familiarize them with keywords like "nice," "mean," and "truth" (e.g., "Pam ate five cookies, but Pam told her mom a lie that she didn’t eat any cookie. Was Pam telling the truth?"). 
Then the experimenter read two (original) or four (replication) stories to each participant. 
While reading each episode, experimenters checked for the participants' comprehension twice by asking whether the speaker liked the product (e.g., "So did Sally like the cookie or did she not like the cookie?") and what the speaker told the listener ("So what did Sally tell Edward again?"). If the participant gave an incorrect answer to these comprehension check questions, the experimenter said "let's think about that one more time," and repeated the story. For adult participants, we presented the same stories that children heard in an online task (see http://langcog.stanford.edu/expts/EJY/trupol/adult/trupol.html for the online task that adults completed). 

## Results and Discussion

### Speaker ratings: truth-telling, niceness, meanness

```{r childInfPlot}
d_plot <- d %>%
  # filter(trial %in% c(1, 2, 3, 4)) %>%
  filter(qkind %in% c("nice", "mean", "truth")) %>%
  # filter(qkind %in% c("nice", "mean")) %>%
  # filter(qkind != "truth") %>%
  mutate(qkind = fct_relevel(qkind, "truth", "nice", "mean")) %>%
  mutate(qkind = fct_recode(qkind, 
                            "telling the truth" = "truth"
                            )) %>%
  mutate(speaker = fct_recode(speaker,
                            "judgments for honest speaker" = "honest",
                            "judgments for dishonest speaker" = "polite"
                            )) %>%
  mutate(cond = fct_recode(cond, 
                           "no apparent reason \nfor dishonesty" = "cont",
                           "politeness reasons" = "expt"
                           )) %>%
  mutate(agebin = fct_recode(agebin,
                             "5-6-yr" = "6",
                             "7-8-yr" = "8"
                             )) %>%
  filter(answer == "1" | answer == "0") %>%
  mutate(answer = as.numeric(as.character(answer)))

plot <- d_plot %>%
  group_by(sample, agebin, qkind, cond, speaker, subid) %>%
  summarise(answer = mean(answer, na.rm=T)) %>%
  group_by(sample, agebin, qkind, cond, speaker) %>%
  multi_boot_standard(col="answer") %>%
  rename(answer = mean) %>%
  # ggplot(., aes(x=agebin, y=answer, col=cond, shape=sample, alpha=sample)) +
  ggplot(., aes(x=agebin, y=answer, col=cond, shape=sample)) +
  # geom_jitter(height=.05) +
  geom_smooth() +
  geom_point(aes(size=.4), position=position_dodge(width=.3), stat = "identity") +
  geom_linerange(aes(ymin=ci_lower, ymax=ci_upper), position=position_dodge(width=.3), stat = "identity") +
  facet_grid(qkind~speaker) + 
  theme_few() +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  geom_hline(aes(yintercept=0.5), linetype="dashed") +
  scale_colour_ptol() + 
  # scale_alpha_manual(values=c(0,1)) +
  # ggtitle("Expt 1: Judgments for honest vs. polite speaker") +
  ylab("proportion \"yes [the speaker was _____]\"") +
  xlab("age") +
  ylim(-0.1,1.1) +
  scale_y_continuous(breaks=seq(0,1,.5)) +
  guides(size=FALSE)

# ggsave(here("age_by_cond_bothSamples_truth.pdf"), width=6, height=5)
ggsave(plot, file=here::here(child_lies_image_path, "trupol_plot.png"), width=5, height=5)
```

```{r figTrupolResultsPlacement, fig.env = "figure*", fig.pos = "p", fig.width=7, fig.height=5, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Speaker ratings by different age groups (x-axis) for the honest speaker (left column) and the dishonest speaker (right), in different contexts (colors). Rows represent question types (e.g., Was Sally telling the truth?), and y-axis represents proportion saying \`\`yes\" to the question. Shapes represent original (circles) vs. replication samples (triangles). ", fig.scap = "Speaker ratings for the experiment in Chapter 3."}
png::readPNG(here::here(child_lies_image_path, "trupol_plot.png")) %>%
  grid::grid.raster()
```

```{r trupol_brm, echo = F, results = 'asis'}
# ms_stat <- d %>%
#   filter(qkind == "nice" | qkind == "mean" | qkind == "truth") %>%
#   filter(!is.na(agebin)) %>%
#   mutate(answer = as.numeric(as.character(answer))) %>%
#   mutate(age = scale(age)) %>%
#   filter(!is.na(age)) %>%
#   select(sample, cond, trial, item, age, agebin, speaker, qkind, subid, answer)
# 
# brm_trupol <- brm(data=ms_stat, family=bernoulli,
#                   answer ~ cond * qkind * speaker * age + (qkind + speaker| subid) + (cond + qkind + speaker | item) + (cond + qkind + speaker | sample), iter=3000, control = list(adapt_delta = 0.99, max_treedepth = 15))
# 
# save(brm_trupol, file=here(child_lies_file_path, "brm_trupol.Rds"))
load(here(child_lies_file_path, "brm_trupol.Rds"))

trupol_tab <- as.data.frame(summary(brm_trupol)$fixed) %>%
  select(Estimate, Est.Error, 'l-95% CI', 'u-95% CI') %>%
  rename(Mean = Estimate,
         "SD" = Est.Error,
         "95% CI-Lower" = 'l-95% CI',
         "95% CI-Upper" = 'u-95% CI'
         )

trupol_tab$Predictor <- c("Intercept",
                      "Experimental condition (Expt)",
                      "Niceness question (Nice)",
                      "Meanness question (Mean)",
                      "Dishonest speaker (Dishonest)",
                      "Age",
                      "Expt * Nice",
                      "Expt * Mean",
                      "Expt * Dishonest",
                      "Nice * Dishonest",
                      "Mean * Dishonest",
                      "Expt * Age",
                      "Nice * Age",
                      "Mean * Age",
                      "Dishonest * Age",
                      "Expt * Nice * Dishonest",
                      "Expt * Mean * Dishonest",
                      "Expt * Nice * Age",
                      "Expt * Mean * Age",
                      "Expt * Dishonest * Age",
                      "Nice * Dishonest * Age",
                      "Mean * Dishonest * Age",
                      "Expt * Nice * Dishonest * Age",
                      "Expt * Mean * Dishonest * Age"
                      )
rownames(trupol_tab) <- NULL
trupol_tab <- trupol_tab[,c(5,1:4)]

apa_table(trupol_tab, caption= "Predictor mean estimates with standard deviation and 95% credible interval information for a Bayesian linear mixed-effects model predicting \'\'yes\" responses to questions.")

# trupol_tab %>% 
#   kable("latex", booktabs = T, 
#         caption = "Predictor mean estimates with standard deviation and 95% credible interval information for a Bayesian linear mixed-effects model predicting \'\'yes\" responses to questions.",
#         caption.short = "Predictor mean estimates with standard deviation and 95% credible interval information for a Bayesian linear mixed-effects model predicting \'\'yes\" responses to questions for the experiment in Chapter 4.") %>% 
#   row_spec(row = 0, bold = TRUE)

```

The results from child and adult participants are plotted in Figure\ \ref{fig:figTrupolResultsPlacement}. 
We can make a few qualitative observations for each of the question types: 
For the truth-telling rating, adult and child participants correctly judged that the honest speaker was indeed telling the truth, and that the dishonest speaker was not telling the truth, regardless of the condition (top row of Figure\ \ref{fig:figTrupolResultsPlacement}). 
The niceness rating varied by condition: Given politeness reasons, participants tended to say that the dishonest speaker was nice more often and honest speaker was nice less often (middle row of Figure\ \ref{fig:figTrupolResultsPlacement}). The meanness rating showed the opposite pattern (bottom row of Figure\ \ref{fig:figTrupolResultsPlacement}). 

Additionally, we also see a developmental trend. 
Adults showed the clearest discrepancies in speaker ratings by condition and tended to be much more charitable toward the dishonest speaker given politeness reasons compared to no apparent reasons to lie. 
Older children (7-8-year-olds) show similar patterns but with smaller rating differences between the two conditions. 
Younger children (5-6-year-olds) also differentiated between the two conditions but not as much as older children and adults did, and younger children generally tended to rate the honest speaker more favorably than the dishonest speaker across both conditions.

We conducted statistical analysis to verify these observations. We used a Bayesian linear mixed-effects model [`brms` package in R; @R-brms] using crossed random effects of participant, item and sample with the maximal random effect structure supported by the design [@gelman2006data; @barr2013random]. We ran the statistical model on the child dataset only. Age is plotted in bins in Figure\ \ref{fig:figTrupolResultsPlacement}, but was analyzed as a continuous variable, scaled and centered, in our statistical model. 

The Bayesian linear mixed model^[This model had a few adjustments to the pre-registered model structure: whereas we pre-registered \texttt{brm(niceness rating $\sim$ age * condition * speaker + (speaker * condition | subject) + (speaker * condition | item)}, we ran a more appropriate and inclusive model that contained question type as a main effect and a random effect of item, and corrected crossed random effects structure: \texttt{brm(answer ~ $\sim$ * condition * speaker type  * question type + (question type + speaker type | participant) + (condition + question type + speaker type | item) + (condition + question type + speaker type | sample)}..
] predicting "yes" responses based on participant age, context type (control vs. experimental), speaker type (honest vs. dishonest) and question type (truth-telling vs. niceness vs. meanness) showed a positive interaction between experimental condition, dishonest speaker and niceness judgment: Participants judged a dishonest speaker as nicer in the experimental condition, where the speaker had politeness reasons to lie to the listener, compared to the control condition where the speaker had no apparent reasons to lie. 
Thus, children were indeed able to evaluate the dishonest speaker's intentions differently based on the context. 
There also was a positive interaction between dishonest speaker and meanness rating, which indicates that a dishonest speaker was rated as mean more often compared to the honest speaker overall regardless of the condition. 

```{r plotListenerFeel}
d_Lfeel1 <- d %>%
  filter(qkind == "LFeel") %>%
  mutate(answer = as.numeric(as.character(case_when(
    grepl(paste( "sad", "bad", sep = "|" ), answer, ignore.case=TRUE) ~ "0",
    grepl(paste( "good", "happy", "nice", sep = "|" ),  answer, ignore.case=TRUE) ~ "1",
    TRUE ~ "NA"
  )))) %>%
  filter(!is.na(answer))

plot_Lfeel <- d_Lfeel1 %>%
  rbind(., d %>% filter(qkind == "listener_feeling")) %>%
  filter(answer == "1" | answer == "0") %>%
  mutate(answer = as.numeric(as.character(answer))) %>%
  mutate(speaker = fct_recode(speaker,
                              "dishonest" = "polite"
                              )) %>%
  ggplot(., aes(x=age, y=answer, color=answer)) +
  geom_jitter(height=.1) +
  geom_smooth() +
  facet_grid(.~speaker) +
  geom_hline(yintercept=0.5, lty=2) +
  theme_few() +
  ylab("listener feeling \n(0 = negative, 1 = positive)") +
  theme(legend.position = "none")
  

ggsave(plot_Lfeel, file=here::here(child_lies_image_path, "listener_inference.png"), width=5, height=3)

```

```{r figTrupolLfeelResultsPlacement, fig.env = "figure*", fig.pos = "t", fig.width=7, fig.height=4, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Children's judgments for listener feelings (y-axis) upon hearing the utterance of the honest versus dishonest speaker (columns), across age (x-axis).", fig.scap = "Listener feeling judgments in the experiment in Chapter 3."}
png::readPNG(here::here(child_lies_image_path, "listener_inference.png")) %>%
  grid::grid.raster()
```

Finally, there was also a positive interaction between participant age, dishonest speaker and niceness judgment, which confirmed that children judged the dishonest speaker as nice more often with increasing age, a trend that extended to adulthood (Figure\ \ref{fig:figTrupolResultsPlacement}). 
Why did adults and older children judge the dishonest speaker more favorably compared to younger children? 
One possible explanation is older children are more proficient at inferring other people’s mental states [@wellman2004], leading them to place more weight on the addressee’s feelings in evaluating a white lie or blunt truth. 
Indeed, when asked about how the listener would have felt upon hearing the polite liar's utterance, older children tended to answer that the listener would have felt "happy", "good", or "nice" more often than younger children (Figure\ \ref{fig:figTrupolLfeelResultsPlacement}).
Another possibility is that younger and older children use different communicative goals; younger children prioritize honesty, whereas older children value politeness more. 
Finally, it is also possible that children's construal of linguistic terms "niceness" and "meanness" may differ from adults (see more detailed explanation in section "Play partner selection" below). 

### Play partner selection

```{r plotPlayPartner}
d_play <- d %>%
  filter(qkind == "play") %>%
  mutate(answer = fct_recode(answer, "1" = "Sally", "1" = "Richard", "1" = "Bobby", "1" = "Nancy", "0" = "Mary", "0" = "Stanley", "0" = "Colin", "0" = "Gabby")) %>%
  filter(answer == "0" | answer == "1") %>%
  mutate(answer = as.numeric(as.character(answer))) %>%
  mutate(cond = fct_recode(cond, 
                           "no apparent reason \nfor dishonesty" = "cont",
                           "politeness reasons" = "expt"
                           ))

plot_play <- d_play %>%
  ggplot(., aes(x=age, y=answer, color=cond)) +
  geom_jitter(height=.1) +
  geom_smooth(span=1.5) +
  # facet_grid(.~cond) +
  geom_hline(yintercept=0.5, lty=2) +
  scale_color_ptol(name="context") +
  theme_few() +
  ylab("play partner preference \n(0=dishonest, 1=honest)")
  
ggsave(plot_play, file=here::here(child_lies_image_path, "play_partner.png"), width=5, height=3)

```

```{r figTrupolPlayPlacement, fig.env = "figure*", fig.pos = "t", fig.width=7, fig.height=4, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Children's play partner selection between the honest speaker (1 on the y-axis) and dishonest speaker (0 on the y-axis) across age (x-axis), across the two context conditions (columns).", fig.scap = "Play partner selection in the experiment in Chapter 3."}
png::readPNG(here::here(child_lies_image_path, "play_partner.png")) %>%
  grid::grid.raster()
```

```{r}
d_play2 <- d %>%
  filter(agebin != "adult") %>%
  filter(qkind == "play" | (qkind == "nice" & speaker == "honest")) %>%
  select(subid, site, sample, cond, trial, age, agebin, qkind, answer) %>%
  mutate(answer = fct_recode(answer, "1" = "Sally", "1" = "Richard", "1" = "Bobby", "1" = "Nancy", "0" = "Mary", "0" = "Stanley", "0" = "Colin", "0" = "Gabby")) %>%
  filter(answer == "0" | answer == "1") %>%
  mutate(answer = as.numeric(as.character(answer))) %>%
  mutate(cond = fct_recode(cond, 
                           "no apparent reason \nfor dishonesty" = "cont",
                           "politeness reasons" = "expt"
                           )) %>%
  spread(qkind, answer)

plot_play_nice <- ggplot(data=d_play2,
       aes(x=nice, y=play, colour = cond)) +
  # facet_grid(.~cond) +
  geom_jitter(height = .05, width=.2) +
  theme_few() +
  scale_color_ptol(name="context") +
  geom_hline(aes(yintercept=0.5), linetype="dashed") +
  # geom_smooth(method = "lm", se = FALSE, size=.5) +
  geom_smooth(method = "lm", se = T, size=.5) +
  xlab("Response to \"was [the honest speaker] nice?\" \n(0=no, 1=yes)") +
  ylab("Play partner selection \n(0=dishonest, 1=honest)")
  
ggsave(plot_play_nice, file=here::here(child_lies_image_path, "play_partner_nice.png"), width=6, height=4)
```

```{r figTrupolPlayNicePlacement, fig.env = "figure*", fig.pos = "t", fig.width=7, fig.height=4, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Children's play partner selection (y-axis) versus their nicess judgment for the honest speaker (x-axis) across age (x-axis), across the two context conditions (columns).", fig.scap = "Play partner selection versus niceness judgment for the honest speaker in the experiment in Chapter 3."}
png::readPNG(here::here(child_lies_image_path, "play_partner_nice.png")) %>%
  grid::grid.raster()
```

When asked to choose the speaker they would like to play with more,  children's preference for the honest speaker was slightly higher in the control condition (i.e., given no apparent reason for dishonesty), though in both conditions children selected the honest speaker as their play partner more often overall (Figure\ \ref{fig:figTrupolPlayPlacement}). 
Children's play partner choice differed depending on their niceness rating of the honest speaker within the same trial (Figure\ \ref{fig:figTrupolPlayNicePlacement}): those who rated the honest speaker as "nice" were more likely to prefer to play with the honest speaker, whereas those who rated the honest speaker as "not nice" were divided between selecting the honest speaker and dishonest speaker as their play partner. 

Why did some children prefer to play with the honest speaker, even when they rated the honest speaker as "not nice" given politeness reasons to lie? 
Perhaps the niceness ratings and play partner preference have different implications: 
Play partner choice could reveal the participant's holistic judgment of the two speakers' personalities ("I like Sally better because she tells the truth"), 
whereas judgment of whether a given speaker is "nice" can depend on several factors, such as the participant's evaluation of the speaker's personality ("Sally is not a nice person"), the speaker's intention ("Sally was not trying to be nice and instead wanted to tell the blunt truth") and the construal of the linguistic term "nice" ("Sally was not nice, because nice means saying something positive like the cookie is tasty").

## Conclusion

In this work, we showed that both adults and 5- to 8-year-old children were able to use context information to evaluate speaker intentions and rate their niceness and meanness accordingly. This suggests that they are sensitive to the tradeoffs between informational goals (pushing toward truthfulness) and prosocial goals (pushing toward face-saving) and reason about what goals should be prioritized depending on the context.

There was also a trend for developmental differences in attribution of niceness and meanness to prosocial liars versus blunt truth-tellers: Younger children (5-6-year-olds) were more charitable toward blunt truth-tellers in their rating of speaker niceness. 
However, it is still an open question why younger and older children different in their evaluation of the speaker intentions. Possibilities are (1) younger children might prioritize the social concerns over informational concerns compared to older children and adults; (2) their lack of Theory-of-Mind abilities prevent them from understanding needs for polite lies; or (3) their construal of linguistic terms like "nice" may differ from that of older children, and depend more on rule-following and less on face-saving.
Future work should tease apart these possibilities by testing a broader set of utterances that reflect more gradient tradeoff decisions between informational and social goals. For example, the speaker could say "I don't think this cookie is very tasty" to be somewhat informative but also somewhat face-saving at the same time.

In sum, this work presented evidence that by 6 years children are able to evaluate speakers differently based on context that affects tradeoff of informational and social goals, though the ability to evaluate this tradeoff may develop until adulthood. 
